### 2018-07-02 response-to-reviewers.tex
response added

% -*- mode: LaTeX; mode: flyspell; -*-
% mode: Tex-Pdf -*-
\documentclass{article}
\usepackage{amsmath}
\usepackage[T1]{fontenc}
\usepackage[bookmarks=TRUE,
            colorlinks,
            pdfpagemode=none,
            pdfstartview=FitH,
            citecolor=black,
            filecolor=black,
            linkcolor=blue,
            urlcolor=black,
            ]{hyperref}
\usepackage{graphicx}
\usepackage{icomma}
\usepackage[utf8]{inputenc}
\usepackage{natbib}
\usepackage{setspace}
\usepackage{xspace}
\input{isomath}

\newcommand{\debug}[1]{\marginpar{\small\raggedright\begin{spacing}{1} #1
\end{spacing}
}}
\newenvironment{response}
{\slshape}{}

\begin{document}

\section*{Response to the referees}

\section{Comments by the editor}

In revising your paper, please make an effort to keep within the
journal's word-length norm of 7500 words (including references, notes
and appendices, but not figures and tables) and restrict the number of
references to 50 items.

\debug{nothing else but 7500 words/50 items.}

When submitting your revised manuscript, you will be able to respond to the comments made by the referee(s) in the space provided.  You can use this space to document any changes you make to the original manuscript.  In order to expedite the processing of the revised manuscript, please be as specific as possible in your response to the referee(s).

\section{Referee 1}

\subsection{Main comments:}

\begin{enumerate}
\item 1. The paper aims to contribute to an already large
  literature. The recent literature in this field focus on the
  identification of causal effects by using instrumental variable
  approaches (see, e.g., Isphording et al., 2014; Yao and van Ours,
  2015). However, I like the fact that the authors a very clear that
  they are not able to identify causal effects. This is, of course, a
  shortcoming and is limiting the overall contribution of the
  paper. Given the specific focus of International Journal of Manpower
  and the interests of its readership, I find that the paper is
  nevertheless providing a small, but still interesting
  contribution. By analysing data from Estonia and providing results
  on natives’ language skills the paper distinguished itself form
  large parts of the literature and adds some new results to our
  knowledge on the labour market effects of language skills.
\item My main concern is with some of their wage results. I find it
  puzzling that they don’t find a wage premium for Russian men who
  have Estonian language skills as they do find a sizeable significant
  effect of about 11 to 17 percent for Russian women and a significant
  positive effect for Estonians who speak Russian. Furthermore, they
  find that Estonian language skills do reduce the probability of
  being unemployed for Russians. Why is there a reduction in the
  probability of being unemployed, but no wage effect? Can we trust
  this result? Looking at the descriptive statistics (see Table 1) the
  wage for Russian men who speak Estonian seems to be higher compared
  to Russian men without the ability to speak Estonian (489.96 vs
  401.59). The authors should either provide more statistics on this
  result (if possible) or a more detailed discussion on potential
  reasons that lead to this finding.
\item The paper needs to be checked for spelling and grammar
  errors. There are a number of typos and errors, which should be
  corrected in a revision. This would normally be a minor comment, but
  here the authors should take this comment very serious as there are
  so many mistakes.
\end{enumerate}

\subsection{Minor comments:}

\begin{enumerate}
\item - The description of the estimation models in Chapter 4 should
  be more detailed. Please describe more specifically what exactly you
  are estimating. In particular the description of the second model
  estimating the time trend is very short.
\item - The tables and figures should have notes that explain in more
  detail what is shown in the respective table and figure. For
  instance, the table notes should contain the included control
  variables, the sample period and the age restriction applied.
\item 
- Page 4: You write that you are only analysing individuals who are
working or actively looking for a job, but in line 35 on the same page
you write that inactivity is one of the included labour market
outcomes. Please clarify this and be clear in your description of what
is included in your sample.
\item 
- The sample size for different specification of the same analysis
should be the equal. Otherwise it is difficult to conclude whether the
changes in the coefficients are coming from the addition of more
controls or form the change in the size of the estimation sample.
\item 
- In the paper, you are only showing the results of the variables of
interest. I suggest to provide tables including all coefficients (not
the year dummies) in the Appendix. It might be interesting to see how
the coefficients of the control variables change across the different
models.
\item 
- All tables: Be consistent in the description of your tables. The
table notes and the labels for e.g., "observations", are inconsistent
across the different tables. 
\item 
- Page 1: To cite Chiswick you are using different versions
(B. Chiswick and B. R. Chiswick).

\begin{response}
  OT: let's make all the technical changes and thereafter I'll go over the
  language.  Maybe we'll need a language editor but hope we don't.
\end{response}

\item 
- Page 2, line 58: Not the unemployment rate, but the probability of
being unemployed is reduced.
\item 
- Page 3, lines 46-50: You are using a comma as the decimal separator, but in all your tables you are using a point. Please use a point everywhere. 
\end{enumerate}

\section{Referee: 2}

\subsection{Additional Questions:}

\subsubsection*{4. Results}

\begin{enumerate}
\item For this papers findings section in the abstract they imply that
  for all men fluency in Estonian is related to 5\% lower unemployment
  and no income premium.  From Table 2 and 3 it appears that this
  should be for only Russian males. English skills are associated with
  a large income premium and no unemployment. From Table 2 and 3 this
  appears to be more accurately just Russians, as the Estonians appear
  to have a significant negative correlation with unemployment.  This
  is supported by what is said later in the Discussion and Concluding
  Remarks section in what they state is their most intriguing
  observation.  Claiming this to be the most intriguing is interesting
  as it seems to support some what previous literature has stated and
  one of the extensions that this paper is making the inclusion of
  women and namely how their effects differ from males and previous
  literature. 
\item In the Discussion and Concluding Remarks section they state that
  “The lower end labour market, associated with frequent unemployment,
  is better integrated and those who are fluent in the language may
  expect both less unemployment and higher wage. However, men at
  better paid and more stable jobs gain little form Estonian” (the
  language I presume) This conclusion felt surprising when reading the
  paper as it did not feel fully fleshed out in the results section
  how this was observed. Tying this to the results would be helpful
  and make it clearer exactly where these results come from.
\item In Table 3 I am perplexed how the number of observations increases as more restrictions are added to the model. How could running the same model but including additional workplace controls increase the observations from 7978 to 8233 for men and 9697 to 9895 for women? It makes me somewhat cautious of the results—though it could just be a typo. Could the models be run using the same sample for each column?
\end{enumerate}

\subsubsection*{6. Quality of Communication}

\begin{enumerate}
\item There appear to be a few grammatical/typo errors in
  the paper. This is not an exhaustive list, but: 
  \begin{enumerate}
  \item pg 1 ln 51 “an” is
    not needed. 
  \item Pg 2 ln43: maybe indent this paragraph. 
  \item ln 49 “We find
    that in the case of, Estonian language is associated…” maybe missing
    the word “the”  
  \item ln 54 and 57: its instead of “it’s” 
  \item ln 58 and 59
    “that [the] Estonian…” and “boundaries, men [are] more…” 
  \item Pg. 16 ln
    45-50 The whole paragraph feels a little awkward. 
  \item I also do not know
    what “cv.ee” means.
  \end{enumerate}
\item pg 13 ln 35. “However too little results are
  statistically significant.” Does this imply that they model is not
  useful/good? A little more explanation would be helpful.
\item pg 15 ln 60(?) “, but not precisely estimated.” More explanation on what you mean here would be helpful.
\end{enumerate}

\end{document}

### 2018-07-02 response-to-reviewers.tex
editors request about CEE comparison

@@
 
+\begin{enumerate}
+\item In addition, please elaborate further the comparison of your
+  results with respect to the previous literature about the role of
+  language in Baltic, CEE, and former Soviet Union countries. 
+\item 
 In revising your paper, please make an effort to keep within the
@@
 \debug{nothing else but 7500 words/50 items.}
-
-When submitting your revised manuscript, you will be able to respond to the comments made by the referee(s) in the space provided.
+\item When submitting your revised manuscript, you will be able to respond to the comments made by the referee(s) in the space provided.
 You can use this space to document any changes you make to the original manuscript.
 In order to expedite the processing of the revised manuscript, please be as specific as possible in your response to the referee(s).
+\end{enumerate}
 

### 2018-07-02 paper/ijm.tex
paper, figures, bibliography added

%\documentclass[10pt,a4paper,english]{article}
\documentclass[12pt, a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[margin=2.5cm, top=2.5cm, bottom=2.0cm]{geometry}
\usepackage[english]{babel}
%\usepackage{lmodern}
\usepackage{newtxtext}
\usepackage{newtxmath}
\usepackage[fleqn]{mathtools}
\usepackage{amssymb}
\usepackage{dcolumn}
\usepackage{siunitx}
\usepackage[official]{eurosym}
\setcounter{secnumdepth}{3}

\usepackage[babel=true]{microtype}
\usepackage[hang]{footmisc}
\usepackage[usenames,dvipsnames,svgnames,table]{xcolor}

\usepackage[format=hang, justification=RaggedRight]{caption}
\usepackage[section]{placeins}
\usepackage{booktabs}
\usepackage{comment}
\usepackage{graphicx}
\usepackage{epstopdf}

 \usepackage[author=, status=draft]{fixme}
\usepackage{longtable}
\usepackage{paralist}
\usepackage{rotating}
\usepackage{subfigure}
\usepackage[natbibapa]{apacite}
%\usepackage[authoryear]{natbib}
\usepackage{csquotes}
%modifying the thanks commands
\usepackage{titling}
\usepackage[colorlinks=true, urlcolor=blue, citecolor=black, linkcolor=black]{hyperref}
\usepackage[noabbrev,capitalise]{cleveref}

\thanksfootextra{}{\hfill}
\setlength{\thanksmargin}{1em}
\setlength{\thanksmarkwidth}{0.75em}

%Custom commands
\newcommand{\eur}{\EUR}
\newcommand{\std}[1]{\emph{(#1)}}
\newcommand{\V}{{\ensuremath\checkmark}}
\def\fns{\footnotesize}
\renewcommand*{\vec}[1]{\boldsymbol{#1}}

\def\tenpc{$^{\ast}$}
\def\fivepc{$^{\ast\ast}$}
\def\onepc{$^{\ast\ast\ast}$}
\newcommand{\legend}{\normalsize{Significance levels:\hspace{1em} \tenpc : 10\% \hspace{1em} \fivepc : 5\% \hspace{1em} \onepc : 1\% \normalsize}}
\def\sep{0.5em}
\def\legendTwo{\multicolumn{3}{l}{\footnotesize{Significance levels
			:\hspace{1em} $\dag$ : 10\% \hspace{1em}
			$\ast$ : 5\% \hspace{1em} $\ast\ast$ : 1\% \normalsize}}}
\renewcommand{\thesection}{\arabic{section}.}
\renewcommand{\thesubsection}{\thesection\arabic{subsection}.}

\title{Language Skills in an Ethnically Segmented Labour market:
  Estonia 1989 -- 2012}
%\author{Sven-Kristjan Bormann \and Svetlana Ridala\thanks{Acknowledgements: 
%This research was supported by European Social Fund's Doctoral Studies
%and Internationalisation Program DoRa through Archimedes Foundation, and the Estonian Science Foundation grant 8627.}  
%\and Ott Toomet
%}
\date{}
\begin{document}

%\maketitle
%\begin{center}
%	\textbf{{\large Language Skills in an Ethnically Segmented Labour market:
%				Estonia 1989 -- 2012}} \\
%	{\large Sven-Kristjan Bormann} \\
%	\emph{School of Economics and Business Administration, University of Tartu, Narva mnt. 4, 51007 Tartu, Estonia\\ Tel.: +372 5844 3873\\ Email: \href{mailto:bormann@ut.ee}{bormann@ut.ee}}	\\
%
%	{\large Svetlana Ridala} \\
%	\emph{School of Business and Governance, Tallinn University of Technology,  Akadeemia tee 3, 12618 Tallinn, Estonia\\ Email: \href{
%			mailto:svetlana.ridala@gmail.com}{
%			svetlana.ridala@gmail.com}} \\
%		{\large Ott Toomet}\\
%		\emph{Information School, University of Washington, USA; Email: \href{mailto:otoomet@uw.edu}{otoomet@uw.edu}}
%%	\emph{(Received XX XXXX 20XX; accepted XX XXXX 20XX)}\\
%	\textbf{Corresponding author:} Sven-Kristjan Bormann Email: \href{mailto:bormann@ut.ee}{bormann@ut.ee}
%\end{center}
%\paragraph{Short biographical note:} \hspace{0pt} \\
%Sven-Kristjan Bormann born 28.11.1985, graduated in 2011 from Kiel University, Germany in Economics with specialisation in Quantitative Economics and Computer Science. Since September 2012 PhD-student in Economics at Tartu University, Estonia. \\
%Svetlana Ridala born 28.03.1976, graduated in 2003 from Tallinn Pedagogical University, Estonia master's (scien) degree in mathematics. Since 2009 PhD-student in Economics at Tallinn School of Economics and Business Administration, Estonia.
%\\
%Ott-Siim Toomet born 18.03.1970, graduated in 2004 from Aarhus University, Denmark PhD in Economics. Since 2015 Visiting scholar, Information School, University of Washington.
%
%\paragraph{Research funding}
%This research was supported by European Social Fund's Doctoral Studies
%and Internationalisation Program DoRa through Archimedes Foundation, and the Estonian Science Foundation grant 8627.
%\newpage
%\noindent
{\centering \textbf{Language Skills in an Ethnically Segmented Labour market: Estonia 1989 -- 2012}}
\begin{abstract}

	\noindent	\textbf{Purpose --} The purpose of this paper is to study the relationship between language skills and labour market
outcomes in Estonia, a linguistically divided country where Estonian
is the sole official language.\\
\textbf{Design/methodology/approach --} The authors use the Estonian Labour Force Survey from 1989 to 2012 to study the impact of language skills on unemployment (probability) and wages.\\
\textbf{Findings --} For men, fluency in
Estonian is related to approximately 5 percentage points lower unemployment, but to virtually no income
premium. English skills are associated with a
substantial income premium, but are virtually unrelated to
unemployment. Russian skills are related to higher wages for Estonians,
but the premium is falling over time and Russian is not associated with lower unemployment.	\\
\textbf{Research limitations/implications -- } No casual claims are possible unless a suitable instruments for language skills can be found. Individual characteristics are able to explain a
large part of English returns, so that part of the remaining effect
may also be related to an ability bias. 
The usage of self-reported language skills may introduce measurement errors, which may	decrease in the future, as language test data becomes available.\\	
\textbf{Practical implications --} These results can be explained by simultaneous ethnic and gender
segregation where the high-skilled male labour market is more segregated
than the female labour market, and females are more often working in
communication-intensive jobs.\\
\textbf{Originality/value --} This paper provides a comprehensive overview about the effects of language skills on labour market outcomes for a linguistically divided, low immigration population. In contrast, the existing literature deals mostly with the effects of language skills on the labour market outcomes of immigrants. \\
\end{abstract}
\textbf{Keywords:} language skills, ethnicity, wage gap, unemployment, Estonia \\
\textbf{JEL classification:} J15, J31, J71

\section{Introduction}
\label{sec:introduction}
Numerous studies document that language skills are related to better
labour market outcomes.
Speaking different languages may make workers genuinely more
productive, either by facilitating communication at the workplace
or by making it possible to perform
tasks that require language knowledge.
Enhanced productivity, in turn, should be reflected both in better wage
and in improved employment prospects.

The bulk of the existing literature analyses the effect of knowledge
of the local majority language for immigrants.  It is well known that
language skills are associated with a substantial an income premium
between 5 and 35 percent
\citep{Chiswick1995,bleakley+chin2004,shields+price2002,leslie+lindley2001,chiswick+miller2002,Chiswick2003,Chiswick2010,Chiswick2015, Dustmann2003}.  For
instance, \citet{chiswick2008} argues that ``proficient'' speakers
typically earn about 15\% more than ``not proficient'' speakers.
The effect works largely through improving educational attainment
\citep{bleakley+chin2004,rooth+saarela2007native}.  Language skills are
also complementary to other types of human capital
\citep{chiswick+miller2007}.
Immigrants who are fluent in the local language also suffer
substantially less from unemployment \citep{shields+price2002, Dustmann2003}.

However, in case of less-than-perfect ethnic integration, the ``local''
language in ethnic enclaves may be the minority language instead, in
this way limiting the usefulness of the majority language skills
\citep{chiswick+miller2002,hwang+2010} in particular in context of ethnic segregation and
limited access to upper-end jobs \citep{Toomet2011}.  However, the
existing evidence suggests that the majority language is
an important production factor in the ethnic enclaves as well
\citep{zhou+logan1989, clark+drinkwater2000}.

There is also an increasing body of literature focusing on relationship
between other languages than the local main business language and
income.  These studies generally find
that English is a significant predictor of better income
\citep{Lang2009, Casale2011, Toomet2011, Williams2011, azam+2013EDandCC, isphording2013, beblavy+2016CEPS}.

The role of other languages is
less clear.  It is especially unclear what is the role of
different languages in a multi-lingual economy.  For instance,
\cite{Drinkwater1997} finds
a positive effect for Welsh speaking workers in
Wales but \citet{FrancoisGrin1998}, in contrast,
shows that Italian language skills in Swiss non-Italian speaking
regions are associated with lower wage.  It remains unclear if
this is a true effect or just an omitted variable bias.
It is estimated by \cite{Armstrong2015} that there is a statistically significant premium paid to bilingual people both inside and outside Quebec who speak French as their mother tongue People speaking English as their mother tongue also earn a premium, but it is much smaller outside of Quebec. In some cases it is even statistically not significant.

Few previous studies have provided a comprehensive analysis of a labour
market from the viewpoint of language skills.
\citet{Chiswick1995, chiswick+miller2002, chiswick+miller2007, Bellante1998, Chiswick2010} analyse the effects of dominant language fluency for earnings among immigrants in the United States and
\citet{Chiswick1995}  also analyse it for Canada, Australia and Israel.
\citet{Dustmann2003, shields+price2002} explore of immigrant assimilation into the labour market of the United Kingdom.

\citet{leslie+lindley2001} analyse both employment and income but
focus on a single year and English language only.
\citet{YaoandOurs2015} only analyse the role of Dutch language
on labour market performance in Netherlands.  In case of Estonia,
\citet{Toomet2011} shows that the majority language gives little wage
premium for minority men.  However, he analyses neither women, nor
unemployment.  \citet{Lindemann2013} shows that Estonian fluency
is associated with faster job finding rate while while it does not
explain the lower occupational prestige of Russian speakers.  However,
she only includes recent school graduates in her study.\\

\noindent In this paper, we analyse the relationship between both
majority and minority language skills, and English for both
wage and unemployment.  We analyse Estonia, a linguistically divided
country where a large Russian-speaking community forms almost 30\% of
the population.  We provide long--term trends from the last years
of the planned economy in 1989 till the post-recession time in 2012.

We find that in case of, Estonian language is associated with very
small albeit slowly increasing wage premium over
the years, but only for women.
Russian skills, on the other hand, are clearly related to
higher wage but the relationship is slowly fading. English fluency was
associated with a very large wage premium during the first decade
after the introduction of the market economy, it's importance later
declined, but was still large in 2012.  For
women, the wage premium of each of these languages is roughly equal.
In contrast, the sole language that plays a role in determining
unemployment is Estonian, it's fluency is associated with
approximately 5 percentage points lower unemployment rate.
These results suggest that Estonian labour market is
segmented both along gender and the ethnic boundaries, men
more likely occupied in less communication-intense jobs.
This view is
supported by data from a specifically designed ethnic integration
dataset.

The paper continues as follows: The next section provides a brief
background of Estonian society and labour market. In the following
section we discuss the data and provide some descriptive
statistics. In \cref{sec:method} we describe the econometric
approach, sections \ref{sec:results} and \ref{sec:extensions} present
the results for unemployment probability and wages.

\section{Background: Ethnic Groups and Languages in Estonia}
\label{sec:hist_background}

This section briefly reviews Estonian institutional background,
focusing on the role of ethnic groups and languages.
See \citet{Leping2008} and
\citet{lindemann+saar2011Russian2ndGeneration} for more information.

Before the Second World War, Estonia was ethnically rather
homogeneous, populated almost exclusively by ethnic Estonians. After the War,
the Russian-speaking population grew rapidly through migration and
reached 40\% by 1989.
Such an influx of mainly
Russian-speaking population
led to two \emph{de facto} official languages
by 1970s.
The society was largely divided across language, and the division was
also reflected at workplace \citep{leppik+vihalemm2015JofBaltStud}.

Certain sectors in the economy, such as the army, railways and the
merchant fleet
were dominated by
Russian-speaking workers while more local industries,
such as agriculture and
local public administration,
were dominated by ethnic Estonians.
Both communities followed the media in their own respective language, the
universities taught many subjects in Russian and Estonian,
and service sector was largely bilingual.  However, the bilingualism
was mainly one-sided as the bulk of Estonians spoke Russian, but not
the other way around.  A particular institution in parts of the Soviet
Union was segregated school system, where Russian schools existed along the
schools teaching in the local language.  Hence a common education
system, one of the central integration mechanisms in the developed world,
was (and still largely is) missing in Estonia.
The widening use of Russian also
caused increasing concerns about the future of the Estonian
language, in turn leading to  unwillingness to use Russian by
the ethnic Estonians.  This further strengthened the language-based segregation.

When the central Soviet authority weakened during the late 1980, the
Estonian-speaking community was quick to organize and establish a
nation-state in 1991 where
Estonian was granted status as the sole official language.  The
above-mentioned ``one-sided bilingualism'' slowly started turning
around.  The universities quickly moved to Estonian-only curriculum,
Estonian language become a large-scale compulsory subject in Russian
schools while teaching Russian in Estonian-language schools declined.
Since 2007, all Russian high-schools have to teach part of the
curriculum in Estonian \citep{lindemann+saar2011Russian2ndGeneration}.

According to the report of the Ministry of Education and Research the number
of students, whose mother tongue is not Estonian in basic schools who study in the Estonian language increased from 17,5\% in 2005 to 25,8\% in 2015 due to the growing popularity of immersion
classes (enrolment of classes rose from 7,8\% in 2005 to 17,5\% in 2015).
At the same time the number of students whose mother tongue is not Estonian studying in Estonian basic schools slowly dropped respectively from 9,5\% to  8,3\% \citep{HTM2015}.

The younger generation of ethnic Estonians is
increasingly less fluent in Russian while the opposite is true for ethnic Russians. As
a bi-product of the rapid integration to the West, the importance of English language rose
substantially.

As a result of the economic and political reforms, substantial
disparities in income and education opportunities
emerged
in the early 1990s \citep{Leping2008,
	lindemann+saar2011Russian2ndGeneration}.  The inter-ethnic contacts
are largely limited to superficial encounters at work and in public
space, the close private ties remain limited
\citep{korts2009JofBaltStud}.  Both ethnic groups have only few  are
largely living on their own with limited contacts. The
separate worlds are also reflected in media which may present quite
different and occasionally antagonistic viewpoints depending on the
language \citep{Korts2002}.  Around 25\% of Estonians show little
tolerance for Russian-speaking population (the corresponding figure
for Russians is substantially smaller).  A major issue for this group
is Russians' ability and willingness to communicate in Estonian.

\section{Data}
\label{subsec:ss_var}

\subsection{Variables and Sample Selection}
\label{sec:variables}

Our main analysis relies on the Estonian Labour Force Survey (ELFS),
first conducted in 1995. Until 1999 the survey was an annual
cross-section and later as a quarterly rotating panel.  The number of distinct
individuals is around 4000 annually. However, due to the rotating
structure, we have about 16,000 annual observations.
The reader should keep in mind that while the pre-2000 waves include retrospective income, they do not include retrospective language skills. In this way, the results before
1995 are partly based on extrapolation, assuming individual language
skills did not vary before that date.  In the main analysis, we only
analyse the 2000--2012 time period but we also provide a long-term
picture that includes the
earlier waves from 1989--1999.
We limit ourselves to men and women in the main working age, between 25 and
55 years old.  Further, we only analyse
individuals who are either working or actively looking for a job.

The dataset allows us to control for standard personal
characteristics and human capital variables, such as age, education
and family status.  The central variables in this study are the same
as in \citep{Leping2008}:

In all waves of the survey, respondents are asked about their
\emph{ethnic nationality}.  Typically, individuals have a single ethnic
identity.  The answers are coded as ``Estonian'' or
``non--Estonian''.  As most of those who do not consider themselves
Estonian use Russian as their primary language, we refer to this group
as ``Russians''.

The labour market outcomes include ``last salary on the main job'' and
labour force status (working, unemployed or inactive).

The survey includes self-reported language skills on languages used at
home, and all other languages they understand.  The respondents are
give some guidance in assessing their skills, they can report either
no knowledge, understanding, speaking, writing, or using the
language at home.  We consolidate this information into a dummy, equal to zero
for languages one cannot speak (but potentially understand) and
unity if one speaks, speaks or writes, or uses that language at
home.

For further evidence on ethnic and gender segregation at workplace we use data
from 2008 Integration Monitor Survey.  The survey was conducted by
SaarPoll and focuses on
ethnic relations in Estonia.  The sample size is 1500,
500 of the respondents consider themselves not ethnic Estonians.  We analyse
two questions: ``which is the language of communication at your
workplace?'' and ``which languages do you need at work''.  The first
question addresses the ethnic segregation while the second focuses on
the need of communication.

\subsection{Descriptive Statistics}
\label{sec:descriptive}

The average wages, language skills and other explanatory variables together with the relative frequencies for the period 2000--2012 are presented in \cref{tab:descriptive}. We report the data separately for ethnic nationalities (Estonians and Russians) and language
skills (Estonian, Russian and English).

The table indicates that there are substantial disparities between
Estonians and Russians in wage and unemployment. For instance, the
average monthly salary\footnote{When interpreting the wage,
	one should keep in mind that during the period
	of observation, 2000-2012, the average salary increased by 180\%,
	from \EUR{314} to \EUR{887} monthly.

} of Estonian
males who are not fluent in English is \EUR{532} while for Russians it
is only \EUR{452}. However, we also see that Russians who speak
English earn approximately 40\% more than those who do not (\EUR{452}
versus \EUR{326} monthly for men and \EUR{307} versus \EUR{221} for
women). Estonian skills are associated with lower income premium, 15\%
for men (\EUR{378} versus \EUR{329} monthly) and 30\% for women
(\EUR{260} versus \EUR{203}).  Similarly, English is more closely
associated with income for Estonians than Russian language. In
contrast, unemployment shows a different picture. For ethnic Russians,
it is Estonian language fluency that is more closely associated with
low unemployment, those fluent in Estonian have 11.2 percent
unemployment rate while for those not fluent it is 17.3 percent.  The
corresponding numbers for English are 11.2 and 15.1.  For Estonians,
English is more closely associated with unemployment than Russian:
Estonians fluent in English have in average 5.0 percent unemployment
while those who are not fluent have 8.8 percent.  The difference
related to Russian fluency is only 1.6 percentage points.  However,
these associations are not easy to interpret as English skills are
also related to education, metropolitan residence, and general
ability.

% Table generated by Excel2LaTeX from sheet 'subgroups_by_ethnic_language'
\begin{sidewaystable}[htbp]
	\centering
	\caption{Averages and relative frequencies of selected explanatory
		variables 2000 -- 2012}
	\begin{tabular}{l|rrrr|rrrr}
		\toprule
		&  \multicolumn{4}{c|}{Estonians}   &   \multicolumn{4}{c}{Russians}    \\ \midrule
		Variable                    & RUS 0  & RUS 1  & ENG 0  & ENG 1  & EST 0  & EST 1  & ENG 0  & ENG 1  \\ \midrule
		Wage, men (EUR)             & 543.86 & 537.22 & 438.53 & 738.63 & 401.59 & 489.96 & 388.91 & 660.39 \\
		Wage, women (EUR)           & 345.51 & 376.98 & 301.13 & 488.83 & 238.25 & 338.62 & 266.87 & 435.60 \\
		Unemployment (\%)           & 8.74   & 7.13   & 8.83   & 4.99   & 17.30  & 11.18  & 15.06  & 11.23  \\
		EST 1 (\%)                  & 99.97  & 99.58  & 99.50  & 99.95  & 0.00   & 100.00 & 40.84  & 80.97  \\
		RUS 1 (\%)                  & 0.00   & 100.00 & 77.35  & 82.86  & 99.90  & 99.04  & 99.65  & 98.77  \\
		ENG 1 (\%)                  & 29.47  & 37.16  & 0.00   & 100.00 & 6.70   & 30.69  & 0.00   & 100.00 \\
		College Degree (\%)         & 15.61  & 23.44  & 10.77  & 41.38  & 12.66  & 28.64  & 13.93  & 49.16  \\
		Married (\%)                & 40.09  & 55.71  & 54.11  & 49.53  & 63.54  & 60.78  & 63.38  & 56.99  \\
		Inter-ethnic household (\%) & 1.34   & 5.20   & 4.79   & 3.70   & 5.07   & 19.46  & 11.97  & 12.17  \\
		Age                         & 37.05  & 41.83  & 42.39  & 38.05  & 42.14  & 40.54  & 42.15  & 37.83  \\
		Kids (number)               & 1.08   & 1.00   & 1.00   & 1.00   & 0.71   & 0.76   & 0.75   & 0.68   \\
		\textbf{Residence County }  &        &        &        &        &        &        &        &        \\
		Metropolitan (\%)           & 17.74  & 22.58  & 14.03  & 35.25  & 35.43  & 56.37  & 38.82  & 75.50  \\
		North-East (\%)             & 0.64   & 3.14   & 3.46   & 1.10   & 53.84  & 15.85  & 40.90  & 11.54  \\
		\textbf{Workplace}          &        &        &        &        &        &        &        &        \\
		Tenure (years)              & 6.17   & 7.33   & 7.45   & 6.40   & 8.19   & 7.23   & 8.08   & 5.99   \\
		Public sector (\%)          & 20.03  & 24.81  & 21.79  & 27.55  & 11.62  & 21.67  & 16.28  & 18.14  \\
		Primary sector (\%)         & 14.10  & 9.80   & 13.00  & 6.43   & 9.91   & 7.46   & 8.82   & 8.11   \\
		Secondary sector (\%)       & 31.02  & 27.20  & 32.63  & 19.41  & 47.21  & 29.72  & 41.54  & 24.07  \\
		Tertiary sector (\%)        & 26.17  & 30.12  & 26.52  & 34.46  & 27.17  & 33.96  & 28.37  & 40.96  \\
		\# observations             & 14,943 & 57,270 & 46,525 & 25,688 & 13,805 & 12,830 & 21,773 & 4,862  \\ \bottomrule
	\end{tabular}%
	\label{tab:descriptive}%
	\caption*{\small
		Workplace--related variables are reported for employed individuals,
		other variables for the complete workforce.  Sample is limited to persons
		25-55 year old.\\
		\emph{RUS 0} refers to individuals who cannot speak Russian and
		\emph{RUS 1} to those who can. Analogously for English and
		Estonian.\\
		Primary sector = Agriculture,
		Fishing, Mining \\ Secondary sector = Manufacturing,
		Construction, Electricity \\ Tertiary (service) sector =
		Wholesale, Hotels, Transport, Financial intermediation, Real
		estate \\ Public sector = Public administration, Education,
		Health}
\end{sidewaystable}%

The language fluency variables clearly show that ethnic identity is
closely related to language use: more than 99\% of Estonians report
being fluent in Estonian, the figure for Russians is similar. We
also see that Estonians are better in English than Russians and they
are also better in Russian than vice versa.

Average age reflects the trend of younger generations
being more fluent in English and Estonian while older Estonians being
better in Russian. The family variables follow the
respective age distribution. Not surprisingly, inter-ethnic
households include disproportionally large share of Russian speaking
Estonians and Estonian speaking Russians.
The average experience follows the same pattern as age.
Public sector jobs are associated with disproportionally large share of
Estonian fluency among Russian workers, probably reflecting the formal
language requirements and little room for ethnic segregation in that
sector.

In conclusion, the descriptive analysis suggests that for Russians,
English skills are a more important driver for income than Estonian
skills while the opposite is true for unemployment.  The labour market
outcomes of Estonians are substantially better correlated with English
skills than with Russian skills.

\section{Method}
\label{sec:method}

We analyse the relationship between labour market outcomes and language
skills by ordinary multivariate regression models.
Several related studies use instrumental variables to correct for
omitted variable bias and measurement errors \citep{Chiswick1995, bleakley+chin2004}.
%\ot{more examples here}
We refrain from doing that. Our decision is mainly data driven,
there are no suitable instruments in our data,\footnote{We run an IV
	regression using age--at--immigration to instrument Estonian skills
	for those Russians who were in the country at 1990.  The results are
	not statistically significant at any conventional level.} but it also facilitates
comparison with other studies.For instance,
\citet{azam+2013EDandCC} and \citet{paolo+tansel2015JofDevStud} only report OLS results.

There is also evidence from job language requirements suggesting that
the reduced-form evidence is not too different from the causal effect
\citep{beblavy+2016CEPS}.

\citet{azam+2013EDandCC} and \citet{paolo+tansel2015JofDevStud}, who use proxy variables to control for
individual ability, find these having little influence on the effect
of language skills.

We estimate unemployment probability by linear probability model
(LPM) to avoid unnecessary parametric
assumptions in the corresponding binary choice models.\footnote{The
	results of corresponding probit models are virtually equal to the LPM results.}
Similarly, we estimate the effect of language skills on wage by
OLS. We correct the estimates for the panel data structure by
clustering the standard errors by individuals.

%\fxnote{Add here another index g to denote the group? I used it in other articles, because it was requested and it makes sense}
We estimate the basic model in the following form:
\begin{equation}
	\label{eq:specification}
	\begin{split}
		y_{it} = &\: \alpha_{0} +
		\beta_{RUS} \cdot RUS_{it} +
		\beta_{EST} \cdot EST_{it} +
		\beta_{ENG} \cdot ENG_{it} +
		\\
		& + \vec{\beta}_{X}' \vec{X}_{it} +
		\upsilon_t + \epsilon_{it},
	\end{split}
\end{equation}
where $y_{it}$ is the outcome (either unemployment indicator
or log-wage)
of individual $i$ in wave $t$; $RUS$, $EST$, and $ENG$ are the
language skill descriptors; $\vec{X}$ are the other individual
characteristics, $\upsilon_{t}$ are the year dummies and $\epsilon_{it}$
is the idiosyncratic error term.  As we use panel data, we cluster the
standard errors on individuals.  When analysing the time trend, we
replace the main language effects in~\eqref{eq:specification} by the
\fxnote*{Did we estimate it really that way? At least not in my code.}{corresponding interactions}
\begin{align}
	\label{eq:time_interaction}
	\beta_{RUS,t} \cdot RUS_{it} \cdot \upsilon_{t} +
	\beta_{EST,t} \cdot EST_{it} \cdot \upsilon_{t} +
	\beta_{ENG,t} \cdot ENG_{it} \cdot \upsilon_{t}.
\end{align}

We estimate three models that differ in terms of the number of
control variables. The first one only includes the language skills
and year dummies. The second one also includes individual
characteristics, such as age, education, and county of residence.
Finally, the third model also includes industry, occupation, and other
workplace descriptors.

\section{Results}
\label{sec:results}
\subsection{Unemployment}
\label{subsec:basic_model_unemployment}

The central results for unemployment regressions are given in
\cref{tab:unemployment_estimation_by_sex_and_ethnic}.

The
table clearly indicates that Estonian language skills are associated
with approximately 5 percentage points lower unemployment for both
Russian men and women. We also see that the effect is not radically
influenced by the individual characteristics--for men it is
virtually unchanged while for women the estimate falls by 30\%.

\begin{table}[t!]
	\begin{center}
		\caption{Estimation results for unemployment.}
		\label{tab:unemployment_estimation_by_sex_and_ethnic}
		\begin{tabular}{l D{.}{.}{3} @{\qquad} D{.}{.}{3} @{\qquad\qquad}
				D{.}{.}{3} @{\qquad} D{.}{.}{3}}
			\toprule
			&         \multicolumn{2}{c}{Men}         &        \multicolumn{2}{c}{Women}        \\
			Estonians:      & \multicolumn{1}{c}{1}      & \multicolumn{1}{l}{\hspace{10pt}2} & \multicolumn{1}{c}{1}      & \multicolumn{1}{c}{2}      \\
			Russian         & -0.026^{***}               & -0.010                             & -0.009^{*}                 & 0.010^{**}                 \\
			                & (0.006)                    & (0.006)                            & (0.005)                    & (0.005)                    \\
			English         & -0.047^{***}               & -0.019^{***}                       & -0.024^{***}               & -0.008^{*}                 \\
			                & (0.004)                    & (0.005)                            & (0.004)                    & (0.004)                    \\
			\# obs          & \multicolumn{1}{c}{36,160} & \multicolumn{1}{l}{36,132}         & \multicolumn{1}{l}{36,050} & \multicolumn{1}{c}{36,015} \\
			$R^{2}$         & 0.022                      & 0.047                              & 0.012                      & 0.036                      \\ \hline
			Russians: & \\
			Estonian        & -0.052^{***}               & -0.052^{***}                       & -0.065^{***}               & -0.045^{***}               \\
			                & (0.010)                    & (0.011)                            & (0.009)                    & (0.010)                    \\
			English         & -0.020                     & 0.006                              & -0.015                     & -0.003                     \\
			                & (0.012)                    & (0.014)                            & (0.011)                    & (0.012)                    \\
			\# obs          & \multicolumn{1}{c}{12,946} & \multicolumn{1}{l}{12,942}         & \multicolumn{1}{l}{13,689} & \multicolumn{1}{c}{13,674} \\
			$R^{2}$         & 0.033                      & 0.066                              & 0.023                      & 0.043                      \\ \hline
			year dummies    & \V                         & \V                                 & \V                         & \V                         \\
			indiv. charact. &                            & \V                                 &                            & \V                         \\
			\bottomrule
		\end{tabular}%
		\begin{flushleft}
			\caption*{ \legend \\ Standard errors (clustered on individuals) in parentheses.}
		\end{flushleft}
	\end{center}

\end{table}%

Neither Russian nor English show a comparably strong effect.
Knowledge of Russian is not associated with less unemployment for
Estonian men, and is even related to a slightly higher unemployment
for Estonian women. The latter outcome may be related to omitted
variable bias, Russian knowledge was widespread before 1990 and may
not have been closely associated with any favourable characteristics,
but during the period was increasingly more associated with age.
English skills are related to less unemployment both for Estonian men
and women, but the effect is small.
For Russians, however, Estonian language skills matter. Those who are
fluent in that language have approximately 5 percentage point less
unemployment, the effect changes only a little when controlling for
individual characteristics.  In contrast, the effect of English
fluency is close to zero and not statistically significant.  As in
case of Estonian, individual characteristics change the estimates only
a little.

In summary, these results suggest that the Estonian language is
important for employment prospects. The role of English is
small, and that of Russian is almost non-existent despite a largely
bilingual service sector in the country.

\subsection{Wage Regressions}
\label{subsec:basic_model_wage}

\cref{tab:wage_estimation_by_sex_and_ethnic} presents the main
results.

The table
confirms that wage is positively associated with fluency in other
languages, in particular English. The only remarkable exception is
Estonian language for Russian men where we fail to find any positive
effect for any model. This qualitatively repeats the results of
\citet{Toomet2011}. However, for women we observe a sizeable
positive effect between 12 and 16 percentage points, suggesting that
\citet{Toomet2011} results only describe the male labour market.  The effect decreases somewhat
(from 0.167 to 0.114) when including the individual characteristics
into the model, suggesting that the premium
is partly caused by education and potentially also by unobserved
individual performance. Observable workplace characteristics do not
influence the estimates.

\begin{table}[htbp]
	\begin{center}
		\caption{Estimation results for log wage}
		\label{tab:wage_estimation_by_sex_and_ethnic}
		\begin{tabular}{l | D{.}{.}{3} @{\qquad} D{.}{.}{3} @{\qquad} D{.}{.}{3}  @{\qquad} | @{\qquad}
				D{.}{.}{3} @{\qquad} D{.}{.}{3} @{\qquad} D{.}{.}{3}}
			\toprule
			&                                   \multicolumn{3}{c}{Men}                                    &                              \multicolumn{3}{c}{Women}                               \\
			Estonians          & \multicolumn{1}{c}{1}      & \multicolumn{1}{c}{2}      & \multicolumn{1}{l}{\hspace{10pt}3} & \multicolumn{1}{c}{1}      & \multicolumn{1}{c}{2}      & \multicolumn{1}{c}{3}      \\\midrule
			Russian            & 0.107^{***}                & 0.072^{***}                & 0.054^{***}                        & 0.096^{***}                & 0.041^{***}                & 0.035^{***}                \\
			                   & (0.015)                    & (0.015)                    & (0.014)                            & (0.011)                    & (0.011)                    & (0.010)                    \\
			English            & 0.343^{***}                & 0.162^{***}                & 0.145^{***}                        & 0.311^{***}                & 0.131^{***}                & 0.123^{***}                \\
			                   & (0.013)                    & (0.015)                    & (0.013)                            & (0.010)                    & (0.010)                    & (0.010)                    \\
			\# obs             & \multicolumn{1}{l}{22,290} & \multicolumn{1}{l}{21,785} & \multicolumn{1}{l}{22,274}         & \multicolumn{1}{l}{26,673} & \multicolumn{1}{l}{26,449} & \multicolumn{1}{c}{26,644} \\
			$R^{2}$            & 0.726                      & 0.755                      & 0.790                              & 0.769                      & 0.810                      & 0.830                      \\ \midrule
			Russians:          &  \\
			Estonian           & 0.018                      & -0.014                     & 0.008                              & 0.167^{***}                & 0.114^{***}                & 0.125^{***}                \\
			                   & (0.018)                    & (0.019)                    & (0.018)                            & (0.014)                    & (0.014)                    & (0.014)                    \\
			English            & 0.249^{***}                & 0.155^{***}                & 0.137^{***}                        & 0.223^{***}                & 0.089^{***}                & 0.089^{***}                \\
			                   & (0.026)                    & (0.027)                    & (0.026)                            & (0.021)                    & (0.022)                    & (0.020)                    \\
			\# obs             & \multicolumn{1}{l}{8234}   & \multicolumn{1}{l}{7978}   & \multicolumn{1}{l}{8233}           & \multicolumn{1}{l}{9904}   & \multicolumn{1}{l}{9697}   & \multicolumn{1}{c}{9895}   \\
			$R^{2}$            & 0.731                      & 0.746                      & 0.783                              & 0.794                      & 0.809                      & 0.837                      \\ \hline
			year dummies       & \V                         & \V                         & \V                                 & \V                         & \V                         & \V                         \\
			indiv. charact.    &                            & \V                         & \V                                 &                            & \V                         & \V                         \\
			workplace charact. &                            &                            & \V                                 &                            &                            & \V                         \\ \bottomrule
		\end{tabular}
		\begin{flushleft}
			\caption*{\legend \\ Standard errors (clustered on individuals) in parenthesis}
		\end{flushleft}
	\end{center}
\end{table}

We also see that knowledge of Russian language is associated with a
substantial income premium of 10\% for both Estonian men and women.
The effect approximately halves when introducing
individual controls, suggesting that it is partly related to
education and potentially also to ability. It
falls further when also controlling for the
workplace characteristics, indicating that Estonians' income is
better characterized by available workplace
variables.

English language is associated with a very large
wage premium, up to 34 log points (model 1 for
Estonian men). It falls substantially when introducing the
individual characteristics into the model (model 2), additional
workplace characteristics have little effect.  However, in all
specifications it is
significantly more
important than Russian for Estonians. The estimates are rather
similar for Estonian and Russian men but little lower for Russian
women than for Estonian women.

In conclusion, the wage regressions suggest that English is the main
language that matters for men.  The effect of Russian is minor and
that of Estonian non-existent.  For women, all three languages are
associated with higher wage but Russian to a smaller extent.
This is in a stark contrast to the unemployment regressions, we return to
this question in the discussion.

\section{Extensions}
\label{sec:extensions}

\subsection{A Long-Run View}
\label{sec:long-run}

Here we look at the yearly estimates from 1992 to 2012.
We report those for the model 2.\footnote{The results for other models
	look essentially the same. If we add more variables like in model 3 then the effect size reduces by about five to ten percentage points, but the overall picture remains the same.}

The effect on language fluency on unemployment is shown on Figure~\ref{fig:long-run_unemployment} and on wage on Figure~\ref{fig:long-run_wage}

\begin{figure}[hbtp]
	\centering
	\subfigure[Non-native languages for men]{
		\includegraphics[width=0.45\linewidth]{Figure1a.eps}

		\label{fig:long-run_unemployment_estonian_russian_men}
	}
	\subfigure[Non-native languages for women]{
		\includegraphics[width=0.45\linewidth]{Figure1b.eps}
		\label{fig:long-run_unemployment_estonian_russian_women}
	}
	\subfigure[English for Men]{
		\includegraphics[width=0.45\linewidth]{Figure1c.eps}
		\label{fig:long-run_unemployment_english_men}
	}
	\subfigure[English for Women]{
		\includegraphics[width=0.45\linewidth]{Figure1d.eps}
		\label{fig:long-run_unemployment_english_women}
	}
	\caption{The effect of language fluency on unemployment, 1992--2012}
	\label{fig:long-run_unemployment}
\end{figure}

The results reveal a few interesting facts.  First, the effects are
relatively stable over time, indicating that neither economic
environment nor the data quality have changed rapidly.  Estonian
fluency has been associated with less unemployment for both men and
women since around year 2000, in 1990s it had little effect.  Russian fluency,
in contrast, had never an impact on unemployment probability.

For Estonian men, fluency in English is associated with less unemployment through the whole
period of observation whereas fluency in Russian has no effect.
Only few of the results are statistically significant pointwise though.
For Estonian women, both languages are associated with less
unemployment in the 1990s but not later. The picture is different for
Russians. For men, we cannot see any substantial effect of fluency in English
whereas fluency in Estonian is clearly associated with less unemployment from
the late 1990s on. For women, the picture is mostly similar, just the
effect of Estonian language seems to be somewhat delayed compared to
that for men.

\begin{figure}[hbtp]
	\centering
	\subfigure[Non-native languages for men]{
		\includegraphics[width=0.45\linewidth]{Figure2a.eps}
		\label{fig:long-run_wage_estonian_russian_men}
	}
	\subfigure[Non-native languages for women]{
		\includegraphics[width=0.45\linewidth]{Figure2b.eps}
		\label{fig:long-run_wage_estonian_russian_women}
	}
	\subfigure[English for Men]{
		\includegraphics[width=0.45\linewidth]{Figure2c.eps}
		\label{fig:long-run_wage_english_men}
	}
	\subfigure[English for Women]{
		\includegraphics[width=0.45\linewidth]{Figure2d.eps}
		\label{fig:long-run_wage_english_women}
	}
	\caption{The effect of language fluency on wage, 1992--2012}
	\label{fig:long-run_wage}
\end{figure}

The estimates for wage are rather stable as well. For Estonians, we
see a slight downward trend of the effect of fluency in Russian whereas
that of English becomes important in the late 1990s. For Russians, the
importance of English seems to be sliding across the years, probably
due to the increasing supply of these skills. For men, fluency in Estonian
has never been significantly associated with wage.
The results are remarkably stable over the whole period, stressing
the continuity of the peculiar labour market institutions,
potentially workplace segregation, through the
whole post-communist period. For women, however, we can see
a slight increasing trend, suggesting that there is either less
workplace segregation or other need for the official language for
the jobs commonly taken by women.

\subsection{Does the Effect Differ by Age?}
\label{sec:age_groups}

We also estimate the effects separately by age groups and time in
order to detect potential trends across the age groups and across ethnic groups
(Table~\ref{tab:age_group_trend_russian} and Table~\ref{tab:age_group_trend_estonian}).
We look separately at 4 sub-periods: Early transition period
(1989--1995); First economic growth period (1996--1999);
Economic boom, EU accession (2000--2007); and the recession
(2008--2012).

We use largely the same setup as described in section \ref{sec:method}. The results presented here are derived using the second model.

For ethnic Estonians, knowledge of Russian
(Table~\ref{tab:age_group_trend_estonian}) has become less
important after its peak in the late 1990s. Notably, the
association between wage and language skills are small in the
youngest age groups where the Russian skills are rapidly declining
while it still is strongly related to salary for
older workers. The importance of English language skills fluctuates
and slowly decline through the period, but the men from group (45-55) and young women (25-35) have a growing trend. They gain more from being fluent in English.

The positive impact of Estonian language skills for ethnic Russians
(Table~\ref{tab:age_group_trend_russian}) on earnings seems to
increase over the sample period for women in the young group (25--35)
and the prime age group (36--45).
While no statistically significant
correlation is visible for Russian men, good
Estonian is associated with about 10\% higher salary for Russian women for the boom in the 2000s. For the
recession period, the figure is even close to 12\%. These age
groups are the workers who were in their twenties or younger during
the major political and economic transition in early 1990s. It
suggests that the previously segregated ``Estonian'' and ``Russian''
economy are slowly becoming a more integrated one where ethnic
Russians with a good Estonian command can get well-paid jobs.
In comparison, the estimates for English language fluency shows downward trend for all age groups for men and for women. This is due to the language skills becoming more common among the population.

\begin{table}[htbp]
	\centering
	\caption{The trend over time across the age groups (ethnic Estonians)}
	\begin{tabular}{lccc|cc c}
		\hline\hline
		\multicolumn{7}{l}{Estonian speakers. Dependent variable: log wage}          \\ \hline
		Russian:   &    \multicolumn{3}{c|}{Men}    &   \multicolumn{3}{c}{Women}    \\
		years/age: & 25-35    & 36-45    & 46-55    & 25-35    & 36-45    & 46-55    \\ \midrule
		89-95      & 0.064    & 0.247*** & 0.187*** & 0.117*   & 0.033    & 0.058    \\
		           & (0.069)  & (0.068)  & (0.064)  & (0.053)  & (0.057)  & (0.056)  \\
		96-99      & 0.116**  & 0.161**  & 0.190*** & 0.059*   & 0.114*** & 0.131*** \\
		           & (0.042)  & (0.049)  & (0.054)  & (0.030)  & (0.030)  & (0.033)  \\
		00-07      & 0.054*   & 0.157*** & 0.093*   & 0.041    & 0.022    & 0.042    \\
		           & (0.026)  & (0.037)  & (0.037)  & (0.024)  & (0.021)  & (0.026)  \\
		08-12      & 0.041    & 0.032    & 0.088    & 0.032    & 0.012    & 0.061    \\
		           & (0.032)  & (0.049)  & (0.069)  & (0.030)  & (0.026)  & (0.033)  \\ \hline
		English:   &          &          &          &          &          &          \\
		89-95      & 0.097    & -0.008   & 0.066    & 0.070    & 0.042    & 0.101    \\
		           & (0.064)  & (0.065)  & (0.083)  & (0.049)  & (0.048)  & (0.078)  \\
		96-99      & 0.190*** & 0.276*** & 0.137*   & 0.113*** & 0.101*** & 0.101**  \\
		           & (0.036)  & (0.049)  & (0.054)  & (0.031)  & (0.028)  & (0.038)  \\
		00-07      & 0.166*** & 0.158*** & 0.225*** & 0.159*** & 0.073*** & 0.164*** \\
		           & (0.027)  & (0.036)  & (0.041)  & (0.024)  & (0.021)  & (0.025)  \\
		08-12      & 0.088*   & 0.179*** & 0.236*** & 0.166*** & 0.123*** & 0.145*** \\
		           & (0.039)  & (0.035)  & (0.043)  & (0.037)  & (0.024)  & (0.029)  \\ \bottomrule
	\end{tabular}
	\caption*{ \legend \\ Standard errors (clustered on individuals) in parenthesis}
	\label{tab:age_group_trend_estonian}
\end{table}

\begin{table}[t!]
	\centering
	\caption{The trend over time across the age groups (ethnic
		Russians)}
	\begin{tabular}{lccc|cc c}
		\hline\hline
		\multicolumn{7}{l}{Russian speakers. Dependent variable: log wage}\\
		\midrule
		Estonian:&\multicolumn{3}{c|}{Men} &\multicolumn{3}{c}{Women}\\
		years/age: & 25-35   & 36-45    & 46-55   & 25-35   & 36-45   & 46-55    \\
		\midrule
		89-95      & -0.027  & -0.113   & -0.029  & 0.134*  & 0.073   & -0.039   \\
		           & (0.094) & (0.077)  & (0.079) & (0.056) & (0.052) & (0.059)  \\
		96-99      & -0.023  & 0.001    & 0.049   & 0.049   & 0.034   & 0.071    \\
		           & (0.050) & (0.048)  & (0.060) & (0.045) & (0.035) & (0.037)  \\
		00-07      & -0.038  & -0.034   & 0.042   & 0.099** & 0.089** & 0.122*** \\
		           & (0.038) & (0.049)  & (0.043) & (0.033) & (0.031) & (0.028)  \\
		08-12      & -0.004  & -0.034   & 0.002   & 0.145** & 0.123** & 0.103**  \\
		           & (0.055) & (0.050)  & (0.047) & (0.051) & (0.044) & (0.038)  \\ \midrule
		English:   &         &          &         &         &         &          \\
		89-95      & 0.325*  & 0.362*   & 0.473*  & 0.191   & 0.096   & -0.096   \\
		           & (0.160) & (0.151)  & (0.216) & (0.104) & (0.085) & (0.353)  \\
		96-99      & 0.324** & 0.224*   & 0.129   & 0.241** & 0.048   & 0.281*   \\
		           & (0.101) & (0.103)  & (0.132) & (0.078) & (0.091) & (0.120)  \\
		00-07      & 0.142** & 0.107    & 0.169*  & 0.127** & 0.104   & 0.127*   \\
		           & (0.051) & (0.097)  & (0.072) & (0.049) & (0.060) & (0.057)  \\
		08-12      & 0.140*  & 0.212*** & 0.138   & 0.029   & 0.105*  & 0.040    \\
		           & (0.056) & (0.057)  & (0.072) & (0.049) & (0.050) & (0.055)  \\
		\bottomrule
	\end{tabular}

	\caption*{\legend \\ Standard errors (clustered on individuals) in parenthesis}
	\label{tab:age_group_trend_russian}
\end{table}

We estimate the effect of language skills for unemployment as well for the second model. However too little results are statistically significant. The importance of Estonian language skills was growing during the latest periods and is associated with approximately 7 percentage points lower unemployment for both Russian men and women. The best results are reached for the youngest age groups and for middle age groups.
English skills are related to less unemployment both for Russian men and women. The effect is smaller for Estonian men while for Estonian women all results are insignificant.

\section{Additional Evidence: Estonian Language at Workplace}
\label{sec:segregation_analysis}

Previous results can be explained by two hypotheses: first, Russian--speaking men are working
primarily in Russian language environment while this is not true for
women; and second, Russian-speaking men are working in jobs with
little communication requirements (gender segregation).

To shed some additional light on these hypotheses, we use data
from 2008 Integration Monitor Survey.  We focus on
two questions: ``which is the language of communication at your
workplace?'' and ``which languages do you need at work''.  The first
question addresses the ethnic segregation while the second focuses on
the need of communication.  As very few individuals work in English
environment, we only look for Estonian as the communication language.

\begin{table}[t]
	\centering
	\caption{Language environment and language need at workplace}
	\label{tab:environment_descriptive}
	\begin{tabular}{lrr}
		\toprule
		                                     & men  & women \\
		\midrule
		main communication language Estonian & 15.0 & 22.2  \\
		Need Estonian at work                & 53.0 & 61.9  \\
		Need English  at work                & 26.5 & 11.9  \\
		\midrule
		observations                         & 132  & 134   \\
		\bottomrule
	\end{tabular}
	\begin{flushleft}
		Note: percentage of respondents who respond affirmatively
	\end{flushleft}
\end{table}

Table~\ref{tab:environment_descriptive} shows the proportion of
Russian respondents who use Estonian as the main communication language at work, and
who need Estonian and English at work.  As we see, women are more likely to
use Estonian than men while the opposite is true for English.
Table~\ref{tab:environment_model} presents the regression results when
controlling for other
characteristics, including education and geographic location.

\begin{table}[t]
	\centering
	\caption{Language environment and language need at workplace:
		regression results}
	\label{tab:environment_model}
	\begin{tabular}{l r@{}l r@{}l r@{}l}
		\toprule
		Dependent variable: & \multicolumn{2}{c}{Need Estonian} & \multicolumn{2}{c}{Use Estonian} & \multicolumn{2}{c}{Need English} \\ \midrule
		woman             & 0.262       & **  & 0.162       & *   & -0.045      &   \\
		                  & \std{0.117} &     & \std{0.095} &     & \std{0.192} &   \\
		college education & 0.201       & **  & 0.132       & **  & 0.133       & * \\
		                  & \std{0.083} &     & \std{0.067} &     & \std{0.079} &   \\
		region Tallinn    & -0.276      & *** & -0.463      & *** & 0.036       &   \\
		                  & \std{0.083} &     & \std{0.067} &     & \std{0.080} &   \\
		region North-East & -0.527      & *** & -0.473      & *** & 0.022       &   \\
		                  & \std{0.091} &     & \std{0.074} &     & \std{0.088} &   \\ \midrule
		N obs             & 228         &     & 228         &     & 228         &   \\
		$R^{2}$           & 0.2598      &     & 0.2831      &     & 0.108       &   \\ \bottomrule
	\end{tabular}
	\begin{flushleft}
		Note: control variables include: marital status, education,
		occupation and age.
	\end{flushleft}
\end{table}

The table indicates that Russian women need Estonian 26 percentage
points more at work than Russian men.  The table also suggests that
Russian women are 16 percentage points more likely to be working in
Estonian-speaking environment when controlling for other factors.
Both estimates are statistically significant (at 5\% and 10 \% level
respectively), but not precisely estimated.  We can also see that
college education is associated by much more Estonian need and usage,
but in regions where Russian speakers are concentrated, the capital
Tallinn and the North-East, Estonian is less needed.  In contrast, no
gender difference is visible for English needs.

In summary, this dataset supports the previous hypothesis: Russian women are
working in less segregated environment where Estonian is the main
communication language, and they need Estonian for other reasons as
well.  Gender differences in English usage are not statistically
significant.

Additionally we briefly analysed online job market \href{http://www.cv.ee/english/}{cv.ee}.  We measured all jobs
that required English, Finnish and Russian, and calculated the average education requirement
at these jobs (coded as college/less than college education).  According to the observations,
the jobs that required English, in average, 51\% of college education while those where Finnish is requested, 19\% and Russian is 26\% respectively.

\section{Discussion and Concluding Remarks}
\label{sec:discussion}

We document that different languages are associated in a
different way with unemployment and wage. Our most
intriguing observation is that
Russian men earn virtually no income premium from being fluent in Estonian,
the majority and official language of the country, while the fluency is related to a substantially
lower unemployment rate.
Our analysis supports \citet{YaoandOurs2015} and \citet{Lindemann2013} finding that
the labour market is segmented between ethnic and gender lines.
However, we find that ethnic segregation is less prevalent at the lower end
of the male labour market.
The lower--end labour market, associated with frequent unemployment, is
better integrated and
those who are fluent in the language may expect both less unemployment
and higher wage.  However, men at better paid and more stable jobs
gain little from Estonian.  We
suppose this is because the middle and upper-end labour market is more
segregated and even
those who speak the official language cannot improve their income
much.  This is possibly a type of glass-ceiling effect.  This hypothesis is
supported by \citet{leppik+vihalemm2015JofBaltStud} who show that
Estonian language skills are not associated with improved career
mobility over time.  It is also corroborated with the quantile regression evidence that
Estonian language is related to a positive wage premium only at the
lowest end of income scale \citep{Toomet2011}.  There is also
anecdotal evidence suggesting that offices are
typically manned by ethnic Estonians while production units have a
large share of Russian workers.
One can speculate that this outcome is related to a substantial population share
with negative attitudes toward Russians \citep{korts2009JofBaltStud}.

The ethnic segregation seems to be less of an issue for women.
Unfortunately, neither \citet{Toomet2011} nor
\citet{leppik+vihalemm2015JofBaltStud} analyse men and women
separately.  We suppose that women are more frequently employed in jobs in which they need Estonian
language more, such as working in a direct contact with customers.
We also find evidence that over time Estonian is becoming more
important in the female labour market.  Unfortunately, the current data
does not let us to assess whether is due to decreasing segregation, or
economy--wide rise of Estonian language.  No such trend is visible for men.

The other results are more in line with other studies.
English language is related to a substantial income premium but
virtually to no effect on unemployment.  This is similar to findings by
\citet{ginsburgh+prieto-rodriguez2011ILRR} and
\citet{beblavy+2016CEPS} who show that English is more important at better paid
jobs.  In contrast, our outcomes suggest that English has little use
at low-paid, unstable jobs \citep{Toomet2011}.

Note also that for
English, we are able to explain a substantial part of the raw effect
by individual characteristics, suggesting that the true causal effect
may be smaller than our estimates.

The study has a number of limitations.  Although we believe that our
estimates are good indicators of a causal relationship, we cannot make
such claim unless a suitable instruments for language skills can be
found.  In particular, as individual characteristics are able to explain a
large part of English returns, we suppose part of the remaining effect
may also related to an ability bias.  Another weak point in the current
data, although it is
standard in the literature, is using the self-reported language
skills.  As language test data becomes available, we may be able to
decrease the measurement error in the future.

\bibliographystyle{apacite}
\bibliography{literatur}

\end{document}

### 2018-07-02 response-to-reviewers.tex
more comments to reviewers

@@
 \usepackage{setspace}
+\usepackage[dvipsnames]{xcolor}
 \usepackage{xspace}
@@
 
-\newcommand{\debug}[1]{\marginpar{\small\raggedright\begin{spacing}{1} #1
+\newcommand{\debug}[1]{\marginpar{\small\raggedright\begin{spacing}{1}
+      \color{BrickRed} #1
 \end{spacing}
@@
 \begin{enumerate}
-\item 1. The paper aims to contribute to an already large
+\item The paper aims to contribute to an already large
   literature. The recent literature in this field focus on the
@@
   knowledge on the labour market effects of language skills.
-\item My main concern is with some of their wage results. I find it
+
+  \begin{response}
+    No response needed here.
+  \end{response}
+\item 
+  \debug{OT: should refer to Toomet (2011), maybe there are more
+    papers.  The effect is mainly coming from Tallinn and somewhat
+    from education too, either do a table that disentangles these, or
+    a plot (violin plot?) by group.}
+  My main concern is with some of their wage results. I find it
   puzzling that they don’t find a wage premium for Russian men who
@@
   reasons that lead to this finding.
-\item The paper needs to be checked for spelling and grammar
+\item
+  \debug{OT: I'll do a rewrite after changes are made, hope it's
+    sufficient.} 
+  The paper needs to be checked for spelling and grammar
   errors. There are a number of typos and errors, which should be
@@
 \item 
-- The sample size for different specification of the same analysis
+  \debug{ot: let's make it equal (i.e. remove all observations with
+    any of the variables missing.  Add a footnote that when we
+    included all the variables, we still got the same results.}
+  The sample size for different specification of the same analysis
 should be the equal. Otherwise it is difficult to conclude whether the
@@
   literature. 
-\item In the Discussion and Concluding Remarks section they state that
+\item 
+\debug{OT: seems like I have to address this.}
+In the Discussion and Concluding Remarks section they state that
   “The lower end labour market, associated with frequent unemployment,

### 2018-07-02 response-to-reviewers.tex
chiswick given names fixed in .bib

@@
 \item
-- Page 1: To cite Chiswick you are using different versions
+  \debug{ot: this was because of both 'B. Chiswick' and
+    'B. R. Chiswick' in the bibtex file, and bibtex wanted to
+    distinguish between these two guys.}
+ Page 1: To cite Chiswick you are using different versions
 (B. Chiswick and B. R. Chiswick).
@@
 \begin{response}
-  OT: let's make all the technical changes and thereafter I'll go over the
-  language.  Maybe we'll need a language editor but hope we don't.
+  We have corrected the different references.
 \end{response}

### 2018-07-03 paper/ijm.tex
Update ijm.tex
Chapter 4 model (1)

@@
 	\begin{split}
-		y_{it} = &\: \alpha_{0} +
-		\beta_{RUS} \cdot RUS_{it} +
-		\beta_{EST} \cdot EST_{it} +
-		\beta_{ENG} \cdot ENG_{it} +
-		\\
-		& + \vec{\beta}_{X}' \vec{X}_{it} +
-		\upsilon_t + \epsilon_{it},
+		y_{it} ^{g} = &\: 
+		\\alpha_{g}{}' X_{it}^{g}+
+		\\& + \vec{beta}^{g}{}' \cdot \vec{L}_{it}^{g} +
+		\eta_{i}^{g} +
+		\upsilon_t^{g} + \epsilon_{it}^{g},
 	\end{split}
 \end{equation}
-where $y_{it}$ is the outcome (either unemployment indicator
-or log-wage)
-of individual $i$ in wave $t$; $RUS$, $EST$, and $ENG$ are the
-language skill descriptors; $\vec{X}$ are the other individual
-characteristics, $\upsilon_{t}$ are the year dummies and $\epsilon_{it}$
-is the idiosyncratic error term.  As we use panel data, we cluster the
+where $y_{it}^{g}$ is the outcome (either unemployment indicator
+or logarithm of net monthly wage)
+of individual $i$ in wave $t$ from ethnic group g; $\vec{X}^{g}$ are the other individual
+characteristics for both groups; $L$ is the vector of
+language skill descriptors, $eta_{i}^{g}$ is the individual-specific effect, $\upsilon_{t}^{g}$ are the year dummies and $\epsilon_{it}^{g}$
+is the idiosyncratic error term. We denote the groups g by E (Estonian) and R (Russian).
+As we use panel data, we cluster the
 standard errors on individuals.  When analysing the time trend, we

### 2018-07-03 paper/ijm.tex
Update ijm.tex
Small changes in Chapter 4 model (1) and more detail description of model 2

@@
 		y_{it} ^{g} = &\: 
-		\\alpha_{g}{}' X_{it}^{g}+
+		\\alpha^{g}{}' X_{it}^{g}+
 		\\& + \vec{beta}^{g}{}' \cdot \vec{L}_{it}^{g} +
 		\eta_{i}^{g} +
-		\upsilon_t^{g} + \epsilon_{it}^{g},
+		\upsilon_{t}^{g} + \epsilon_{it}^{g},
 	\end{split}
@@
 and year dummies. The second one also includes individual
-characteristics, such as age, education, and county of residence.
-Finally, the third model also includes industry, occupation, and other
+characteristics (age, education) and family descriptors (marital status, having kids up to 17 years old) and county of residence.
+Finally, the third model additionally includes industry, occupation, and other
 workplace descriptors.

### 2018-07-03 paper/ijm.tex
Update ijm.tex
Referee 1 page 2,3 small changes

@@
 unemployment is Estonian, it's fluency is associated with
-approximately 5 percentage points lower unemployment rate.
+approximately 5 percentage points lower probability of being unemployed.
 These results suggest that Estonian labour market is
@@
 According to the report of the Ministry of Education and Research the number
-of students, whose mother tongue is not Estonian in basic schools who study in the Estonian language increased from 17,5\% in 2005 to 25,8\% in 2015 due to the growing popularity of immersion
-classes (enrolment of classes rose from 7,8\% in 2005 to 17,5\% in 2015).
-At the same time the number of students whose mother tongue is not Estonian studying in Estonian basic schools slowly dropped respectively from 9,5\% to  8,3\% \citep{HTM2015}.
+of students, whose mother tongue is not Estonian in basic schools who study in the Estonian language increased from 17.5\% in 2005 to 25.8\% in 2015 due to the growing popularity of immersion
+classes (enrolment of classes rose from 7.8\% in 2005 to 17.5\% in 2015).
+At the same time the number of students whose mother tongue is not Estonian studying in Estonian basic schools slowly dropped respectively from 9.5\% to  8.3\% \citep{HTM2015}.
 

### 2018-07-03 response-to-reviewers.tex
Update response-to-reviewers.tex

@@
     a plot (violin plot?) by group.}
+  \debug{SKB: I did the estimation separated by regions, but not 
+  separated by regions and educational level. We could add the regional
+  breakdown in the appendix or add it as another extension to chapter 6.}
   My main concern is with some of their wage results. I find it
@@
 \begin{enumerate}
-\item - The description of the estimation models in Chapter 4 should
+\item- The description of the estimation models in Chapter 4 should
   be more detailed. Please describe more specifically what exactly you
@@
   estimating the time trend is very short.
+  \debug{SKB: Svetlana modified the equations a bit. I added another table,
+  which summarises the models.}
 \item - The tables and figures should have notes that explain in more

### 2018-07-03 response-to-reviewers.tex
Made a couple of minor changes to the text.

@@
 \usepackage{xspace}
-\input{isomath}
+\usepackage{csquotes}
+ \usepackage[author=, status=draft]{fixme}
+\usepackage{isomath} %SKB: Changed from \input{isomath} to \usepackage{isomath}
+\newcommand{\skb}[1]{
+	\begin{quotation}
+		\color{Blue} SKB: #1	
+	\end{quotation}
 
+}
 \newcommand{\debug}[1]{\marginpar{\small\raggedright\begin{spacing}{1}
@@
 \begin{document}
-
+	\section*{General remarks} % which are too long for the margin... .
+\begin{itemize}
+	\item A rather general remark, I added the occupation variable to the estimations, but did not redo the graphs or tables.
+The results should not differ much.
+It will show up in the tables with all coefficients.
+\item SKB: The column separating lines in Table 4 have some \enquote{holes}.
+We might have to switch from the dcolumn package to the siunitx package to fix these issues.
+I did not manage yet fix these issues.
+The referees did not complain, but it still looks ugly or strange.
+\end{itemize}
 \section*{Response to the referees}
@@
   variables, the sample period and the age restriction applied.
+  \debug{SKB: I added this information to the tables and the figures. The descriptions might need some polishing still.}
 \item 
@@
     included all the variables, we still got the same results.}
+\debug{SKB: I estimated the models, but did not create yet the tables.}
   The sample size for different specification of the same analysis
@@
 models.
+\debug{SKB: Will add them after I figured out how to present the results nicely formatted.
+It boils down to finding the right options for the \enquote{estout} or the \enquote{outtex/outreg} user provided package in Stata.
+I could do the formatting in Excel myself, but I prefer the Stata solution.
+}
 \item 
@@
 across the different tables. 
+\debug{SKB: Fixed. Changed obs to observations}
 \item
@@
 being unemployed is reduced.
+\debug{SKB: Got fixed by Svetlana I think.}
 \item 
 - Page 3, lines 46-50: You are using a comma as the decimal separator, but in all your tables you are using a point. Please use a point everywhere. 
+\debug{SKB: Fixed by someone.}
 \end{enumerate}
@@
 Could the models be run using the same sample for each column?
+\debug{These typos got fixed.}
 \end{enumerate}
@@
     what “cv.ee” means.
+    \debug{SKB: We should set a link or further explanations}
   \end{enumerate}

### 2018-07-03 paper/ijm.tex
Made a couple of minor changes to the text.

@@
 
- \usepackage[author=, status=draft]{fixme}
+ \usepackage[author=, status=final]{fixme}
+  \usepackage[final]{changes} %Manually track changes
+ \definechangesauthor{SKB}
 \usepackage{longtable}
@@
 			$\ast$ : 5\% \hspace{1em} $\ast\ast$ : 1\% \normalsize}}}
+%SKB: Added for documenting the tables and figures
+\newcommand{\modelTwo}{age, age\textsuperscript{2}, education, being married, number of children, inter-ethnic household}
+\newcommand{\modelThree}{\modelTwo, industry, occupation ,ownership type of company, number of workers in company, working in the public sector, experience in company}
+\newcommand{\modelThreeAdd}{industry, occupation ,ownership type of company, number of workers in company, working in the public sector, experience in company}	
+\newcommand{\restrictions}{The sample period is from year 2000 to year 2012. Sample is limited to persons
+	25-55 year old.}
+\newcommand{\agerestrictions}{Sample is limited to persons
+	25-55 year old.}
+%Modified section numbering	
 \renewcommand{\thesection}{\arabic{section}.}
@@
 	\begin{split}
-		y_{it} ^{g} = &\: 
-		\\alpha^{g}{}' X_{it}^{g}+
-		\\& + \vec{beta}^{g}{}' \cdot \vec{L}_{it}^{g} +
+		y_{it} ^{g} = &\: alpha^{g}{}' X_{it}^{g} + \vec{beta}^{g}{}' \cdot \vec{L}_{it}^{g} +
 		\eta_{i}^{g} +
@@
 replace the main language effects in~\eqref{eq:specification} by the
-\fxnote*{Did we estimate it really that way? At least not in my code.}{corresponding interactions}
+\fxnote*{Did we estimate it really that way?
+At least not in my code.
+I found the code for estimations with these interactions, but I don't remember that I used these interactions for the tables.}{corresponding interactions}
 \begin{align}
@@
 workplace descriptors.
+\Cref{tab:models} summarises this description of the models.
+%SKB: This table should have been in the article at some point, but I must have removed it. I use in my Quantile Regression article
+\begin{table}[hbtp]
+	\centering
+	\caption{Groups of explanatory variables included in different models}
+	\label{tab:models}
+	\begin{tabular}{r|ccc}
+		\toprule
+		& Model 1 & Model 2 & Model 3 \\ \midrule
+		year dummies       & \V      & \V      & \V      \\
+		indiv. charact.    &         & \V      & \V      \\
+		workplace charact. &         &         & \V      \\ 
+		\bottomrule
+	\end{tabular}
+\end{table}
 
@@
 			                & (0.004)                    & (0.005)                            & (0.004)                    & (0.004)                    \\
-			\# obs          & \multicolumn{1}{c}{36,160} & \multicolumn{1}{l}{36,132}         & \multicolumn{1}{l}{36,050} & \multicolumn{1}{c}{36,015} \\
+			\# observations          & \multicolumn{1}{c}{36,160} & \multicolumn{1}{l}{36,132}         & \multicolumn{1}{l}{36,050} & \multicolumn{1}{c}{36,015} \\
 			$R^{2}$         & 0.022                      & 0.047                              & 0.012                      & 0.036                      \\ \hline
@@
 			                & (0.012)                    & (0.014)                            & (0.011)                    & (0.012)                    \\
-			\# obs          & \multicolumn{1}{c}{12,946} & \multicolumn{1}{l}{12,942}         & \multicolumn{1}{l}{13,689} & \multicolumn{1}{c}{13,674} \\
+			\# observations          & \multicolumn{1}{c}{12,946} & \multicolumn{1}{l}{12,942}         & \multicolumn{1}{l}{13,689} & \multicolumn{1}{c}{13,674} \\
 			$R^{2}$         & 0.033                      & 0.066                              & 0.023                      & 0.043                      \\ \hline
@@
 		\begin{flushleft}
-			\caption*{ \legend \\ Standard errors (clustered on individuals) in parentheses.}
+			\caption*{ \legend \\ Standard errors (clustered on individuals) in parentheses.\\  Individual characteristics are \modelTwo. \\ \restrictions}
 		\end{flushleft}
@@
 			                   & (0.013)                    & (0.015)                    & (0.013)                            & (0.010)                    & (0.010)                    & (0.010)                    \\
-			\# obs             & \multicolumn{1}{l}{22,290} & \multicolumn{1}{l}{21,785} & \multicolumn{1}{l}{22,274}         & \multicolumn{1}{l}{26,673} & \multicolumn{1}{l}{26,449} & \multicolumn{1}{c}{26,644} \\
+			\# observations             & \multicolumn{1}{l}{22,290} & \multicolumn{1}{l}{22,274} & \multicolumn{1}{l}{21,785}         & \multicolumn{1}{l}{26,673} & \multicolumn{1}{l}{26,644} & \multicolumn{1}{c}{26,449} \\
 			$R^{2}$            & 0.726                      & 0.755                      & 0.790                              & 0.769                      & 0.810                      & 0.830                      \\ \midrule
@@
 			                   & (0.026)                    & (0.027)                    & (0.026)                            & (0.021)                    & (0.022)                    & (0.020)                    \\
-			\# obs             & \multicolumn{1}{l}{8234}   & \multicolumn{1}{l}{7978}   & \multicolumn{1}{l}{8233}           & \multicolumn{1}{l}{9904}   & \multicolumn{1}{l}{9697}   & \multicolumn{1}{c}{9895}   \\
+			\# observations             & \multicolumn{1}{l}{8234}   & \multicolumn{1}{l}{8233}   & \multicolumn{1}{l}{7978}           & \multicolumn{1}{l}{9904}   & \multicolumn{1}{l}{9895}   & \multicolumn{1}{c}{9697}   \\
 			$R^{2}$            & 0.731                      & 0.746                      & 0.783                              & 0.794                      & 0.809                      & 0.837                      \\ \hline
@@
 		\begin{flushleft}
-			\caption*{\legend \\ Standard errors (clustered on individuals) in parenthesis}
+			\caption*{\legend \\ Standard errors (clustered on individuals) in parenthesis \\ Individual characteristics are \modelTwo. \\ Workplace characteristics are \modelThreeAdd. \\ \restrictions}
 		\end{flushleft}
@@
 	}
-	\caption{The effect of language fluency on unemployment, 1992--2012}
+	\caption{The effect of language fluency on unemployment, 1992--2012. \\ Control variables are \modelTwo. \agerestrictions }
 	\label{fig:long-run_unemployment}
@@
 	}
-	\caption{The effect of language fluency on wage, 1992--2012}
+	\caption{The effect of language fluency on wage, 1992--2012. \\ Control variables are \modelTwo. \agerestrictions}
 	\label{fig:long-run_wage}
@@
 		                  & \std{0.091} &     & \std{0.074} &     & \std{0.088} &   \\ \midrule
-		N obs             & 228         &     & 228         &     & 228         &   \\
+		\# observations             & 228         &     & 228         &     & 228         &   \\
 		$R^{2}$           & 0.2598      &     & 0.2831      &     & 0.108       &   \\ \bottomrule
@@
 
+\appendix
+\input{appendix.tex}
+
 \end{document}

### 2018-07-04 paper/ijm.tex
Update ijm.tex
Small correction eq 1 chapter 4. \ added
Update ijm.tex
Changed text p.13

@@
 	\begin{split}
-		y_{it} ^{g} = &\: alpha^{g}{}' X_{it}^{g} + \vec{beta}^{g}{}' \cdot \vec{L}_{it}^{g} +
+		y_{it} ^{g} = &\: \alpha^{g}{}' X_{it}^{g} + \vec{\beta}^{g}{}' \cdot \vec{L}_{it}^{g} +
 		\eta_{i}^{g} +
@@
 
-We estimate the effect of language skills for unemployment as well for the second model.
-However too little results are statistically significant.
-The importance of Estonian language skills was growing during the latest periods and is associated with approximately 7 percentage points lower unemployment for both Russian men and women.
-The best results are reached for the youngest age groups and for middle age groups.
-English skills are related to less unemployment both for Russian men and women. The effect is smaller for Estonian men while for Estonian women all results are insignificant.
+We estimate the effect of language skills for unemployment for the age groups and ethnical groups as well for the second model.
+However dividing the results for four sub-periods does not detect the trends across the age groups for those periods due to only some of the results are statistically significant.
+The exception is the group of young (25-34) Estonian men for whom English language is clearly decreases the probability of being unemployment during the time.
+Notwithstanding importance of English is small for other groups.
+Estimates for the longer time period shows the importance of Estonian language for all age groups for ethnical Russian and have even higher impact for the young women.
 

### 2018-07-04 paper/ijm.tex
Prepared minor changes

--- 2018-07-03 paper/ijm.tex
@@
 		\caption{Estimation results for unemployment.}
-		\label{tab:unemployment_estimation_by_sex_and_ethnic}
+		\label{tab:unemployment_estimation_by_sex_and_ethnic_same_sample} %SKB 04.07.2018 14:22:Not yet updated only prepared
 		\begin{tabular}{l D{.}{.}{3} @{\qquad} D{.}{.}{3} @{\qquad\qquad}
@@
 		\caption{Estimation results for log wage}
-		\label{tab:wage_estimation_by_sex_and_ethnic}
+		\label{tab:wage_estimation_by_sex_and_ethnic_same_sample} %SKB 04.07.2018 14:22:Not yet updated only prepared
 		\begin{tabular}{l | D{.}{.}{3} @{\qquad} D{.}{.}{3} @{\qquad} D{.}{.}{3}  @{\qquad} | @{\qquad}

### 2018-07-04 response-to-reviewers.tex
Changed the tables to have the same number of observations. Corrected the text for adding occupation to Model 3.

@@
     included all the variables, we still got the same results.}
-\debug{SKB: I estimated the models, but did not create yet the tables.}
+\debug{SKB: I estimated the models and updated tht.}
   The sample size for different specification of the same analysis
@@
   useful/good? A little more explanation would be helpful.
+  \debug{SR: For more explanations I reestimated Model2 for unemployment for the age groups.
+I made new folder in dropbox:Tabels4_5. Here are Estimates for the age groups for 4 sub-periods, for time period 2000-2012 and for time period 1989-2012. I also made some changes in the text.}
 \item pg 15 ln 60(?) “, but not precisely estimated.” More explanation on what you mean here would be helpful.

### 2018-07-04 paper/ijm.tex
Changed the tables to have the same number of observations. Corrected the text for adding occupation to Model 3.

@@
 The central results for unemployment regressions are given in
-\cref{tab:unemployment_estimation_by_sex_and_ethnic}.
+\cref{tab:unemployment_estimation_by_sex_and_ethnic_same_sample}.
+\footnote{This table is restricted to have the same number of observations across all models requested by reviewer.
+The unrestricted table is in the appendix \cref{tab:unemployment_estimation_by_sex_and_ethnic}.}
 
@@
 			Estonians:      & \multicolumn{1}{c}{1}      & \multicolumn{1}{l}{\hspace{10pt}2} & \multicolumn{1}{c}{1}      & \multicolumn{1}{c}{2}      \\
-			Russian         & -0.026^{***}               & -0.010                             & -0.009^{*}                 & 0.010^{**}                 \\
+			Russian         & -0.026^{***}               & -0.001                             & -0.009^{*}                 & 0.010^{**}                 \\
 			                & (0.006)                    & (0.006)                            & (0.005)                    & (0.005)                    \\
@@
 			                & (0.004)                    & (0.005)                            & (0.004)                    & (0.004)                    \\
-			\# observations          & \multicolumn{1}{c}{36,160} & \multicolumn{1}{l}{36,132}         & \multicolumn{1}{l}{36,050} & \multicolumn{1}{c}{36,015} \\
+			\# observations          & \multicolumn{1}{c}{36,132} & \multicolumn{1}{l}{36,132}         & \multicolumn{1}{l}{36,015} & \multicolumn{1}{c}{36,015} \\
 			$R^{2}$         & 0.022                      & 0.047                              & 0.012                      & 0.036                      \\ \hline
@@
 			                & (0.010)                    & (0.011)                            & (0.009)                    & (0.010)                    \\
-			English         & -0.020                     & 0.006                              & -0.015                     & -0.003                     \\
+			English         & -0.020                     & 0.006                              & -0.014                     & -0.003                     \\
 			                & (0.012)                    & (0.014)                            & (0.011)                    & (0.012)                    \\
-			\# observations          & \multicolumn{1}{c}{12,946} & \multicolumn{1}{l}{12,942}         & \multicolumn{1}{l}{13,689} & \multicolumn{1}{c}{13,674} \\
+			\# observations          & \multicolumn{1}{c}{12,942} & \multicolumn{1}{l}{12,942}         & \multicolumn{1}{l}{13,674} & \multicolumn{1}{c}{13,674} \\
 			$R^{2}$         & 0.033                      & 0.066                              & 0.023                      & 0.043                      \\ \hline
@@
 \subsection{Wage Regressions}
+%SKB: Adding occupation to Model 3 reduces the effects drastically. Beforehand I somehow forgot to add it to the estimation. Now occupation is included as it should have been in the first place.
 \label{subsec:basic_model_wage}
 
-\cref{tab:wage_estimation_by_sex_and_ethnic} presents the main
-results.
+\cref{tab:wage_estimation_by_sex_and_ethnic_same_sample} presents the main
+results.\footnote{This table is restricted to have the same number of observations across all models requested by reviewer.
+The unrestricted table is in the appendix \cref{tab:wage_estimation_by_sex_and_ethnic}.}
 
@@
 \citet{Toomet2011}. However, for women we observe a sizeable
-positive effect between 12 and 16 percentage points, suggesting that
+positive effect between 6 and 16 percentage points, suggesting that
 \citet{Toomet2011} results only describe the male labour market.  The effect decreases somewhat
@@
 is partly caused by education and potentially also by unobserved
-individual performance. Observable workplace characteristics do not
-influence the estimates.
+individual performance. Adding further observable workplace characteristics nearly halves the effects 
+(when accounting not only for the industry but also the occupation) %SKB: Might remove this sentence
+.
 
@@
 		\label{tab:wage_estimation_by_sex_and_ethnic_same_sample} %SKB 04.07.2018 14:22:Not yet updated only prepared
+		%Accounting for occupation in model reduced the Estonian coefficient for women drastically (from 0.12 down 0.06)!
+		%For other groups it is less
 		\begin{tabular}{l | D{.}{.}{3} @{\qquad} D{.}{.}{3} @{\qquad} D{.}{.}{3}  @{\qquad} | @{\qquad}
@@
 			Estonians          & \multicolumn{1}{c}{1}      & \multicolumn{1}{c}{2}      & \multicolumn{1}{l}{\hspace{10pt}3} & \multicolumn{1}{c}{1}      & \multicolumn{1}{c}{2}      & \multicolumn{1}{c}{3}      \\\midrule
-			Russian            & 0.107^{***}                & 0.072^{***}                & 0.054^{***}                        & 0.096^{***}                & 0.041^{***}                & 0.035^{***}                \\
-			                   & (0.015)                    & (0.015)                    & (0.014)                            & (0.011)                    & (0.011)                    & (0.010)                    \\
-			English            & 0.343^{***}                & 0.162^{***}                & 0.145^{***}                        & 0.311^{***}                & 0.131^{***}                & 0.123^{***}                \\
-			                   & (0.013)                    & (0.015)                    & (0.013)                            & (0.010)                    & (0.010)                    & (0.010)                    \\
-			\# observations             & \multicolumn{1}{l}{22,290} & \multicolumn{1}{l}{22,274} & \multicolumn{1}{l}{21,785}         & \multicolumn{1}{l}{26,673} & \multicolumn{1}{l}{26,644} & \multicolumn{1}{c}{26,449} \\
-			$R^{2}$            & 0.726                      & 0.755                      & 0.790                              & 0.769                      & 0.810                      & 0.830                      \\ \midrule
+			Russian            & 0.112^{***}                & 0.078^{***}                & 0.043^{***}                        & 0.094^{***}                & 0.039^{***}                & 0.016^{*}                \\
+			                   & (0.015)                    & (0.015)                    & (0.014)                            & (0.011)                    & (0.011)                    & (0.009)                    \\
+			English            & 0.343^{***}                & 0.158^{***}                & 0.108^{***}                        & 0.311^{***}                & 0.130^{***}                & 0.075^{***}                \\
+			                   & (0.013)                    & (0.015)                    & (0.013)                            & (0.010)                    & (0.010)                    & (0.009)                    \\
+			\# observations             & \multicolumn{1}{l}{21,785} & \multicolumn{1}{l}{21,785} & \multicolumn{1}{l}{21,785}         & \multicolumn{1}{l}{26,673} & \multicolumn{1}{l}{26,644} & \multicolumn{1}{c}{26,449} \\
+			$R^{2}$            & 0.730                      & 0.760                      & 0.801                              & 0.769                      & 0.810                      & 0.830                      \\ \midrule
 			Russians:          &  \\
-			Estonian           & 0.018                      & -0.014                     & 0.008                              & 0.167^{***}                & 0.114^{***}                & 0.125^{***}                \\
-			                   & (0.018)                    & (0.019)                    & (0.018)                            & (0.014)                    & (0.014)                    & (0.014)                    \\
-			English            & 0.249^{***}                & 0.155^{***}                & 0.137^{***}                        & 0.223^{***}                & 0.089^{***}                & 0.089^{***}                \\
-			                   & (0.026)                    & (0.027)                    & (0.026)                            & (0.021)                    & (0.022)                    & (0.020)                    \\
-			\# observations             & \multicolumn{1}{l}{8234}   & \multicolumn{1}{l}{8233}   & \multicolumn{1}{l}{7978}           & \multicolumn{1}{l}{9904}   & \multicolumn{1}{l}{9895}   & \multicolumn{1}{c}{9697}   \\
-			$R^{2}$            & 0.731                      & 0.746                      & 0.783                              & 0.794                      & 0.809                      & 0.837                      \\ \hline
+			Estonian           & 0.020                      & -0.013                     & -0.009                              & 0.167^{***}                & 0.114^{***}                & 0.066^{***}                \\
+			                   & (0.018)                    & (0.019)                    & (0.018)                            & (0.014)                    & (0.014)                    & (0.013)                    \\
+			English            & 0.248^{***}                & 0.152^{***}                & 0.103^{***}                        & 0.223^{***}                & 0.089^{***}                & 0.054^{***}                \\
+			                   & (0.026)                    & (0.027)                    & (0.024)                            & (0.021)                    & (0.022)                    & (0.018)                    \\
+			\# observations             & \multicolumn{1}{l}{7978}   & \multicolumn{1}{l}{7978}   & \multicolumn{1}{l}{7978}           & \multicolumn{1}{l}{9904}   & \multicolumn{1}{l}{9895}   & \multicolumn{1}{c}{9697}   \\
+			$R^{2}$            & 0.731                      & 0.746                      & 0.794                              & 0.794                      & 0.809                      & 0.854                      \\ \hline
 			year dummies       & \V                         & \V                         & \V                                 & \V                         & \V                         & \V                         \\

### 2018-07-04 code/plots.R
response-to-reviewers: better margins

@@ -1,0 +1,29 @@
+
+loadData <- function() {
+   library(data.table)
+   load("~/tyyq/andmebaasiq/ETU/mergeELFS/ETU_panel.Rdat")
+   setDT(panel)
+   panel
+}
+
+maleWage <- function(data) {
+   library(magrittr)
+   library(ggplot2)
+   subset <- data[year(date) == 2012 & sex == 1 & !is.na(wage) & nonEst, .(wage, estLevel, residenceCounty, edu)][
+      wage > 0, ][
+    , metro := residenceCounty == 37][
+    , et := estLevel %in% c("1", "2", "home")]
+   plain <- subset %>%
+      ggplot(aes(x=et, y=log(wage))) +
+      geom_violin(aes(col=et), size=2) +
+      stat_summary(fun.y=mean, geom="point")
+   metro <- subset %>%
+      ggplot(aes(x=et, y=log(wage))) +
+      geom_violin(aes(col=et, fill=metro), size=2) +
+      stat_summary(aes(group=metro), fun.y=mean, geom="point")
+   edu <- subset %>%
+      ggplot(aes(x=et, y=log(wage))) +
+      geom_violin(aes(col=et, fill=metro, alpha=edu), size=2) +
+      stat_summary(aes(group=metro), fun.y=mean, geom="point")
+   gridExtra::grid.arrange(plain, metro, edu, ncol=3)
+}

### 2018-07-05 response-to-reviewers.tex
response-to-reviewers: better margins
Added tables with all coefficients to the appendix. Not connected to the main text yet.

@@
     included all the variables, we still got the same results.}
-\debug{SKB: I estimated the models and updated tht.}
+\debug{SKB: I estimated the models and updated the tables with occupation added to Model 3. Added footnote linking to original tables with \enquote{unrestricted} observations}
   The sample size for different specification of the same analysis
@@
 }
+\debug{SKB: I included a first try in the appendix, which is still not perfect. The labels for the variables are not existing yet or not correct.}
 \item 

### 2018-07-05 response-to-reviewers.tex
MInor edit, which was forgotten for the last commit.

@@
             ]{hyperref}
+\usepackage[top=15mm, bottom=15mm, left=10mm, textwidth=130mm, marginparwidth=70mm]{geometry}
 \usepackage{graphicx}
@@
  \usepackage[author=, status=draft]{fixme}
-\usepackage{isomath} %SKB: Changed from \input{isomath} to \usepackage{isomath}
 \newcommand{\skb}[1]{
@@
 }
-\debug{SKB: I included a first try in the appendix, which is still not perfect. The labels for the variables are not existing yet or not correct.}
+\debug{SKB: I included a first try in the appendix, which is still not perfect. The labels for the variables are not existing yet or not correct. The tables are not linked yet to the main text.}
 \item 
@@
   \debug{SR: For more explanations I reestimated Model2 for unemployment for the age groups.
-I made new folder in dropbox:Tabels4_5. Here are Estimates for the age groups for 4 sub-periods, for time period 2000-2012 and for time period 1989-2012. I also made some changes in the text.}
+I made new folder in dropbox:Tabels4\_5. Here are Estimates for the age groups for 4 sub-periods, for time period 2000-2012 and for time period 1989-2012. I also made some changes in the text.}
 \item pg 15 ln 60(?) “, but not precisely estimated.” More explanation on what you mean here would be helpful.

### 2018-07-05 code/plots.R
plots.R: doing the fiolin plot with facets

@@ -27,3 +27,50 @@ maleWage <- function(data) {
       stat_summary(aes(group=metro), fun.y=mean, geom="point")
    gridExtra::grid.arrange(plain, metro, edu, ncol=3)
 }
+
+maleWageF <- function(data, years=2000:2012, ages=25:50) {
+   library(magrittr)
+   library(ggplot2)
+   subset <- data[sex == 1 & !is.na(wage) & !is.na(residenceCounty) & nonEst,
+                  .(wage, estLevel, residenceCounty, edu, age, date)][
+      wage > 0, ][
+    , metro := residenceCounty == 37][
+    , et := estLevel %in% c("1", "2", "home")][
+    , edu := factor(edu, levels=c("<=basic", "highSchool", "college"))][
+      year(date) %in% years & age >= min(ages) & age <= max(ages), ]
+   subset[, metro := ifelse(metro, "metro", "other")]
+   deg <- length(unique(years)) - 1
+   lm(log(wage) ~ poly(year(date), deg) + metro*edu*et, data=subset) %>%
+      summary() %>%
+      print()
+   m2 <- lm(log(wage) ~ poly(year(date), deg), data=subset)
+   subset[, residual := residuals(m2)]
+   plain <- subset %>%
+      ggplot(aes(x=et, y=residual)) +
+      geom_violin(aes(fill=et)) +
+      stat_summary(fun.y=mean, geom="point") +
+      coord_cartesian(ylim=c(-2,2)) +
+      theme(legend.position="none")
+   metro <- subset %>%
+      ggplot(aes(x=et, y=residual)) +
+      geom_violin(aes(fill=et)) +
+      stat_summary(fun.y=mean, geom="point") +
+      facet_grid(metro ~ .) +
+      coord_cartesian(ylim=c(-2,2)) +
+      theme(legend.position="none")
+   edu <- subset %>%
+      ggplot(aes(x=et, y=residual)) +
+      geom_violin(aes(fill=et)) +
+      stat_summary(fun.y=mean, geom="point") +
+      facet_grid(metro ~ edu) +
+      coord_cartesian(ylim=c(-2,2)) +
+      labs(fill="Speaks\nEstonian")
+   subset[, .(wage = mean(wage), residual=mean(residual), n = .N), keyby=.(et)] %>%
+      print()
+   subset[, .(wage = mean(wage), residual=mean(residual), n = .N), keyby=.(metro, et)] %>%
[…]

### 2018-07-05 response-to-reviewers.tex
Minor changes to the appendix and positioning of the tables

@@
 \debug{SKB: I included a first try in the appendix, which is still not perfect. The labels for the variables are not existing yet or not correct. The tables are not linked yet to the main text.}
+\debug{SKB: Should I include tables for unemployment as well? This would blow up the number of pages even further. I could drop the standard errors to save space. Let me know what would be best.}
 \item 
@@
 across the different tables. 
-\debug{SKB: Fixed. Changed obs to observations}
+\debug{SKB: Fixed. Changed obs to Observations in tables}
 \item
@@
 I made new folder in dropbox:Tabels4\_5. Here are Estimates for the age groups for 4 sub-periods, for time period 2000-2012 and for time period 1989-2012. I also made some changes in the text.}
+\debug{SKB: I did not find the tables. Where exactly did you put them? Did you include them in the text as well?}
 \item pg 15 ln 60(?) “, but not precisely estimated.” More explanation on what you mean here would be helpful.

### 2018-07-05 paper/ijm.tex
Minor changes to the appendix and positioning of the tables
Updated a reference

@@
 \usepackage[section]{placeins}
+\usepackage{float}
 \usepackage{booktabs}
@@
 \newcommand{\modelThree}{\modelTwo, industry, occupation ,ownership type of company, number of workers in company, working in the public sector, experience in company}
-\newcommand{\modelThreeAdd}{industry, occupation ,ownership type of company, number of workers in company, working in the public sector, experience in company}	
+\newcommand{\modelThreeAdd}{industry, occupation, ownership type of company, number of workers in company, working in the public sector, experience in company}	
 \newcommand{\restrictions}{The sample period is from year 2000 to year 2012. Sample is limited to persons
@@
 that English is a significant predictor of better income
-\citep{Lang2009, Casale2011, Toomet2011, Williams2011, azam+2013EDandCC, isphording2013, beblavy+2016CEPS}.
+\citep{Lang2009, Casale2011, Toomet2011, Williams2011, azam+2013EDandCC, isphording2013, fabo+2017E}.
 
@@
 		Tertiary sector (\%)        & 26.17  & 30.12  & 26.52  & 34.46  & 27.17  & 33.96  & 28.37  & 40.96  \\
-		\# observations             & 14,943 & 57,270 & 46,525 & 25,688 & 13,805 & 12,830 & 21,773 & 4,862  \\ \bottomrule
+		\# Observations             & 14,943 & 57,270 & 46,525 & 25,688 & 13,805 & 12,830 & 21,773 & 4,862  \\ \bottomrule
 	\end{tabular}%
@@
 
-\begin{table}[t!]
+\begin{table}[h]
 	\begin{center}
@@
 			                & (0.004)                    & (0.005)                            & (0.004)                    & (0.004)                    \\
-			\# observations          & \multicolumn{1}{c}{36,132} & \multicolumn{1}{l}{36,132}         & \multicolumn{1}{l}{36,015} & \multicolumn{1}{c}{36,015} \\
+			\# Observations          & \multicolumn{1}{c}{36,132} & \multicolumn{1}{l}{36,132}         & \multicolumn{1}{l}{36,015} & \multicolumn{1}{c}{36,015} \\
 			$R^{2}$         & 0.022                      & 0.047                              & 0.012                      & 0.036                      \\ \hline
@@
 			                & (0.012)                    & (0.014)                            & (0.011)                    & (0.012)                    \\
-			\# observations          & \multicolumn{1}{c}{12,942} & \multicolumn{1}{l}{12,942}         & \multicolumn{1}{l}{13,674} & \multicolumn{1}{c}{13,674} \\
+			\# Observations          & \multicolumn{1}{c}{12,942} & \multicolumn{1}{l}{12,942}         & \multicolumn{1}{l}{13,674} & \multicolumn{1}{c}{13,674} \\
 			$R^{2}$         & 0.033                      & 0.066                              & 0.023                      & 0.043                      \\ \hline
@@
 			                   & (0.013)                    & (0.015)                    & (0.013)                            & (0.010)                    & (0.010)                    & (0.009)                    \\
-			\# observations             & \multicolumn{1}{l}{21,785} & \multicolumn{1}{l}{21,785} & \multicolumn{1}{l}{21,785}         & \multicolumn{1}{l}{26,673} & \multicolumn{1}{l}{26,644} & \multicolumn{1}{c}{26,449} \\
+			\# Observations             & \multicolumn{1}{l}{21,785} & \multicolumn{1}{l}{21,785} & \multicolumn{1}{l}{21,785}         & \multicolumn{1}{l}{26,673} & \multicolumn{1}{l}{26,644} & \multicolumn{1}{c}{26,449} \\
 			$R^{2}$            & 0.730                      & 0.760                      & 0.801                              & 0.769                      & 0.810                      & 0.830                      \\ \midrule
@@
 			                   & (0.026)                    & (0.027)                    & (0.024)                            & (0.021)                    & (0.022)                    & (0.018)                    \\
-			\# observations             & \multicolumn{1}{l}{7978}   & \multicolumn{1}{l}{7978}   & \multicolumn{1}{l}{7978}           & \multicolumn{1}{l}{9904}   & \multicolumn{1}{l}{9895}   & \multicolumn{1}{c}{9697}   \\
+			\# Observations             & \multicolumn{1}{l}{7978}   & \multicolumn{1}{l}{7978}   & \multicolumn{1}{l}{7978}           & \multicolumn{1}{l}{9904}   & \multicolumn{1}{l}{9895}   & \multicolumn{1}{c}{9697}   \\
 			$R^{2}$            & 0.731                      & 0.746                      & 0.794                              & 0.794                      & 0.809                      & 0.854                      \\ \hline
@@
 \bibliography{literatur}
-
+\clearpage
 \appendix

### 2018-07-06 code/plots.R
use fixme for comments

@@ -32,10 +32,11 @@ maleWageF <- function(data, years=2000:2012, ages=25:50) {
    library(magrittr)
    library(ggplot2)
    subset <- data[sex == 1 & !is.na(wage) & !is.na(residenceCounty) & nonEst,
-                  .(wage, estLevel, residenceCounty, edu, age, date)][
+                  .(wage, estLevel, engLevel, residenceCounty, edu, age, date)][
       wage > 0, ][
     , metro := residenceCounty == 37][
     , et := estLevel %in% c("1", "2", "home")][
+    , en := engLevel %in% c("1", "2", "home")][
     , edu := factor(edu, levels=c("<=basic", "highSchool", "college"))][
       year(date) %in% years & age >= min(ages) & age <= max(ages), ]
    subset[, metro := ifelse(metro, "metro", "other")]
@@ -47,20 +48,20 @@ maleWageF <- function(data, years=2000:2012, ages=25:50) {
    subset[, residual := residuals(m2)]
    plain <- subset %>%
       ggplot(aes(x=et, y=residual)) +
-      geom_violin(aes(fill=et)) +
+      geom_violin(aes(fill=et), alpha=0.6) +
       stat_summary(fun.y=mean, geom="point") +
       coord_cartesian(ylim=c(-2,2)) +
       theme(legend.position="none")
    metro <- subset %>%
       ggplot(aes(x=et, y=residual)) +
-      geom_violin(aes(fill=et)) +
+      geom_violin(aes(fill=et), alpha=0.6) +
       stat_summary(fun.y=mean, geom="point") +
       facet_grid(metro ~ .) +
       coord_cartesian(ylim=c(-2,2)) +
       theme(legend.position="none")
    edu <- subset %>%
       ggplot(aes(x=et, y=residual)) +
-      geom_violin(aes(fill=et)) +
+      geom_violin(aes(fill=et), alpha=0.6) +
       stat_summary(fun.y=mean, geom="point") +
       facet_grid(metro ~ edu) +
       coord_cartesian(ylim=c(-2,2)) +

### 2018-07-06 paper/ijm.tex
use fixme for comments
ijm: polished the age groups section

@@
 \usepackage[T1]{fontenc}
-\usepackage[margin=2.5cm, top=2.5cm, bottom=2.0cm]{geometry}
+\usepackage[margin=3cm,top=2.5cm, bottom=2.0cm]{geometry}
 \usepackage[english]{babel}
@@
 \usepackage{epstopdf}
-
- \usepackage[author=, status=final]{fixme}
+\usepackage[layout=margin,author=,status=draft]{fixme}
   \usepackage[final]{changes} %Manually track changes
@@
 
+\fxsetup{theme=color}
 \def\tenpc{$^{\ast}$}
@@
 skills (Estonian, Russian and English).
+\fxwarning{OT: can you add variable 'year' in this table?  I know it feels a little weird but is great to show time trends.}
 
@@
 order to detect potential trends across the age groups and across ethnic groups
-(Table~\ref{tab:age_group_trend_russian} and Table~\ref{tab:age_group_trend_estonian}).
+(Table~\ref{tab:age_group_trend}).
 We look separately at 4 sub-periods: Early transition period
@@
 
-We use largely the same setup as described in section \ref{sec:method}. The results presented here are derived using the second model.
+We use the same econometric specification as described in section \ref{sec:method}, the results presented here are derived using the model 2.
 
 For ethnic Estonians, knowledge of Russian
-(Table~\ref{tab:age_group_trend_estonian}) has become less
+(Table~\ref{tab:age_group_trend}, upper panel) has become less
 important after its peak in the late 1990s. Notably, the
 association between wage and language skills are small in the
-youngest age groups where the Russian skills are rapidly declining
-while it still is strongly related to salary for
+young groups, the age groups where the Russian skills are also rapidly declining.
+Russian is still closely related to salary for
 older workers. The importance of English language skills fluctuates
-and slowly decline through the period, but the men from group (45-55) and young women (25-35) have a growing trend. They gain more from being fluent in English.
-
-The positive impact of Estonian language skills for ethnic Russians
-(Table~\ref{tab:age_group_trend_russian}) on earnings seems to
-increase over the sample period for women in the young group (25--35)
+and declines slowly through the period, just the oldest male group
+(45-55) and the youngest female group (25-35) show a growing trend.
+This potentially reflects both the changing supply and demand of
+English skills.
+
+Now we turn to ethnic Russians (lower panel in the table).  The association between Estonian skills and income shows no
+statistically significant results at all.  We'll return to this
+outcome below.
+The positive impact of Estonian language skills for Russian women
+increases
+over the sample period for the young group (25--35)
 and the prime age group (36--45).
-While no statistically significant
-correlation is visible for Russian men, good
-Estonian is associated with about 10\% higher salary for Russian women for the boom in the 2000s. For the
+Good
+Estonian language knowledge is associated with approximately 10\% higher salary for Russian women for the boom in the 2000s. For the
 recession period, the figure is even close to 12\%. These age
@@
 economy are slowly becoming a more integrated one where ethnic
-Russians with a good Estonian command can get well-paid jobs.
-In comparison, the estimates for English language fluency shows downward trend for all age groups for men and for women. This is due to the language skills becoming more common among the population.
+Russians, at least women, with a good Estonian command can get well-paid jobs.
+In comparison, the estimates for English language fluency shows
+downward trend for all age groups for men and for women.  A likely
+cause is the increasing abundance of these skills over time.
 
@@
 	\begin{tabular}{lccc|cc c}
-		\hline\hline
+          \toprule
 		\multicolumn{7}{l}{Estonian speakers. Dependent variable: log wage}          \\ \hline
@@
 		08-12      & 0.088*   & 0.179*** & 0.236*** & 0.166*** & 0.123*** & 0.145*** \\
-		           & (0.039)  & (0.035)  & (0.043)  & (0.037)  & (0.024)  & (0.029)  \\ \bottomrule
-	\end{tabular}
-	\caption*{ \legend \\ Standard errors (clustered on individuals) in parenthesis}
-	\label{tab:age_group_trend_estonian}
-\end{table}
-
-\begin{table}[t!]
-	\centering
-	\caption{The trend over time across the age groups (ethnic
-		Russians)}
-	\begin{tabular}{lccc|cc c}
-		\hline\hline
+		           & (0.039)  & (0.035)  & (0.043)  & (0.037)  & (0.024)  & (0.029)  \\ 
+          \midrule
 		\multicolumn{7}{l}{Russian speakers. Dependent variable: log wage}\\
@@
 	\caption*{\legend \\ Standard errors (clustered on individuals) in parenthesis}
-	\label{tab:age_group_trend_russian}
+	\label{tab:age_group_trend}
 \end{table}
 
-We estimate the effect of language skills for unemployment for the age groups and ethnical groups as well for the second model.
-However dividing the results for four sub-periods does not detect the trends across the age groups for those periods due to only some of the results are statistically significant.
-The exception is the group of young (25-34) Estonian men for whom English language is clearly decreases the probability of being unemployment during the time.
-Notwithstanding importance of English is small for other groups.
-Estimates for the longer time period shows the importance of Estonian language for all age groups for ethnical Russian and have even higher impact for the young women.
-
-\section{Additional Evidence: Estonian Language at Workplace}
+We repeat the exercise for unemployment models (using specification 2
+in
+Table~\ref{tab:unemployment_estimation_by_sex_and_ethnic_same_sample}).
+However, as most of the results are not statistically significant, we
+do not present the tables here.
+
+\section{Additional Evidence: Education and Workplace}
 \label{sec:segregation_analysis}
@@
 
+\listoffixmes
+
 \end{document}

### 2018-07-06 paper/ijm.tex
ijm: discuss the Russian 0-premium

@@
 \usepackage[T1]{fontenc}
-\usepackage[margin=3cm,top=2.5cm, bottom=2.0cm]{geometry}
+\usepackage[margin=2.5cm,top=2.5cm, bottom=2.0cm]{geometry}
 \usepackage[english]{babel}
@@
 
-Previous results can be explained by two hypotheses: first, Russian--speaking men are working
-primarily in Russian language environment while this is not true for
+The most interesting result in our analysis so far--the fact that
+Russian men earn virtuannly no Estonian language premium--warrants a
+deeper look at the data.  We split the Russian male wage-earners' data according to three
+dimensions: Estonian language skills, residence in Tallinn metro area,
+and education.  However, to correct very strong trends through these
+years both in wage and language skills, we present the average
+residuals from an OLS regression that explains log wage by year fixed
+effects (Table~\ref{tab:loc-lang-edu}). 
+\fxwarning{ot: Sven, can you redo this table?  Use exactly the same
+  sample as you used.  Would also be good to put both et1 and et0 on
+  the same row}
+The table show that the picture is in fact more complex.  We can see
+that there is little to no gain from Estonian skills for the
+largest group, high-school educated workers.  Even more, outside of
+the metropolitan area, the the lowest and highest education groups
+have in fact negative language premium.  However, these two groups
+enjoy quite a noticeable premium in the Tallinn region.  The
+opposite-signed effects in for these two education groups suggests
+selective internal migration may play a role.
+
+% latex table generated in R 3.4.4 by xtable 1.8-2 package
+% Fri Jul  6 15:59:47 2018
+\begin{table}[ht]
+  \centering
+  \caption{Average wage and time-trend corrected residual across
+    location and education groups for Russian men}
+  \begin{tabular}{lrlrrr}
+    \toprule
+    Tallinn & education & ET & wage & residual & \# obs \\ 
+    \midrule
+    Tallinn & $<$ HS & 0 & 4313.38 & -0.19 & 255 \\ 
+    Tallinn & $<$ HS & 1 & 5351.11 & -0.05 & 219 \\ 
+    Tallinn & HS     & 0 & 5803.21 & 0.05 & 1292 \\ 
+    Tallinn & HS      & 1 & 5666.77 & 0.05 & 1296 \\ 
+    Tallinn & college & 0 & 6562.57 & 0.16 & 212 \\ 
+    Tallinn & college & 1 & 8453.14 & 0.30 & 518 \\ 
+    other   & $<$ HS & 0 & 3877.84 & -0.13 & 461 \\ 
+    other   & $<$ HS & 1 & 4496.62 & -0.18 & 230 \\ 
+    other   & HS     & 0 & 4838.65 & -0.09 & 2233 \\ 
+    other   & HS      & 1 & 5351.51 & -0.05 & 960 \\ 
+    other   & college & 0 & 6283.38 & 0.17 & 278 \\ 
+    other   & college & 1 & 6072.06 & 0.13 & 263 \\ 
+    \bottomrule
+  \end{tabular}
+  \label{tab:loc-lang-edu}
+\end{table}
+
+We can conclude the table~\ref{tab:loc-lang-edu} that our
+most controversial finding, no positive effect of Estonian language
+skills for Russian men, is primarily driven by workers with
+high-school degree.
+
+All previous results can be explained by two hypotheses: first, Russian--speaking men are working
+primarily in Russian language environment (ethnic segregation) while this is not true for
 women; and second, Russian-speaking men are working in jobs with
@@
 significant.
-
-Additionally we briefly analysed online job market \href{http://www.cv.ee/english/}{cv.ee}.  We measured all jobs
-that required English, Finnish and Russian, and calculated the average education requirement
-at these jobs (coded as college/less than college education).  According to the observations,
-the jobs that required English, in average, 51\% of college education while those where Finnish is requested, 19\% and Russian is 26\% respectively.
+\fxwarning{ot: let's remove the cv.ee stuff.  Or substantially improve
+that.}
 

### 2018-07-06 code/plots.R

@@ -66,12 +66,13 @@ maleWageF <- function(data, years=2000:2012, ages=25:50) {
       facet_grid(metro ~ edu) +
       coord_cartesian(ylim=c(-2,2)) +
       labs(fill="Speaks\nEstonian")
-   subset[, .(wage = mean(wage), residual=mean(residual), n = .N), keyby=.(et)] %>%
+   t1 <- subset[, .(wage = mean(wage), residual=mean(residual), n = .N), keyby=.(et)] %>%
       print()
-   subset[, .(wage = mean(wage), residual=mean(residual), n = .N), keyby=.(metro, et)] %>%
+   t2 <- subset[, .(wage = mean(wage), residual=mean(residual), n = .N), keyby=.(metro, et)] %>%
       print()
-   subset[, .(wage = mean(wage), residual=mean(residual), n = .N), keyby=.(metro, edu, et)] %>%
+   t3 <- subset[, .(wage = mean(wage), residual=mean(residual), n = .N), keyby=.(metro, edu, et)] %>%
       print()
    hlay <- matrix(c(1,2,3,3,3), nrow=1)
    gridExtra::grid.arrange(plain, metro, edu, ncol=3, layout_matrix=hlay)
+   t3
 }

### 2018-07-06 response-to-reviewers.tex
use fixme for comments
response: commented on the RU men 0-premium

@@
 \usepackage{csquotes}
- \usepackage[author=, status=draft]{fixme}
+\usepackage[layout=margin,author=,status=draft]{fixme}
+
+\fxsetup{theme=color}
 \newcommand{\skb}[1]{
@@
 	\end{quotation}
-
 }
@@
 \item 
-  \debug{OT: should refer to Toomet (2011), maybe there are more
-    papers.  The effect is mainly coming from Tallinn and somewhat
-    from education too, either do a table that disentangles these, or
-    a plot (violin plot?) by group.}
-  \debug{SKB: I did the estimation separated by regions, but not 
-  separated by regions and educational level. We could add the regional
-  breakdown in the appendix or add it as another extension to chapter 6.}
   My main concern is with some of their wage results. I find it
@@
   reasons that lead to this finding.
+
+  \begin{response}
+    This is a good point.  We have added some more analysis (see
+    Section 7), and it appears the story is somewhat more nuanced.
+    \fxwarning{ensure it's also in the discussion}
+  \end{response}
 \item

### 2018-07-06 paper/ijm.tex
response: commented on the RU men 0-premium
introduction improved

@@
 
+\fxsetup{theme=color}
 %Custom commands
@@
 
-\fxsetup{theme=color}
 \def\tenpc{$^{\ast}$}
@@
 
-The role of other languages is
-less clear.  It is especially unclear what is the role of
-different languages in a multi-lingual economy.  For instance,
+The role of other languages, in particular in multi-lingual economy, is
+less clear.  For instance,
 \cite{Drinkwater1997} finds
 a positive effect for Welsh speaking workers in
-Wales but \citet{FrancoisGrin1998}, in contrast,
+Wales and \cite{Armstrong2015} shows that bilingual native French-speakers enjoy
+a significant premium both inside and outside of Quebec.
+\citet{FrancoisGrin1998}, in contrast,
 shows that Italian language skills in Swiss non-Italian speaking
@@
 this is a true effect or just an omitted variable bias.
-It is estimated by \cite{Armstrong2015} that there is a statistically significant premium paid to bilingual people both inside and outside Quebec who speak French as their mother tongue People speaking English as their mother tongue also earn a premium, but it is much smaller outside of Quebec.
-In some cases it is even statistically not significant.
 
@@
 market from the viewpoint of language skills.
-\citet{Chiswick1995, chiswick+miller2002, chiswick+miller2007, Bellante1998, Chiswick2010} analyse the effects of dominant language fluency for earnings among immigrants in the United States and
-\citet{Chiswick1995}  also analyse it for Canada, Australia and Israel.
+\citet{Chiswick1995, chiswick+miller2002, chiswick+miller2007, Bellante1998, Chiswick2010} analyse the effects of dominant language fluency for earnings among immigrants in the United States
+\citet{Chiswick1995}  also do this for Canada, Australia and Israel.
 \citet{Dustmann2003, shields+price2002} explore of immigrant assimilation into the labour market of the United Kingdom.
@@
 \citet{YaoandOurs2015} only analyse the role of Dutch language
-on labour market performance in Netherlands.  In case of Estonia,
+on labour market performance in Netherlands.  
+\fxwarning{ot:add CEE stuff here?}
+In case of Estonia,
 \citet{Toomet2011} shows that the majority language gives little wage
@@
 explain the lower occupational prestige of Russian speakers.  However,
-she only includes recent school graduates in her study.\\
-
-\noindent In this paper, we analyse the relationship between both
+she only includes recent school graduates in her study.
+
+In this paper, we analyse the relationship between both
 majority and minority language skills, and English for both
-wage and unemployment.  We analyse Estonia, a linguistically divided
-country where a large Russian-speaking community forms almost 30\% of
+wage and unemployment.  We analyse Estonia, a former Soviet republic
+and now a rapidly growing and
+transforming Easter European country.  It is characterized by a stark linguistic division
+where the Russian-speaking community forms almost 30\% of
 the population.  We provide long--term trends from the last years
@@
 
-We find that in case of, Estonian language is associated with very
+We find that the Estonian language, the majority and the official
+language of the country, is associated with very
 small albeit slowly increasing wage premium over
-the years, but only for women.
+the years.  Interestingly, this is true only for women, Russian men enjoy
+virtually no premium from the majority language skills.
 Russian skills, on the other hand, are clearly related to
 higher wage but the relationship is slowly fading.  English fluency was
-associated with a very large wage premium during the first decade
-after the introduction of the market economy, it's importance later
-declined, but was still large in 2012.  For
-women, the wage premium of each of these languages is roughly equal.
+associated with a very large wage premium early after the country
+transitioned to a market economy, later it's importance
+declined but remained sizable.
+
 In contrast, the sole language that plays a role in determining
-unemployment is Estonian, it's fluency is associated with
+unemployment is Estonian.  It's fluency is associated with
 approximately 5 percentage points lower probability of being unemployed.
@@
 more likely occupied in less communication-intense jobs.
-This view is
-supported by data from a specifically designed ethnic integration
-dataset.
 

### 2018-07-07 paper/ijm.tex
data section overwritten

@@
 
-This section briefly reviews Estonian institutional background,
+This section briefly reviews the institutional and economic background
+in Estonia, a country of 1.3M inhabitants,
 focusing on the role of ethnic groups and languages.
@@
 
-Before the Second World War, Estonia was ethnically rather
+Before the Second World War, the country was ethnically rather
 homogeneous, populated almost exclusively by ethnic Estonians. After the War,
 the Russian-speaking population grew rapidly through migration and
-reached 40\% by 1989.
+reached 40\% by 1989.  The migrants largely settled in Ida-Virumaa, a
+mineral-rich industrial area in North-East of the country, and in the
+metropolitan area near the capital city Tallinn, and hence the
+Russian-speakers are still very unevenly distributed across the country.
+
 Such an influx of mainly
@@
 also reflected at workplace \citep{leppik+vihalemm2015JofBaltStud}.
-
 Certain sectors in the economy, such as the army, railways and the
@@
 classes (enrolment of classes rose from 7.8\% in 2005 to 17.5\% in 2015).
-At the same time the number of students whose mother tongue is not Estonian studying in Estonian basic schools slowly dropped respectively from 9.5\% to  8.3\% \citep{HTM2015}.
-
-The younger generation of ethnic Estonians is
-increasingly less fluent in Russian while the opposite is true for ethnic Russians. As
-a bi-product of the rapid integration to the West, the importance of English language rose
-substantially.
-
-As a result of the economic and political reforms, substantial
+At the same time the number of students whose mother tongue is not
+Estonian studying in Estonian basic schools slowly dropped
+respectively from 9.5\% to  8.3\% \citep{HTM2015}.  The younger generation of ethnic Estonians is
+increasingly less fluent in Russian while the ethnic Russians are
+steadily getting better in Estonian.
+
+The Estonian economy, a part of the Soviet economy up to 1991, successfully
+re-oriented to the Western markets and has been growing rapidly since
+the mid-1990s.  
+  As
+a bi-product of the re-adjustment, English skills become extremely
+valuable while the supply was still rather limited during the early
+years of transition.
+
+The economic and political reforms led to substantial
 disparities in income and education opportunities
-emerged
 in the early 1990s \citep{Leping2008,
@@
 are largely limited to superficial encounters at work and in public
-space, the close private ties remain limited
-\citep{korts2009JofBaltStud}.  Both ethnic groups have only few  are
-largely living on their own with limited contacts. The
+space, the number of close private ties remain limited
+\citep{korts2009JofBaltStud}.  The
 separate worlds are also reflected in media which may present quite
@@
 is Russians' ability and willingness to communicate in Estonian.
+\fxwarning{ot: citation here?}
 
@@
 Our main analysis relies on the Estonian Labour Force Survey (ELFS),
-first conducted in 1995. Until 1999 the survey was an annual
-cross-section and later as a quarterly rotating panel.  The number of distinct
-individuals is around 4000 annually. However, due to the rotating
-structure, we have about 16,000 annual observations.
-The reader should keep in mind that while the pre-2000 waves include retrospective income, they do not include retrospective language skills. In this way, the results before
-1995 are partly based on extrapolation, assuming individual language
-skills did not vary before that date.  In the main analysis, we only
-analyse the 2000--2012 time period but we also provide a long-term
-picture that includes the
-earlier waves from 1989--1999.
+first conducted in 1995 by the Estonian Statistical Office.  We limit
+ourselves with years 2000--2012 in the main analysis, motivated by a
+methodology break: Until 1999 the survey was conducted as an annual
+cross-section and later as a quarterly rotating panel.  The survey
+contains data on approximately 4000 distinct individuals annually,
+however, due to it's rotating nature, we have roughly 16,000 annual
+observations for each year since 2000.  For the long-term analysis we
+also use the earlier waves.  These wave also include a retrospective
+section that contains income up to several years back.
+
 We limit ourselves to men and women in the main working age, between 25 and
@@
 In all waves of the survey, respondents are asked about their
-\emph{ethnic nationality}.  Typically, individuals have a single ethnic
+``ethnic nationality''.  Typically, individuals have a single ethnic
 identity.  The answers are coded as ``Estonian'' or
@@
 
-The labour market outcomes include ``last salary on the main job'' and
-labour force status (working, unemployed or inactive).
+The labor market outcomes we analyze are income, the ``last salary on the main job'' and
+labor force status (working, unemployed or inactive).
 
@@
 no knowledge, understanding, speaking, writing, or using the
-language at home.  We consolidate this information into a dummy, equal to zero
-for languages one cannot speak (but potentially understand) and
-unity if one speaks, speaks or writes, or uses that language at
-home.
+language at home.  We consolidate this information into a dummy variable, equal
+to one if one speaks or writes, or uses that language at
+home, and zero otherwise.  Hence we disregard passive understanding
+only.
+  The reader should keep in mind that while the pre-2000 waves include retrospective income, they do not include retrospective language skills. In this way, the results before
+1995 are partly based on extrapolation, assuming individual language
+skills did not vary before that date.
 
@@
 	of observation, 2000-2012, the average salary increased by 180\%,
-	from \EUR{314} to \EUR{887} monthly.
-
-} of Estonian
+	from \EUR{314} to \EUR{887} monthly.} of Estonian
 males who are not fluent in English is \EUR{532} while for Russians it

### 2018-07-07 paper/ijm.tex
methos overwritten

@@
 the mid-1990s.  
+\fxwarning{ot: a few numbers about economic growth would be good}
   As
@@
 Estonians and Russians in wage and unemployment. For instance, the
-average monthly salary\footnote{When interpreting the wage,
-  one should keep in mind that during the period
-	of observation, 2000-2012, the average salary increased by 180\%,
-	from \EUR{314} to \EUR{887} monthly.} of Estonian
+average monthly salary\footnote{When interpreting these figures,
+  one should keep in mind that during this period, 2000-2012, the average monthly salary grow by 180\%,
+  from \EUR{314} to \EUR{887} while the language knowledge changed rapidly as
+  well.  However, the ethnic composition of the workforce remained
+  roughly constant.} of Estonian
 males who are not fluent in English is \EUR{532} while for Russians it
@@
 for men (\EUR{378} versus \EUR{329} monthly) and 30\% for women
-(\EUR{260} versus \EUR{203}).  Similarly, English is more closely
-associated with income for Estonians than Russian language. In
+(\EUR{260} versus \EUR{203}).  Analogously, English is more closely
+associated with income for Estonians compared to Russian language. In
 contrast, unemployment shows a different picture. For ethnic Russians,
@@
 related to Russian fluency is only 1.6 percentage points.  However,
-these associations are not easy to interpret as English skills are
+these correlations are not easy to interpret as besides of the strong
+time trends, English skills are
 also related to education, metropolitan residence, and general
@@
 % Table generated by Excel2LaTeX from sheet 'subgroups_by_ethnic_language'
-\begin{sidewaystable}[htbp]
+\begin{sidewaystable}[tbp]
 	\centering
@@
 		\emph{RUS 0} refers to individuals who cannot speak Russian and
-		\emph{RUS 1} to those who can. Analogously for English and
-		Estonian.\\
+		\emph{RUS 1} to those who can. Analogously for English
+                (ENG) and
+		Estonian (EST).\\
 		Primary sector = Agriculture,
@@
 being more fluent in English and Estonian while older Estonians being
-better in Russian. The family variables follow the
+better in Russian. The family status--related variables correspond to the
 respective age distribution. Not surprisingly, inter-ethnic
@@
 omitted variable bias and measurement errors \citep{Chiswick1995, bleakley+chin2004}.
-%\ot{more examples here}
 We refrain from doing that. Our decision is mainly data driven,
@@
 	not statistically significant at any conventional level.} but it also facilitates
-comparison with other studies.For instance,
-\citet{azam+2013EDandCC} and \citet{paolo+tansel2015JofDevStud} only report OLS results.
-
-There is also evidence from job language requirements suggesting that
-the reduced-form evidence is not too different from the causal effect
-\citep{beblavy+2016CEPS}.
-
-\citet{azam+2013EDandCC} and \citet{paolo+tansel2015JofDevStud}, who use proxy variables to control for
-individual ability, find these having little influence on the effect
-of language skills.
-
-We estimate unemployment probability by linear probability model
-(LPM) to avoid unnecessary parametric
+comparison with other studies.  For instance,
+\citet{azam+2013EDandCC} and \citet{paolo+tansel2015JofDevStud} only
+report OLS results, and, even more, find that the available proxy
+variables have little influence on the final results.
+
+We use linear probability models (LPM) to estimate the relationship between
+language skills and unemployment, mainly in order to avoid unnecessary parametric
 assumptions in the corresponding binary choice models.\footnote{The
@@
 Similarly, we estimate the effect of language skills on wage by
-OLS. We correct the estimates for the panel data structure by
-clustering the standard errors by individuals.
-
-%\fxnote{Add here another index g to denote the group? I used it in other articles, because it was requested and it makes sense}
+OLS.
+
 We estimate the basic model in the following form:
@@
 	\begin{split}
-		y_{it} ^{g} = &\: \alpha^{g}{}' X_{it}^{g} + \vec{\beta}^{g}{}' \cdot \vec{L}_{it}^{g} +
+		y_{it} ^{g} = &\: \alpha^{g}{}' \vec{X}_{it}^{g} + \vec{\beta}^{g}{}' \cdot \vec{L}_{it}^{g} +
 		\eta_{i}^{g} +
@@
 or logarithm of net monthly wage)
-of individual $i$ in wave $t$ from ethnic group g; $\vec{X}^{g}$ are the other individual
-characteristics for both groups; $L$ is the vector of
-language skill descriptors, $eta_{i}^{g}$ is the individual-specific effect, $\upsilon_{t}^{g}$ are the year dummies and $\epsilon_{it}^{g}$
-is the idiosyncratic error term. We denote the groups g by E (Estonian) and R (Russian).
+of individual $i$ in year $t$ from ethnic group $g$ (either Estonian
+or Russian); $\vec{X}$ are the other individual
+characteristics; $\vec{L}$ is the vector of
+language skill descriptors, $\eta_{i}^{g}$ is the individual-specific effect, $\upsilon_{t}^{g}$ are the year dummies and $\epsilon_{it}^{g}$
+is the idiosyncratic error term. 
+\fxerror{ot: what's eta?  do you do random effects?}
 As we use panel data, we cluster the
@@
 replace the main language effects in~\eqref{eq:specification} by the
-\fxnote*{Did we estimate it really that way?
-At least not in my code.
-I found the code for estimations with these interactions, but I don't remember that I used these interactions for the tables.}{corresponding interactions}
+corresponding interactions
+\fxwarning{ot: ensure this is what we do :-)}
 \begin{align}
@@
 characteristics (age, education) and family descriptors (marital status, having kids up to 17 years old) and county of residence.
-Finally, the third model additionally includes industry, occupation, and other
-workplace descriptors.
-\Cref{tab:models} summarises this description of the models.
-%SKB: This table should have been in the article at some point, but I must have removed it. I use in my Quantile Regression article
-\begin{table}[hbtp]
-	\centering
-	\caption{Groups of explanatory variables included in different models}
-	\label{tab:models}
-	\begin{tabular}{r|ccc}
-		\toprule
-		& Model 1 & Model 2 & Model 3 \\ \midrule
-		year dummies       & \V      & \V      & \V      \\
-		indiv. charact.    &         & \V      & \V      \\
-		workplace charact. &         &         & \V      \\ 
-		\bottomrule
-	\end{tabular}
-\end{table}
+Finally, the third model also adds industry, occupation, and other
+workplace descriptors.  Note that in case of unemployment probability,
+we only estimate the first two models.
 

### 2018-07-07 paper/ijm.tex
more rewrite, till 6.2

@@
 %SKB: Added for documenting the tables and figures
-\newcommand{\modelTwo}{age, age\textsuperscript{2}, education, being married, number of children, inter-ethnic household}
-\newcommand{\modelThree}{\modelTwo, industry, occupation ,ownership type of company, number of workers in company, working in the public sector, experience in company}
+\newcommand{\modelTwo}{age, age\textsuperscript{2}, education, marriage, number of children, inter-ethnic household}
+\newcommand{\modelThree}{\modelTwo, industry, occupation, ownership type of company, number of workers in company, working in the public sector, experience in company}
 \newcommand{\modelThreeAdd}{industry, occupation, ownership type of company, number of workers in company, working in the public sector, experience in company}	
@@
 	25-55 year old.}
-\newcommand{\agerestrictions}{Sample is limited to persons
-	25-55 year old.}
+\newcommand{\agerestrictions}{25-55 year olds only.}
 %Modified section numbering	
@@
 there are no suitable instruments in our data,\footnote{We run an IV
-	regression using age--at--immigration to instrument Estonian skills
+	regression using age at immigration to instrument Estonian skills
 	for those Russians who were in the country at 1990.  The results are
@@
 is the idiosyncratic error term. 
-\fxerror{ot: what's eta?  do you do random effects?}
+\fxerror{ot: what's the eta term?  do you do random effects?}
 As we use panel data, we cluster the
@@
 The central results for unemployment regressions are given in
-\cref{tab:unemployment_estimation_by_sex_and_ethnic_same_sample}.
-\footnote{This table is restricted to have the same number of observations across all models requested by reviewer.
-The unrestricted table is in the appendix \cref{tab:unemployment_estimation_by_sex_and_ethnic}.}
-
+\cref{tab:unemployment_estimation_by_sex_and_ethnic_same_sample}.\footnote{We
+  restrict both models to have the same number of observations as
+  requested by a reviewer. The unrestricted table is in the appendix \cref{tab:unemployment_estimation_by_sex_and_ethnic}.}
 The
@@
 influenced by the individual characteristics--for men it is
-virtually unchanged while for women the estimate falls by 30\%.
+virtually unchanged while for women the estimate falls by 30\%, from
+6.5 to 4.5 percentage points.
 
@@
 for Estonian women. The latter outcome may be related to omitted
-variable bias, Russian knowledge was widespread before 1990 and may
+variable bias, Russian knowledge was widespread in the Soviet era and may
 not have been closely associated with any favourable characteristics,
-but during the period was increasingly more associated with age.
+but has been increasingly more associated with age  during the period of analysis.
 English skills are related to less unemployment both for Estonian men
@@
 
-In summary, these results suggest that the Estonian language is
-important for employment prospects. The role of English is
-small, and that of Russian is almost non-existent despite a largely
-bilingual service sector in the country.
-
-\subsection{Wage Regressions}
+In summary, these results suggest that Estonian is the only language
+that matters for the employment prospects.  Despite of widespread
+bilingualism in the service sector, and increasing global importance of
+English, these languages are not closely associated with unemployment
+probability.
+
+\subsection{Wage}
 %SKB: Adding occupation to Model 3 reduces the effects drastically. Beforehand I somehow forgot to add it to the estimation. Now occupation is included as it should have been in the first place.
@@
 
-\cref{tab:wage_estimation_by_sex_and_ethnic_same_sample} presents the main
-results.\footnote{This table is restricted to have the same number of observations across all models requested by reviewer.
-The unrestricted table is in the appendix \cref{tab:wage_estimation_by_sex_and_ethnic}.}
-
+\cref{tab:wage_estimation_by_sex_and_ethnic_same_sample} presents the
+central wage regression
+results.\footnote{As above, we
+  restrict both models to have the same number of observations as
+  requested by a reviewer.  The unrestricted table is in the appendix \cref{tab:wage_estimation_by_sex_and_ethnic}.}
 The table
-confirms that wage is positively associated with fluency in other
-languages, in particular English. The only remarkable exception is
+confirms the descriptive evidence that wage is positively associated
+with fluency of all analyzed languages with English showing the
+largest effect.  The only remarkable exception is
 Estonian language for Russian men where we fail to find any positive
-effect for any model. This qualitatively repeats the results of
+effect for any of the specifications.  This qualitatively repeats the results of
 \citet{Toomet2011}. However, for women we observe a sizeable
 positive effect between 6 and 16 percentage points, suggesting that
-\citet{Toomet2011} results only describe the male labour market.  The effect decreases somewhat
+\citet{Toomet2011} results are not valid for the female labour market.  The effect decreases somewhat
 (from 0.167 to 0.114) when including the individual characteristics
@@
 is partly caused by education and potentially also by unobserved
-individual performance. Adding further observable workplace characteristics nearly halves the effects 
-(when accounting not only for the industry but also the occupation) %SKB: Might remove this sentence
-.
-
-\begin{table}[htbp]
+individual performance.  Adding observable workplace characteristics
+lowers the effects further to 0.066, suggesting that part of the
+language skill premium is collected through workplace mobility.
+
+\begin{table}[tbp]
 	\begin{center}
@@
 substantial income premium of 10\% for both Estonian men and women.
-The effect approximately halves when introducing
-individual controls, suggesting that it is partly related to
-education and potentially also to ability. It
-falls further when also controlling for the
-workplace characteristics, indicating that Estonians' income is
-better characterized by available workplace
-variables.
+The effect falls rapidly when introducing
+individual and workplace controls, suggesting that both ability bias
+and workplace mobility play a role.
 
@@
 associated with higher wage but Russian to a smaller extent.
-This is in a stark contrast to the unemployment regressions, we return to
-this question in the discussion.
+This is in a stark contrast to the unemployment regressions and we return to
+this question in the discussion below.
 
@@
 
-Here we look at the yearly estimates from 1992 to 2012.
-We report those for the model 2.\footnote{The results for other models
-	look essentially the same. If we add more variables like in model 3 then the effect size reduces by about five to ten percentage points, but the overall picture remains the same.}
-
-The effect on language fluency on unemployment is shown on Figure~\ref{fig:long-run_unemployment} and on wage on Figure~\ref{fig:long-run_wage}
-
-\begin{figure}[hbtp]
+As Estonian economy went through turbulent times and rapid changes
+during the 1990s, additional evidence can be gained by a long-term
+trends in the estimated effect size.  Here we look at the yearly estimates from 1992 to 2012.
+We report the results for model 2, i.e. models that include year
+dummies and individual controls, but not workplace
+characteristics.\footnote{The results for models with workplace data (model
+  3 for wage)
+  look qualitatively similar.  More controls in the model reduces the effect size but does not qualitatively
+  change it's temporal pattern.}
+
+The effect of language fluency on unemployment is shown on
+Figure~\ref{fig:long-run_unemployment}, and on wage on
+Figure~\ref{fig:long-run_wage}.
+\fxnote{ot: SKB, I think I asked if you can slightly offset the black
+  and red lines and you could not?}
+The results reveal a few interesting facts.  First, the effects are
+relatively stable over time, indicating that neither economic
+environment nor the data quality have changed rapidly.  Estonian
+fluency has been associated with less unemployment for both Russian men and
+women since around year 2000, in 1990s it had little effect.  Russian fluency,
+in contrast, had never had an impact on Estonians' unemployment probability.
+
+\begin{figure}[bt!]
 	\centering
@@
 
-The results reveal a few interesting facts.  First, the effects are
-relatively stable over time, indicating that neither economic
-environment nor the data quality have changed rapidly.  Estonian
-fluency has been associated with less unemployment for both men and
-women since around year 2000, in 1990s it had little effect.  Russian fluency,
-in contrast, had never an impact on unemployment probability.
-
 For Estonian men, fluency in English is associated with less unemployment through the whole
 period of observation whereas fluency in Russian has no effect.
-Only few of the results are statistically significant pointwise though.
+Only few of the results are pointwise statistically significant though.
 For Estonian women, both languages are associated with less
@@
 
-\begin{figure}[hbtp]
+\begin{figure}[tb!]
 	\centering
@@
 
-The estimates for wage are rather stable as well. For Estonians, we
-see a slight downward trend of the effect of fluency in Russian whereas
-that of English becomes important in the late 1990s. For Russians, the
-importance of English seems to be sliding across the years, probably
-due to the increasing supply of these skills. For men, fluency in Estonian
+The wage effects show a similar smooth long-term trend.  For Estonians, we
+see a slowly fading effect of Russian fluency whereas
+English becomes important in the late 1990s.  For Russian men, fluency in Estonian
 has never been significantly associated with wage.
-The results are remarkably stable over the whole period, stressing
-the continuity of the peculiar labour market institutions,
-potentially workplace segregation, through the
-whole post-communist period. For women, however, we can see
-a slight increasing trend, suggesting that there is either less
+The results are remarkably stable over the whole period, indicating
+that the peculiar labour market institutions have been persistent for
+two decades.  However, we can see how Estonian language turned
+important in late 1990s, suggesting that there is either less
 workplace segregation or other need for the official language for
-the jobs commonly taken by women.
+the jobs commonly taken by women.  The
+importance of English seems to be falling over time for Russians, possibly
+due to the increasing supply of these skills.
 

### 2018-07-08 paper/ijm.tex
ijm: written till conclusion

@@
 \newcommand{\agerestrictions}{25-55 year olds only.}
-%Modified section numbering	
-\renewcommand{\thesection}{\arabic{section}.}
-\renewcommand{\thesubsection}{\thesection\arabic{subsection}.}
+% Modified section numbering: removed dot at the end as this jumps
+% into the cross-references.
+\renewcommand{\thesection}{\arabic{section}}
+\renewcommand{\thesubsection}{\thesection\arabic{subsection}}
 
@@
 
-We also estimate the effects separately by age groups and time in
-order to detect potential trends across the age groups and across ethnic groups
+As age is a central determinant how major economic and political
+reforms influence individual fates, 
+we also analyze the time trends by age groups
 (Table~\ref{tab:age_group_trend}).
-We look separately at 4 sub-periods: Early transition period
+We group the observation period into 4 sub-periods: Early transition period
 (1989--1995); First economic growth period (1996--1999);
@@
 (2008--2012).
-
-We use the same econometric specification as described in section \ref{sec:method}, the results presented here are derived using the model 2.
+We use the same econometric framework as described in section
+\ref{sec:method}, the results presented here are based on the specification 2.
 
@@
 association between wage and language skills are small in the
-young groups, the age groups where the Russian skills are also rapidly declining.
-Russian is still closely related to salary for
-older workers. The importance of English language skills fluctuates
-and declines slowly through the period, just the oldest male group
-(45-55) and the youngest female group (25-35) show a growing trend.
+young groups, the age groups where knowledge of that language
+declining rapidly.
+For older age groups, the estimates are larger but not statistically
+significant since the recession period.  English was not important
+during the early years of transition, but has been very closely
+associated with better pay since 1996.  It's importance seems to be
+falling though for the young and middle male groups while the oldest men
+(45-55) and the youngest women (25-35) show a growing trend.
 This potentially reflects both the changing supply and demand of
@@
 Now we turn to ethnic Russians (lower panel in the table).  The association between Estonian skills and income shows no
-statistically significant results at all.  We'll return to this
-outcome below.
-The positive impact of Estonian language skills for Russian women
-increases
-over the sample period for the young group (25--35)
-and the prime age group (36--45).
-Good
-Estonian language knowledge is associated with approximately 10\% higher salary for Russian women for the boom in the 2000s. For the
-recession period, the figure is even close to 12\%. These age
-groups are the workers who were in their twenties or younger during
-the major political and economic transition in early 1990s. It
+statistically significant results at all.  This is the most unexpected
+result in our analysis and we'll return to this
+below in section~\ref{sec:segregation_analysis}.
+The impact of Estonian language skills for Russian women too, but
+since year 2000, we observe a sizable effect of approximately
+10\% for several cases.  However, standard errors are large and we
+cannot conclude that the effect is positive for all the age groups.
+The positive outcomes for women for the second decade in our analysis
 suggests that the previously segregated ``Estonian'' and ``Russian''
-economy are slowly becoming a more integrated one where ethnic
-Russians, at least women, with a good Estonian command can get well-paid jobs.
-In comparison, the estimates for English language fluency shows
-downward trend for all age groups for men and for women.  A likely
+economies are slowly becoming a more integrated one where ethnic
+Russians, at least women, with good Estonian command get better-paid
+jobs than those who cannot speak the language.
+In comparison, the estimates for English language show
+a downward trend for all age groups for both men and for women.  A likely
 cause is the increasing abundance of these skills over time.
@@
 
-We repeat the exercise for unemployment models (using specification 2
-in
-Table~\ref{tab:unemployment_estimation_by_sex_and_ethnic_same_sample}).
+We repeat the exercise for unemployment models.
 However, as most of the results are not statistically significant, we
-do not present the tables here.
+do not report the results here.
 
@@
 
-The most interesting result in our analysis so far--the fact that
-Russian men earn virtuannly no Estonian language premium--warrants a
-deeper look at the data.  We split the Russian male wage-earners' data according to three
+The most surprising result in our analysis so far--the fact that
+Russian men earn virtually no Estonian language premium while women do--warrants a
+deeper look at the data.  We compute the average wage for the Russian male wage-earners
+along the three
 dimensions: Estonian language skills, residence in Tallinn metro area,
-and education.  However, to correct very strong trends through these
-years both in wage and language skills, we present the average
+and education.  The metropolitan area is one of the two major regions
+where the Russian-speaking population is concentrated, and it's
+booming economy may be very different from that in the North-East.
+Even more, while Russians form a large minority in and around Tallinn,
+they are in majority in the North-East.  
+In addition, to correct very strong wage and language skill trends through these
+years, we also present the average
 residuals from an OLS regression that explains log wage by year fixed
@@
   the same row}
-The table show that the picture is in fact more complex.  We can see
+The table shows that the picture is in fact quite complex.  We can see
 that there is little to no gain from Estonian skills for the
 largest group, high-school educated workers.  Even more, outside of
-the metropolitan area, the the lowest and highest education groups
+the metropolitan area, the lowest and highest education groups
 have in fact negative language premium.  However, these two groups
@@
 opposite-signed effects in for these two education groups suggests
+that a
 selective internal migration may play a role.
@@
 We can conclude the table~\ref{tab:loc-lang-edu} that our
-most controversial finding, no positive effect of Estonian language
+most suprising finding, no positive effect of Estonian language
 skills for Russian men, is primarily driven by workers with
-high-school degree.
-
-All previous results can be explained by two hypotheses: first, Russian--speaking men are working
+high-school degree.  It also suggests that highly educated workers in
+the metropolitan area enjoy, in fact, a substantial language premium.
+However, this group is not very large.
+
+The previous results can be explained by two hypotheses: first,
+Russian--speaking men, at least those with high-school degree as their
+highest completed education, are working
 primarily in Russian language environment (ethnic segregation) while this is not true for
@@
 question addresses the ethnic segregation while the second focuses on
-the need of communication.  As very few individuals work in English
-environment, we only look for Estonian as the communication language.
+the need of communication.
 
@@
 who need Estonian and English at work.  As we see, women are more likely to
-use Estonian than men while the opposite is true for English.
-Table~\ref{tab:environment_model} presents the regression results when
-controlling for other
+use Estonian while the opposite is true for English.
+Table~\ref{tab:environment_model} presents the regression results
+where we estimate the likelihood of having the need and using Estonian at work
+while
+controlling for gender and other individual
 characteristics, including education and geographic location.
@@
 Estonian-speaking environment when controlling for other factors.
-Both estimates are statistically significant (at 5\% and 10 \% level
+Both figures are statistically significant (at 5\% and 10 \% level
 respectively), but not precisely estimated.  We can also see that
@@
 working in less segregated environment where Estonian is the main
-communication language, and they need Estonian for other reasons as
+communication language, and they need Estonian at work for other reasons as
 well.  Gender differences in English usage are not statistically

### 2018-07-08 paper/ijm.tex
paper: conclusion rewritten

@@
 
-We document that different languages are associated in a
-different way with unemployment and wage. Our most
-intriguing observation is that
-Russian men earn virtually no income premium from being fluent in Estonian,
-the majority and official language of the country, while the fluency is related to a substantially
+We document that all analyzed language skills are associated with
+unemployment and wage, however in a different way. Our most
+intriguing observation is that the largest group of
+Russian men, high-school graduates, earn virtually no income premium if fluent in Estonian,
+the majority and the official language of the country, while ability
+to speak the language is related to a substantially
 lower unemployment rate.
-Our analysis supports \citet{YaoandOurs2015} and \citet{Lindemann2013} finding that
+Our analysis supports \citet{YaoandOurs2015}, and \citet{Lindemann2013} findings that
 the labour market is segmented between ethnic and gender lines.
-However, we find that ethnic segregation is less prevalent at the lower end
-of the male labour market.
-The lower--end labour market, associated with frequent unemployment, is
-better integrated and
-those who are fluent in the language may expect both less unemployment
-and higher wage.  However, men at better paid and more stable jobs
-gain little from Estonian.  We
-suppose this is because the middle and upper-end labour market is more
-segregated and even
-those who speak the official language cannot improve their income
-much.  This is possibly a type of glass-ceiling effect.  This hypothesis is
-supported by \citet{leppik+vihalemm2015JofBaltStud} who show that
-Estonian language skills are not associated with improved career
-mobility over time.  It is also corroborated with the quantile regression evidence that
-Estonian language is related to a positive wage premium only at the
-lowest end of income scale \citep{Toomet2011}.  There is also
+However, we find that ethnic segregation is less prevalent in the male
+labour market.
+We suspect that for majority of Russian speaking men, Estonian
+language gives a distinct advantage by facilitating hiring by
+Estonian-dominated employers.  However, these
+jobs are associated with little career mobility.
+(\citet{leppik+vihalemm2015JofBaltStud} reach a similar conclusion
+based on Immigrant Population Survey).  There is also
 anecdotal evidence suggesting that offices are
-typically manned by ethnic Estonians while production units have a
+typically manned by ethnic Estonians while manufacturing units have a
 large share of Russian workers.
@@
 with negative attitudes toward Russians \citep{korts2009JofBaltStud}.
+On a more positive tone, we find
+that this may not be the case for highly educated workers.
 
@@
 \citet{leppik+vihalemm2015JofBaltStud} analyse men and women
-separately.  We suppose that women are more frequently employed in jobs in which they need Estonian
+separately.  We find some evidence that female labor market is less
+segregated along ethnic lines, and women are more frequently employed in jobs in which they need Estonian
 language more, such as working in a direct contact with customers.
+
 We also find evidence that over time Estonian is becoming more
@@
 does not let us to assess whether is due to decreasing segregation, or
-economy--wide rise of Estonian language.  No such trend is visible for men.
+economy--wide rise of the importance of Estonian language.  No such trend is visible for
+men suggesting that 20 years--almost a generation after the collapse of Soviet Union, the
+labor market integration is still not complete.
 
@@
 jobs.  In contrast, our outcomes suggest that English has little use
-at low-paid, unstable jobs \citep{Toomet2011}.
-
+at unstable jobs, at these jobs where workers frequently move between
+employment and unemployment.
 Note also that for
@@
 The study has a number of limitations.  Although we believe that our
-estimates are good indicators of a causal relationship, we cannot make
-such claim unless a suitable instruments for language skills can be
-found.  In particular, as individual characteristics are able to explain a
+estimates are good indicators of a causal relationship, we cannot 
+claim this as our data do not contain strong enough instruments.
+In particular, as individual characteristics are able to explain a
 large part of English returns, we suppose part of the remaining effect
 may also related to an ability bias.  Another weak point in the current
-data, although it is
-standard in the literature, is using the self-reported language
-skills.  As language test data becomes available, we may be able to
+data is using the self-reported language
+skills, although this is the standard practice in the literature.  As language test data becomes available, we may be able to
 decrease the measurement error in the future.

### 2018-07-10 paper/ijm.tex
a little more responses

@@
 
-We estimate the basic model in the following form:
+We describe the outcome of individual $i$ belonging to group $g$ (either Estonian
+or Russian) at year $t$ as
 \begin{equation}
@@
 \end{equation}
-where $y_{it}^{g}$ is the outcome (either unemployment indicator
-or logarithm of net monthly wage)
-of individual $i$ in year $t$ from ethnic group $g$ (either Estonian
-or Russian); $\vec{X}$ are the other individual
+where $y$ is the outcome (either unemployment indicator
+or logarithm of net monthly wage), $\vec{X}$ are the other individual
 characteristics; $\vec{L}$ is the vector of
@@
 \fxerror{ot: what's the eta term?  do you do random effects?}
+\fxerror{ot: why does $\upsilon$ have index $g$?}
 As we use panel data, we cluster the
-standard errors on individuals.  When analysing the time trend, we
-replace the main language effects in~\eqref{eq:specification} by the
-corresponding interactions
-\fxwarning{ot: ensure this is what we do :-)}
-\begin{align}
-	\label{eq:time_interaction}
-	\beta_{RUS,t} \cdot RUS_{it} \cdot \upsilon_{t} +
-	\beta_{EST,t} \cdot EST_{it} \cdot \upsilon_{t} +
-	\beta_{ENG,t} \cdot ENG_{it} \cdot \upsilon_{t}.
-\end{align}
+standard errors on individuals.  When analysing the long-term time
+trend, we use the same specification (without year fixed effects) to
+estimate separate models for each individual year.
 
 We estimate three models that differ in terms of the number of
-control variables. The first one only includes the language skills
-and year dummies. The second one also includes individual
-characteristics (age, education) and family descriptors (marital status, having kids up to 17 years old) and county of residence.
-Finally, the third model also adds industry, occupation, and other
-workplace descriptors.  Note that in case of unemployment probability,
+control variables. The first specification only includes the language skills
+and year dummies.  It describes the ``raw'' effect of language skills
+on outcomes after controlling for substantial time trends in our data.
+The second specification additionally includes individual
+characteristics (age, education) and family descriptors (marital
+status, indicator for interethnic marriage, having kids up to 17 years
+old) and county of residence.  
+Finally, the third specification also adds industry, occupation, and other
+workplace descriptors.
+Note that in case of unemployment probability,
 we only estimate the first two models.
@@
 labour market.
-We suspect that for majority of Russian speaking men, Estonian
+This suggests for majority of Russian speaking men, Estonian
 language gives a distinct advantage by facilitating hiring by
-Estonian-dominated employers.  However, these
-jobs are associated with little career mobility.
-(\citet{leppik+vihalemm2015JofBaltStud} reach a similar conclusion
-based on Immigrant Population Survey).  There is also
+Estonian-dominated employers.  However, our outcome also supports 
+\citet{leppik+vihalemm2015JofBaltStud} conclusion that
+these
+jobs are associated with little career mobility.  There is also
 anecdotal evidence suggesting that offices are

### 2018-07-10 paper/ijm.tex
Added a comment and two new references to bib-file.

--- 2018-07-08 paper/ijm.tex
@@
   and red lines and you could not?}
+\fxnote{SKB: I do not remember such request.
+The only request, that I remember, is to make the scaling of the figures equal or cut off parts of the large confidence intervals, so that the scaling of the y-axis becomes smaller/more detailed.}
 The results reveal a few interesting facts.  First, the effects are

### 2018-07-10 paper/ijm.tex
Reacted to several comments by adding new comments. Copy and pasted some lines to start the CEE comparison part. Removed the $g$ index from  $\upsilon_{t}$.

@@
 \fxwarning{ot:add CEE stuff here?}
+\fxwarning{SKB: Let's collect first enough material and then decide, but I can start adding here some notes from \cite{Kahanec2009,Kahanec2010}.}
+%Start here CEE stuff for now
+\cite{Kahanec2009} provide an overview about \enquote{the roles of foreign origin and citizenship in the labor markets of Eastern and Eestern[sic] Member States of the EU} \dots and use the EU Survey of Income and Living Conditions (EU-SILC) dataset.
+They\enquote{ mapped and compared the roles of foreign origin and citizenship for labor market performance in Eastern and Western EU Member States.}
+Using Oaxaca and Fairlie decompositions, they show that there is native/non-native divide in the national labour markets \dots.
+They find that \enquote{both foreign origin and citizenship remain important barriers to non-native labor market integration}
+\enquote{In Estonia and Latvia, in particular, employment
+	policies seem to be most relevant for non-immigrant non-citizens. Once employed,
+	non-nativity may play a less negative role in the labor market for some groups,
+	although labor market segmentation remains a significant issue.}
+\fxnote{\cite{Kahanec2009} essentially confirms your results in \cite{Leping2008,Toomet2011}}
+\cite{Kahanec2010} show that \enquote{the labor market situation of ethnic minorities in the European
+	Union. Facing a serious measurement challenge and lacking adequate data, we apply
+	several measures of ethnicity and examine various data sources as well as secondary
+	evidence. We find significant gaps between ethnic minority and majority populations in
+	terms of labor market outcomes.}
+%Continue with existing stuff
 In case of Estonia,
@@
 characteristics; $\vec{L}$ is the vector of
-language skill descriptors, $\eta_{i}^{g}$ is the individual-specific effect, $\upsilon_{t}^{g}$ are the year dummies and $\epsilon_{it}^{g}$
+language skill descriptors, $\eta_{i}^{g}$ is the individual-specific effect, $\upsilon_{t}$ are the year dummies and $\epsilon_{it}^{g}$
 is the idiosyncratic error term. 
 \fxerror{ot: what's the eta term?  do you do random effects?}
+\fxerror{SKB: Eta should be the individual specific random effect.
+We cluster the standard errors at the individual level, hence estimate a random-effect model, although not a panel random-effect model.}
 \fxerror{ot: why does $\upsilon$ have index $g$?}
+\fxerror{SKB: Should be an error, probably index $g$ was just added to everything.}
 As we use panel data, we cluster the
@@
 characteristics (age, education) and family descriptors (marital
-status, indicator for interethnic marriage, having kids up to 17 years
+status, indicator for inter-ethnic marriage, having kids up to 17 years
 old) and county of residence.  
@@
 we only estimate the first two models.
+\fxnote{Actually, I tried to estimate Model 3 as well for unemployment probability.
+The language coefficients become insignificant after controlling for industry and occupation.
+Hence, Estonian language fluency lowers the unemployment probability only if workplace characteristics are ignored.
+Since nobody questioned this result during review, we should maybe not mention it now.
+}
 
@@
   the same row}
+\fxwarning{SKB: Will try.
+Although I still do not understand, what the residual is telling me and why the wages are so high.
+Are the wages in EEK?
+What does ET stand for?
+The table needs more explanation or at least a proper legend.}
 The table shows that the picture is in fact quite complex.  We can see
@@
 that.}
+\fxwarning{SKB: You removed the cv.ee already?
+I only see stuff using data from Integration Monitor Survey 2008.
+I did not do these analyses nor do I have the data to repeat the analyses for the latest edition of the Integration Monitor Survey.
+The cv.ee might have been interesting or useful, if it was done properly documented. But that might warrant another section or even another paper. See \cite{fabo+2017E} for more on that.
+}
 

### 2018-07-10 paper/ijm.tex
Added table and figure to section 7

@@
 The table needs more explanation or at least a proper legend.}
+
 The table shows that the picture is in fact quite complex.  We can see
@@
 \end{table}
+\fxwarning{SKB: Copied and modified table above. }
+\begin{table}[ht]
+	\centering
+	\caption{Average wage and time-trend corrected language parameter across
+		location and education groups for Russian men}
+	\begin{tabular}{lrlrrr}
+		\toprule
+		Tallinn & education & ET & wage & parameter & \# obs \\ 
+		\midrule
+		Tallinn & $<$ HS & 0 & 334 & -0.16\onepc & 255 \\ 
+		Tallinn & $<$ HS & 1 & 424 & -0.08 & 219 \\ 
+%		Tallinn & HS     & 0 &476 & 0.05 & 1292 \\ 
+		Tallinn & HS      & 1 & 512 & -0.05 \fivepc & 1296 \\ 
+		Tallinn & college & 0 & 520 & -0.02 & 212 \\ 
+		Tallinn & college & 1 & 737 & 0.05 & 518 \\ 
+		Ida-Viru & $<$ HS & 0 & 396 &  -0.20\onepc & 379 \\ 
+		Ida-Viru & $<$ HS & 1 & 269 & -0.23\onepc & 20 \\ 
+		Ida-Viru & HS     & 0 & 337 & -0.23\onepc & 1889 \\ 
+		Ida-Viru & HS      & 1 & 368 & -0.21\onepc & 252 \\ 
+		Ida-Viru & college & 0 & 451 & -0.07 & 246 \\ 
+		Ida-Viru & college & 1 & 493 & -0.06 & 154 \\ 
+		other   & $<$ HS & 0 & 279 & -0.23\onepc & 83 \\ 
+		other   & $<$ HS & 1 & 334 & -0.19\onepc & 212 \\ 
+		other   & HS     & 0 & 378& -0.13\onepc & 353 \\ 
+		other   & HS      & 1 & 389 & -0.09\onepc & 713\\ 
+		other   & college & 0 & 788 & 0.03 & 32\\ 
+		other   & college & 1 & 414 & -0.11 & 110 \\ 
+		\bottomrule
+	\end{tabular}
+	\label{tab:loc-lang-edu_m3}
+\end{table}
+
+\fxwarning{SKB: Added graph showing the same parameter estimates. Maybe a better formatted graph like this shows the story better than a table}
+\begin{figure}[hbtp]
+	\centering
+	\caption{Coefficient plot of Model 3 for Russian Men separated by Region and Education}
+	\label{fig:russianmenlanguagecoefsm3}
+	\includegraphics[width=1.0\linewidth]{russian_men_language_coefs_m3}
+\end{figure}
 
 We can conclude the table~\ref{tab:loc-lang-edu} that our
-most suprising finding, no positive effect of Estonian language
+most surprising finding, no positive effect of Estonian language
 skills for Russian men, is primarily driven by workers with

### 2018-07-18 paper/ijm.tex
Update ijm.tex
index g removed from (1)
Update ijm.tex
Add another figure showing gdp growth per year

@@
 \renewcommand{\thesection}{\arabic{section}}
-\renewcommand{\thesubsection}{\thesection\arabic{subsection}}
+\renewcommand{\thesubsection}{\thesection.\arabic{subsection}}
 
@@
 transitioned to a market economy, later it's importance
-declined but remained sizable.
+declined but remained sizeable.
 
@@
 re-oriented to the Western markets and has been growing rapidly since
-the mid-1990s.  
+the mid-1990s.  \Cref{fig:gdp_growth} indicates that the Estonian economy grew around 7\% per year before the financial crisis in 2008 and after that grew at a lower rate around 3\% per year.
 \fxwarning{ot: a few numbers about economic growth would be good}
+\fxwarning{SKB: I added rather a figure. Pure numbers or table might not give the best impression of the growth.}
+\begin{figure}[h]
+	\centering
+	\caption{GDP growth per year for Estonia}\label{fig:gdp_growth}
+	\includegraphics[width=0.6\linewidth]{gdp_growth_per_year.eps}
+	\caption*{Source: Worldbank - World Development Indicators, Series  NY.GDP.MKTP.KD.ZG}
+\end{figure}
   As
@@
 	\begin{split}
-		y_{it} ^{g} = &\: \alpha^{g}{}' \vec{X}_{it}^{g} + \vec{\beta}^{g}{}' \cdot \vec{L}_{it}^{g} +
+		y_{it} ^{g} = &\: \alpha^{g}{}' \vec{X}_{it}^{g} + \vec{\beta}^{g}{}' \vec{L}_{it}^{g} +
 		\eta_{i}^{g} +
-		\upsilon_{t}^{g} + \epsilon_{it}^{g},
+		\upsilon_{t} + \epsilon_{it}^{g},
 	\end{split}

### 2018-07-19 paper/ijm.tex
Reacted to one more comment about descriptive table
Added couple of references which might be useful for the CEE comparison stuff

@@
 %Start here CEE stuff for now
+Comparing the results for Estonia with other Central Eastern European (CEE) countries and former Soviet Union countries is rather difficult due to the lack of data about language skills.
+Information about ethnicity is widely available, but no information about individual native and foreign language skills.
+For example, the Latvian Labour Force Survey does not (did not) contain questions regarding language skills.
+While the language policies in the Baltic states are discussed in \cite{Hogan-Brun2008,Hogan-Brun2007}, the implications for the labour market are not discussed.
+\cite{Grasmane2011} use information from a survey conducted at the Latvian University of Agriculture with undergraduate, master, doctoral students to find out  how foreign language skills impact employability.
+They find that the better foreign language skills are related to higher willingness to work abroad.
+\cite{Alan2015} \fxnote{SKB: Quite detailed article about Russian language proficiency in three former Soviet Union states. Needs further comments from us and find similar articles.}
 \cite{Kahanec2009} provide an overview about \enquote{the roles of foreign origin and citizenship in the labor markets of Eastern and Eestern[sic] Member States of the EU} \dots and use the EU Survey of Income and Living Conditions (EU-SILC) dataset.
@@
 \fxwarning{OT: can you add variable 'year' in this table?  I know it feels a little weird but is great to show time trends.}
+\fxwarning{SKB: What do you mean with time trends? Which value should a ``year'' variable take? Give me an example, since I don't understand what you want. }
 

### 2018-07-20 paper/ijm.tex
better wage residuals table and discussion in the 7th section

@@
 
+\DeclareUnicodeCharacter{2010}{-}% support older LaTeX versions
 \thanksfootextra{}{\hfill}
@@
 schools while teaching Russian in Estonian-language schools declined.
-Since 2007, all Russian high-schools have to teach part of the
+Since 2007, all Russian high schools have to teach part of the
 curriculum in Estonian \citep{lindemann+saar2011Russian2ndGeneration}.
@@
 Russian men earn virtually no Estonian language premium while women do--warrants a
-deeper look at the data.  We compute the average wage for the Russian male wage-earners
+deeper look at the data.  We split the average wage for the Russian male wage-earners
 along the three
-dimensions: Estonian language skills, residence in Tallinn metro area,
-and education.  The metropolitan area is one of the two major regions
+dimensions: Estonian language skills (\emph{EST 0} and \emph{EST 1}),
+residence in Tallinn metro area (\emph{Tallinn} and \emph{Other}),
+and education (\emph{< HS}, \emph{HS}, \emph{College Degree}).  The metropolitan area is one of the two major regions
 where the Russian-speaking population is concentrated, and it's
-booming economy may be very different from that in the North-East.
+booming economy may be very different from the other such region, the
+North-East (Ida-Virumaa), and the rest of the country.
 Even more, while Russians form a large minority in and around Tallinn,
 they are in majority in the North-East.  
-In addition, to correct very strong wage and language skill trends through these
-years, we also present the average
-residuals from an OLS regression that explains log wage by year fixed
-effects (Table~\ref{tab:loc-lang-edu}). 
-\fxwarning{ot: Sven, can you redo this table?  Use exactly the same
-  sample as you used.  Would also be good to put both et1 and et0 on
-  the same row}
-\fxwarning{SKB: Will try.
-Although I still do not understand, what the residual is telling me and why the wages are so high.
-Are the wages in EEK?
-What does ET stand for?
-The table needs more explanation or at least a proper legend.}
-
-The table shows that the picture is in fact quite complex.  We can see
+In order to correct for the strong wage and language skill trends
+through the observation period, we do not present the average wage,
+but instead the respective OLS residuals where we explain the wage by year fixed
+effects and include no other explanatory variables (Table~\ref{tab:loc-lang-edu}).
+
+The table shows that the picture is in fact complex.  We can see
 that there is little to no gain from Estonian skills for the
-largest group, high-school educated workers.  Even more, outside of
+largest group of workers, those with a high school degree.  Even more, outside of
 the metropolitan area, the lowest and highest education groups
@@
     location and education groups for Russian men}
-  \begin{tabular}{lrlrrr}
+  \begin{tabular}{llrrrr}
     \toprule
-    Tallinn & education & ET & wage & residual & \# obs \\ 
+    & & &\multicolumn{2}{c}{Log Wage}\\
+    Location & Education & \# Observations & EST 0 & EST 1 & Premium\\
     \midrule
-    Tallinn & $<$ HS & 0 & 4313.38 & -0.19 & 255 \\ 
-    Tallinn & $<$ HS & 1 & 5351.11 & -0.05 & 219 \\ 
-    Tallinn & HS     & 0 & 5803.21 & 0.05 & 1292 \\ 
-    Tallinn & HS      & 1 & 5666.77 & 0.05 & 1296 \\ 
-    Tallinn & college & 0 & 6562.57 & 0.16 & 212 \\ 
-    Tallinn & college & 1 & 8453.14 & 0.30 & 518 \\ 
-    other   & $<$ HS & 0 & 3877.84 & -0.13 & 461 \\ 
-    other   & $<$ HS & 1 & 4496.62 & -0.18 & 230 \\ 
-    other   & HS     & 0 & 4838.65 & -0.09 & 2233 \\ 
-    other   & HS      & 1 & 5351.51 & -0.05 & 960 \\ 
-    other   & college & 0 & 6283.38 & 0.17 & 278 \\ 
-    other   & college & 1 & 6072.06 & 0.13 & 263 \\ 
+    Tallinn & $<$ HS & 399 & -0.20 & -0.01 & 0.19 \\ 
+    Tallinn & HS & 2164 & 0.07 & 0.04 & -0.03 \\ 
+    Tallinn & College Degree & 610 & 0.15 & 0.30 & 0.15 \\ 
+    Other & $<$ HS & 501 & -0.12 & -0.12 & -0.01 \\ 
+    Other & HS & 2658 & -0.10 & -0.07 & 0.03 \\ 
+    Other & College Degree & 429 & 0.17 & 0.11 & -0.06 \\ 
     \bottomrule
   \end{tabular}
+  \begin{flushleft}
+    Notes: \emph{Log Wage} refers to regression residual where log
+    wage is explained by year fixed effects.  \emph{EST0} and
+    \emph{EST 1} are mean values for those who cannot, and who can,
+    speak Estonian; $\text{Premium} = \text{EST 1} - \text{EST 0}$.
+    Education level \emph{< HS} refers to less than high school
+    degree, \emph{HS} is the high school degree as the highest
+    completed education level.
+  \end{flushleft}
   \label{tab:loc-lang-edu}
 \end{table}
-\fxwarning{SKB: Copied and modified table above. }
-\begin{table}[ht]
-	\centering
-	\caption{Average wage and time-trend corrected language parameter across
-		location and education groups for Russian men}
-	\begin{tabular}{lrlrrr}
-		\toprule
-		Tallinn & education & ET & wage & parameter & \# obs \\ 
-		\midrule
-		Tallinn & $<$ HS & 0 & 334 & -0.16\onepc & 255 \\ 
-		Tallinn & $<$ HS & 1 & 424 & -0.08 & 219 \\ 
-%		Tallinn & HS     & 0 &476 & 0.05 & 1292 \\ 
-		Tallinn & HS      & 1 & 512 & -0.05 \fivepc & 1296 \\ 
-		Tallinn & college & 0 & 520 & -0.02 & 212 \\ 
-		Tallinn & college & 1 & 737 & 0.05 & 518 \\ 
-		Ida-Viru & $<$ HS & 0 & 396 &  -0.20\onepc & 379 \\ 
-		Ida-Viru & $<$ HS & 1 & 269 & -0.23\onepc & 20 \\ 
-		Ida-Viru & HS     & 0 & 337 & -0.23\onepc & 1889 \\ 
-		Ida-Viru & HS      & 1 & 368 & -0.21\onepc & 252 \\ 
-		Ida-Viru & college & 0 & 451 & -0.07 & 246 \\ 
-		Ida-Viru & college & 1 & 493 & -0.06 & 154 \\ 
-		other   & $<$ HS & 0 & 279 & -0.23\onepc & 83 \\ 
-		other   & $<$ HS & 1 & 334 & -0.19\onepc & 212 \\ 
-		other   & HS     & 0 & 378& -0.13\onepc & 353 \\ 
-		other   & HS      & 1 & 389 & -0.09\onepc & 713\\ 
-		other   & college & 0 & 788 & 0.03 & 32\\ 
-		other   & college & 1 & 414 & -0.11 & 110 \\ 
-		\bottomrule
-	\end{tabular}
-	\label{tab:loc-lang-edu_m3}
-\end{table}
-
-\fxwarning{SKB: Added graph showing the same parameter estimates. Maybe a better formatted graph like this shows the story better than a table}
-\begin{figure}[hbtp]
-	\centering
-	\caption{Coefficient plot of Model 3 for Russian Men separated by Region and Education}
-	\label{fig:russianmenlanguagecoefsm3}
-	\includegraphics[width=1.0\linewidth]{russian_men_language_coefs_m3}
-\end{figure}
 
@@
 skills for Russian men, is primarily driven by workers with
-high-school degree.  It also suggests that highly educated workers in
+high school degree.  It also suggests that highly educated workers in
 the metropolitan area enjoy, in fact, a substantial language premium.
@@
 The previous results can be explained by two hypotheses: first,
-Russian--speaking men, at least those with high-school degree as their
-highest completed education, are working
+Russian--speaking men, at least those with high school degree as their
+highest completed education level, are working
 primarily in Russian language environment (ethnic segregation) while this is not true for
@@
 little communication requirements (gender segregation).
-
 To shed some additional light on these hypotheses, we use data
@@
 use Estonian while the opposite is true for English.
-Table~\ref{tab:environment_model} presents the regression results
-where we estimate the likelihood of having the need and using Estonian at work
+Table~\ref{tab:environment_model} presents the corresponding regression results
+where we estimate the likelihood of having the need, and using, Estonian at work
 while
@@
 intriguing observation is that the largest group of
-Russian men, high-school graduates, earn virtually no income premium if fluent in Estonian,
+Russian men, high school graduates, earn virtually no income premium if fluent in Estonian,
 the majority and the official language of the country, while ability

### 2018-07-20 paper/ijm.tex
Minor changes to CEE part

--- 2018-07-19 paper/ijm.tex
@@
 They find that the better foreign language skills are related to higher willingness to work abroad.
-\cite{Alan2015} \fxnote{SKB: Quite detailed article about Russian language proficiency in three former Soviet Union states. Needs further comments from us and find similar articles.}
+\cite{Alan2015} \enquote{During the Soviet era, proficiency in the Russian language was often a ticket to
+	attractive employment opportunities in the member republics. Does it still contribute
+	to securing employment in the former Soviet republics after two decades of transition?
+	Using data from Armenia, Azerbaijan and Georgia in the years 2008–2010,
+	this paper demonstrates that Russian language skills remain economically valuable.
+	The baseline estimates suggest that Russian language skills increase probability of
+	employment by about 6 (males) and 9 (females) percentage points. Our results bear
+	important implications for the ongoing debates on language policies in the post-
+	Soviet countries.} \fxnote{SKB: Quite detailed article about Russian language proficiency in three former Soviet Union states. Needs further comments from us and find similar articles.}
 \cite{Kahanec2009} provide an overview about \enquote{the roles of foreign origin and citizenship in the labor markets of Eastern and Eestern[sic] Member States of the EU} \dots and use the EU Survey of Income and Living Conditions (EU-SILC) dataset.

### 2018-07-20 response-to-reviewers.tex
model description improved

@@
     Section 7), and it appears the story is somewhat more nuanced.
-    \fxwarning{ensure it's also in the discussion}
   \end{response}
@@
   estimating the time trend is very short.
-  \debug{SKB: Svetlana modified the equations a bit. I added another table,
-  which summarises the models.}
+
+  \begin{response}
+    We have improved and simplified the description of the model and related variables.
+  \end{response}
+  \fxwarning{ot: should you cluster if you do random effects?}
 \item - The tables and figures should have notes that explain in more

### 2018-07-20 paper/ijm.tex
model description improved

--- 2018-07-20 paper/ijm.tex
@@
 
-We describe the outcome of individual $i$ belonging to group $g$ (either Estonian
-or Russian) at year $t$ as
+We describe the outcome of individual $i$ at year $t$ as
 \begin{equation}
@@
 	\begin{split}
-		y_{it} ^{g} = &\: \alpha^{g}{}' \vec{X}_{it}^{g} + \vec{\beta}^{g}{}' \vec{L}_{it}^{g} +
-		\eta_{i}^{g} +
-		\upsilon_{t} + \epsilon_{it}^{g},
+		y_{it} = &\: \vec{\alpha}{}' \vec{X}_{it} + \vec{\beta}{}' \vec{L}_{it} +
+		\eta_{i} +
+		\upsilon_{t} + \epsilon_{it},
 	\end{split}
@@
 where $y$ is the outcome (either unemployment indicator
-or logarithm of net monthly wage), $\vec{X}$ are the other individual
-characteristics; $\vec{L}$ is the vector of
-language skill descriptors, $\eta_{i}^{g}$ is the individual-specific effect, $\upsilon_{t}$ are the year dummies and $\epsilon_{it}^{g}$
-is the idiosyncratic error term. 
-\fxerror{ot: what's the eta term?  do you do random effects?}
-\fxerror{SKB: Eta should be the individual specific random effect.
-We cluster the standard errors at the individual level, hence estimate a random-effect model, although not a panel random-effect model.}
-\fxerror{ot: why does $\upsilon$ have index $g$?}
-\fxerror{SKB: Should be an error, probably index $g$ was just added to everything.}
+or logarithm of net monthly wage), $\vec{X}$ are the individual and
+workplace descriptors; $\vec{L}$ is the vector of
+language skill descriptors, $\eta_{i}$ is the individual random effect, $\upsilon_{t}$ are the year dummies and $\epsilon_{it}$
+is the idiosyncratic error term.  We estimate separate models for
+Estonians and Russians.
+\fxnote{ot: if you do random effects--do you still have to cluster?}
 As we use panel data, we cluster the
@@
 
-We estimate three models that differ in terms of the number of
+We estimate three models that differ in
 control variables. The first specification only includes the language skills
@@
 status, indicator for inter-ethnic marriage, having kids up to 17 years
-old) and county of residence.  
+old), and county of residence.  
 Finally, the third specification also adds industry, occupation, and other

### 2018-07-20 response-to-reviewers.tex
captions/notes improved

@@
   variables, the sample period and the age restriction applied.
-  \debug{SKB: I added this information to the tables and the figures. The descriptions might need some polishing still.}
-\item 
-- Page 4: You write that you are only analysing individuals who are
+
+  \begin{response}
+    We have improved the captions and notes.
+  \end{response}
+
+\item page 4: You write that you are only analysing individuals who are
 working or actively looking for a job, but in line 35 on the same page

### 2018-07-20 paper/ijm.tex
captions/notes improved

@@
 \newcommand{\modelThreeAdd}{industry, occupation, ownership type of company, number of workers in company, working in the public sector, experience in company}	
-\newcommand{\restrictions}{The sample period is from year 2000 to year 2012. Sample is limited to persons
-	25-55 year old.}
+\newcommand{\restrictions}{Only years 2000--2012 and individuals 25-55
+  year old included in the sample.}
 \newcommand{\agerestrictions}{25-55 year olds only.}
@@
 the mid-1990s.  \Cref{fig:gdp_growth} indicates that the Estonian economy grew around 7\% per year before the financial crisis in 2008 and after that grew at a lower rate around 3\% per year.
-\fxwarning{ot: a few numbers about economic growth would be good}
-\fxwarning{SKB: I added rather a figure. Pure numbers or table might not give the best impression of the growth.}
 \begin{figure}[h]
 	\centering
-	\caption{GDP growth per year for Estonia}\label{fig:gdp_growth}
+	\caption{Annual GDP growth in Estonia}\label{fig:gdp_growth}
 	\includegraphics[width=0.6\linewidth]{gdp_growth_per_year.eps}
@@
 \end{figure}
+\fxnote{ot: remove the cryptic series?}
   As
@@
 	\label{tab:descriptive}%
-	\caption*{\small
-		Workplace--related variables are reported for employed individuals,
-		other variables for the complete workforce.  Sample is limited to persons
+        \newgeometry{textwidth=0.75\paperheight}
+        \begin{flushleft}
+          \small Workplace--related variables are reported for
+          employed individuals, other variables for the complete
+          workforce.  Sample is limited to persons
           25-55 year old.\\
-		\emph{RUS 0} refers to individuals who cannot speak Russian and
-		\emph{RUS 1} to those who can. Analogously for English
-                (ENG) and
+          \emph{RUS 0} refers to individuals who cannot speak
+          Russian and \emph{RUS 1} to those who can. Analogously for
+          English (ENG) and
           Estonian (EST).\\
-		Primary sector = Agriculture,
-		Fishing, Mining \\ Secondary sector = Manufacturing,
-		Construction, Electricity \\ Tertiary (service) sector =
-		Wholesale, Hotels, Transport, Financial intermediation, Real
-		estate \\ Public sector = Public administration, Education,
-		Health}
+          Primary sector = Agriculture, Fishing, Mining; Secondary
+          sector = Manufacturing, Construction, Electricity;
+          Tertiary (service) sector = Wholesale, Hotels, Transport,
+          Financial intermediation, Real estate; Public sector =
+          Public administration, Education, Health
+        \end{flushleft}
 \end{sidewaystable}%
@@
 	\begin{center}
-		\caption{Estimation results for unemployment.}
+		\caption{Estimation results for unemployment probability.}
 		\label{tab:unemployment_estimation_by_sex_and_ethnic_same_sample} %SKB 04.07.2018 14:22:Not yet updated only prepared
@@
 		\begin{flushleft}
-			\caption*{ \legend \\ Standard errors (clustered on individuals) in parentheses.\\  Individual characteristics are \modelTwo. \\ \restrictions}
+                  \legend \\ Standard errors (clustered on individuals) in parentheses.\\  Individual characteristics are \modelTwo. \\ \restrictions
 		\end{flushleft}
@@
 		\begin{flushleft}
-			\caption*{\legend \\ Standard errors (clustered on individuals) in parenthesis \\ Individual characteristics are \modelTwo. \\ Workplace characteristics are \modelThreeAdd. \\ \restrictions}
+                  \legend \\ Standard errors (clustered on individuals) in parenthesis \\ Individual characteristics are \modelTwo. \\ Workplace characteristics are \modelThreeAdd. \\ \restrictions
 		\end{flushleft}
@@
 	\centering
-	\caption{The trend over time across the age groups (ethnic Estonians)}
+	\caption{Estimated trend over time across the age groups}
 	\begin{tabular}{lccc|cc c}
@@
 	\end{tabular}
-
-	\caption*{\legend \\ Standard errors (clustered on individuals) in parenthesis}
+        \begin{flushleft}
+          \legend \\ Standard errors (clustered on individuals) in
+          parenthesis \\
+          Individual characteristics are \modelTwo. \\
+          \restrictions
+        \end{flushleft}
 	\label{tab:age_group_trend}
@@
 	\begin{flushleft}
-		Note: percentage of respondents who respond affirmatively
+		Note: percentage of respondents (Russian speakers) who respond affirmatively
 	\end{flushleft}

### 2018-07-20 paper/ijm.tex
hint to inactivity removed in 3.1

@@
 individuals who are either working or actively looking for a job.
-
 The dataset allows us to control for standard personal
@@
 and family status.  The central variables in this study are the same
-as in \citep{Leping2008}:
+as in \citet{Leping2008}.
 
@@
 
-The labor market outcomes we analyze are income, the ``last salary on the main job'' and
-labor force status (working, unemployed or inactive).
-
-The survey includes self-reported language skills on languages used at
-home, and all other languages they understand.  The respondents are
-give some guidance in assessing their skills, they can report either
+The labor market outcomes we analyze are income, the ``last salary on the main job'', and
+labor force status (working or unemployed).
+
+The survey includes self-reported language skills on all languages
+respondents can understand or communicate.  The questionnaire 
+gives some guidance in assessing the skills, one can report either
 no knowledge, understanding, speaking, writing, or using the
@@
 SaarPoll and focuses on
-ethnic relations in Estonia.  The sample size is 1500,
-500 of the respondents consider themselves not ethnic Estonians.  We analyse
+ethnic relations in Estonia.  The sample size is 1500, out of which 
+500 respondents do not consider themselves ethnic Estonians.  We analyse
 two questions: ``which is the language of communication at your

### 2018-07-20 response-to-reviewers.tex
hint to inactivity removed in 3.1
models have the same number of obs

@@
 is included in your sample.
-\item 
-  \debug{ot: let's make it equal (i.e. remove all observations with
-    any of the variables missing.  Add a footnote that when we
-    included all the variables, we still got the same results.}
-\debug{SKB: I estimated the models and updated the tables with occupation added to Model 3. Added footnote linking to original tables with \enquote{unrestricted} observations}
-  The sample size for different specification of the same analysis
+
+\begin{response}
+  We have removed the erroneous mentioning of inactivity 
+\end{response}
+\item  The sample size for different specification of the same analysis
   should be the equal. Otherwise it is difficult to conclude whether the
@@
   controls or form the change in the size of the estimation sample.
+  \begin{response}
+    Now we report the models with identical results.  The original
+    (very similar)
+    results are still available in Appendix.
+  \end{response}
+
 \item 

### 2018-07-20 paper/ijm.tex
models have the same number of obs

@@
   restrict both models to have the same number of observations as
-  requested by a reviewer. The unrestricted table is in the appendix \cref{tab:unemployment_estimation_by_sex_and_ethnic}.}
+  requested by a reviewer. The unrestricted results are qualitatively
+  very similar (\cref{tab:unemployment_estimation_by_sex_and_ethnic} in Appendix).}
 The
@@
 \subsection{Wage}
-%SKB: Adding occupation to Model 3 reduces the effects drastically. Beforehand I somehow forgot to add it to the estimation. Now occupation is included as it should have been in the first place.
 \label{subsec:basic_model_wage}
@@
   restrict both models to have the same number of observations as
-  requested by a reviewer.  The unrestricted table is in the appendix \cref{tab:wage_estimation_by_sex_and_ethnic}.}
+  requested by a reviewer.  The unrestricted results are qualitatively
+  very similar (\cref{tab:wage_estimation_by_sex_and_ethnic} in Appendix).}
 The table

### 2018-07-20 response-to-reviewers.tex
fixed the all resutls tables stuff (U still missing)

@@
 \end{enumerate}
+
+\begin{response}
+  At a reviewers request, we have added the full regression tables in
+  Appendix.  We agree these figures are valuable, in particular in the
+  light of the striving toward the replicable research in the recend
+  years, but we think they fit better in an online supplement.
+\end{response}
 
@@
   controls or form the change in the size of the estimation sample.
+
   \begin{response}
@@
 
-\item 
-- In the paper, you are only showing the results of the variables of
+\item In the paper, you are only showing the results of the variables of
   interest. I suggest to provide tables including all coefficients (not
@@
   models.
-\debug{SKB: Will add them after I figured out how to present the results nicely formatted.
-It boils down to finding the right options for the \enquote{estout} or the \enquote{outtex/outreg} user provided package in Stata.
-I could do the formatting in Excel myself, but I prefer the Stata solution.
-}
-\debug{SKB: I included a first try in the appendix, which is still not perfect. The labels for the variables are not existing yet or not correct. The tables are not linked yet to the main text.}
-\debug{SKB: Should I include tables for unemployment as well? This would blow up the number of pages even further. I could drop the standard errors to save space. Let me know what would be best.}
+
+  \begin{response}
+    We have added the full wage results in Appendix.  We think these
+    tables would be more suitable for an online supplement.
+    \fxerror{ot: if we do wage, we should also do unemployment}
+  \end{response}
 \item 

### 2018-07-20 paper/ijm.tex
fixed the all resutls tables stuff (U still missing)

@@
 we only estimate the first two models.
-\fxnote{Actually, I tried to estimate Model 3 as well for unemployment probability.
-The language coefficients become insignificant after controlling for industry and occupation.
-Hence, Estonian language fluency lowers the unemployment probability only if workplace characteristics are ignored.
-Since nobody questioned this result during review, we should maybe not mention it now.
-}
 
@@
 The central results for unemployment regressions are given in
-\cref{tab:unemployment_estimation_by_sex_and_ethnic_same_sample}.\footnote{We
+\cref{tab:unemployment_estimation_by_sex_and_ethnic_same_sample}\footnote{We
   restrict both models to have the same number of observations as
   requested by a reviewer. The unrestricted results are qualitatively
-  very similar (\cref{tab:unemployment_estimation_by_sex_and_ethnic} in Appendix).}
+  very similar (\cref{tab:unemployment_estimation_by_sex_and_ethnic}
+  in Appendix).}
+(the full results are available in Section~\ref{sec:unemployment_full}
+in Appendix).
+\fxerror{ot: if we have wage, we should also have unemployment}
 The
@@
 central wage regression
-results.\footnote{As above, we
+results\footnote{As above, we
   restrict both models to have the same number of observations as
   requested by a reviewer.  The unrestricted results are qualitatively
-  very similar (\cref{tab:wage_estimation_by_sex_and_ethnic} in Appendix).}
+  very similar (\cref{tab:wage_estimation_by_sex_and_ethnic} in
+  Appendix).}
+(The full results are given in Section~\ref{sec:wage_full} in Appendix).
 The table

### 2018-07-20 response-to-reviewers.tex
consistently use 'obsrevations' instead of 'obs'

@@
   \end{response}
-\item 
-- All tables: Be consistent in the description of your tables. The
+\item All tables: Be consistent in the description of your tables. The
 table notes and the labels for e.g., "observations", are inconsistent
 across the different tables.
-\debug{SKB: Fixed. Changed obs to Observations in tables}
-\item
-  \debug{ot: this was because of both 'B. Chiswick' and
-    'B. R. Chiswick' in the bibtex file, and bibtex wanted to
-    distinguish between these two guys.}
- Page 1: To cite Chiswick you are using different versions
+
+\begin{response}
+  We now consistently talk about ``observations''.
+\end{response}
+
+\item Page 1: To cite Chiswick you are using different versions
 (B. Chiswick and B. R. Chiswick).

### 2018-07-20 response-to-reviewers.tex
unemployment rate/probability

@@
 
-\item 
-- Page 2, line 58: Not the unemployment rate, but the probability of
+\item Page 2, line 58: Not the unemployment rate, but the probability of
   being unemployed is reduced.
-\debug{SKB: Got fixed by Svetlana I think.}
+
+  \begin{response}
+    We now use ``unemployment probability'' when talking about
+    individual outcomes and leave ``unemployment rate'' solely for
+    describing group outcomes.
+  \end{response}
+
 \item 

### 2018-07-20 paper/ijm.tex
unemployment rate/probability

@@
 is the sole official language.\\
-\textbf{Design/methodology/approach --} The authors use the Estonian Labour Force Survey from 1989 to 2012 to study the impact of language skills on unemployment (probability) and wages.\\
+\textbf{Design/methodology/approach --} The authors use the Estonian Labour Force Survey from 1989 to 2012 to study the impact of language skills on unemployment probability and wages.\\
 \textbf{Findings --} For men, fluency in
-Estonian is related to approximately 5 percentage points lower unemployment, but to virtually no income
+Estonian is related to approximately 5 percentage points lower
+unemployment probability, but to virtually no income
 premium. English skills are associated with a
@@
 majority and minority language skills, and English for both
-wage and unemployment.  We analyse Estonia, a former Soviet republic
+wage and unemployment probability.  We analyse Estonia, a former Soviet republic
 and now a rapidly growing and
@@
 English is more closely associated with unemployment than Russian:
-Estonians fluent in English have in average 5.0 percent unemployment
+Estonians fluent in English have in average 5.0 percent unemployment rate
 while those who are not fluent have 8.8 percent.  The difference
@@
 We use linear probability models (LPM) to estimate the relationship between
-language skills and unemployment, mainly in order to avoid unnecessary parametric
+language skills and unemployment probability, mainly in order to avoid unnecessary parametric
 assumptions in the corresponding binary choice models.\footnote{The
@@
 Knowledge of Russian is not associated with less unemployment for
-Estonian men, and is even related to a slightly higher unemployment
+Estonian men, and is even related to a slightly higher unemployment probability
 for Estonian women. The latter outcome may be related to omitted
@@
 
-The effect of language fluency on unemployment is shown on
+The effect of language fluency on unemployment probability is shown on
 Figure~\ref{fig:long-run_unemployment}, and on wage on
@@
 	}
-	\caption{The effect of language fluency on unemployment, 1992--2012. \\ Control variables are \modelTwo. \agerestrictions }
+	\caption{The effect of language fluency on unemployment probability, 1992--2012. \\ Control variables are \modelTwo. \agerestrictions }
 	\label{fig:long-run_unemployment}
@@
 to speak the language is related to a substantially
-lower unemployment rate.
+lower unemployment probability.
 Our analysis supports \citet{YaoandOurs2015}, and \citet{Lindemann2013} findings that

### 2018-07-20 response-to-reviewers.tex
the fuzzy paragraph about integration at the low end of job market addressed

@@
 
-\item 
-- Page 3, lines 46-50: You are using a comma as the decimal separator, but in all your tables you are using a point. Please use a point everywhere. 
-\debug{SKB: Fixed by someone.}
+\item Page 3, lines 46-50: You are using a comma as the decimal separator, but in all your tables you are using a point. Please use a point everywhere.
+
+  \begin{response}
+    We now consistently use period as decimal separator and comma as
+    thousands' separator.
+  \end{response}
+
 \end{enumerate}
@@
   literature.
-\item 
-\debug{OT: seems like I have to address this.}
-In the Discussion and Concluding Remarks section they state that
+
+  \begin{response}
+    No response neede here.
+  \end{response}
+
+\item In the Discussion and Concluding Remarks section they state that
   “The lower end labour market, associated with frequent unemployment,
@@
   and make it clearer exactly where these results come from.
+
+  \begin{response}
+    We have completely re-phrased this paragraph and rely more on our
+    results (and literature) now.
+  \end{response}
+
 \item In Table 3 I am perplexed how the number of observations increases as more restrictions are added to the model.

### 2018-07-20 paper/ijm.tex
the fuzzy paragraph about integration at the low end of job market addressed

@@
 intriguing observation is that the largest group of
-Russian men, high school graduates, earn virtually no income premium if fluent in Estonian,
+Russian men, high school graduates, earn virtually no income premium
+from being fluent in Estonian,
 the majority and the official language of the country, while ability
@@
 the labour market is segmented between ethnic and gender lines.
-However, we find that ethnic segregation is less prevalent in the male
-labour market.
-This suggests for majority of Russian speaking men, Estonian
+However, we find that ethnic segregation is more prevalent in the male
+labor market.
+It is true that for majority of Russian speaking men, Estonian
 language gives a distinct advantage by facilitating hiring by
@@
 separately.  We find some evidence that female labor market is less
-segregated along ethnic lines, and women are more frequently employed in jobs in which they need Estonian
-language more, such as working in a direct contact with customers.
+segregated along ethnic lines, women are also more frequently employed
+in jobs where they need Estonian
+language more, possibly because of being in a direct contact with customers.
 
@@
 important in the female labour market.  Unfortunately, the current data
-does not let us to assess whether is due to decreasing segregation, or
+does not let us assess whether this is due to decreasing segregation,
+or due to
 economy--wide rise of the importance of Estonian language.  No such trend is visible for
-men suggesting that 20 years--almost a generation after the collapse of Soviet Union, the
+men suggesting that 20 years---almost a generation---after the collapse of Soviet Union, the
 labor market integration is still not complete.
@@
 English language is related to a substantial income premium but
-virtually to no effect on unemployment.  This is similar to findings by
+to virtually no effect on unemployment.  This is similar to findings by
 \citet{ginsburgh+prieto-rodriguez2011ILRR} and
-\citet{beblavy+2016CEPS} who show that English is more important at better paid
+\citet{fabo+2017E} who show that English is more important at better paid
 jobs.  In contrast, our outcomes suggest that English has little use
@@
 Note also that for
-English, we are able to explain a substantial part of the raw effect
+English we are able to explain a substantial part of the raw effect
 by individual characteristics, suggesting that the true causal effect
@@
 The study has a number of limitations.  Although we believe that our
-estimates are good indicators of a causal relationship, we cannot 
-claim this as our data do not contain strong enough instruments.
+estimates are good indicators of a causal relationship, it is still
+somewhat uncertain as our data do not contain strong instruments.
 In particular, as individual characteristics are able to explain a
 large part of English returns, we suppose part of the remaining effect
-may also related to an ability bias.  Another weak point in the current
+may also related to the ability bias.  Another weak point in the current
 data is using the self-reported language

### 2018-07-20 paper/ijm.tex
communication quality responses

@@
 of the local majority language for immigrants.  It is well known that
-language skills are associated with a substantial an income premium
+language skills are associated with a substantial income premium
 between 5 and 35 percent
@@
 associated with a very large wage premium early after the country
-transitioned to a market economy, later it's importance
+transitioned to a market economy, later its importance
 declined but remained sizeable.
@@
 In contrast, the sole language that plays a role in determining
-unemployment is Estonian.  It's fluency is associated with
+unemployment is Estonian.  Its fluency is associated with
 approximately 5 percentage points lower probability of being unemployed.
 These results suggest that Estonian labour market is
-segmented both along gender and the ethnic boundaries, men
+segmented both along gender and the ethnic boundaries, and men are
 more likely occupied in less communication-intense jobs.
@@
 As age is a central determinant how major economic and political
-reforms influence individual fates, 
+reforms influence individual careers, 
 we also analyze the time trends by age groups
@@
 We repeat the exercise for unemployment models.
-However, as most of the results are not statistically significant, we
-do not report the results here.
+However, due to relatively small groups, most of the results are not
+statistically significant and we
+do not report these here.
 
@@
 Both figures are statistically significant (at 5\% and 10 \% level
-respectively), but not precisely estimated.  We can also see that
+respectively) although the standard errors are large.  We can also see that
 college education is associated by much more Estonian need and usage,

### 2018-07-20 paper/ijm.tex
Minor changes to the CEE part

--- 2018-07-20 paper/ijm.tex
@@
 \newcommand{\modelThreeAdd}{industry, occupation, ownership type of company, number of workers in company, working in the public sector, experience in company}	
-\newcommand{\restrictions}{Only years 2000--2012 and individuals 25-55
-  year old included in the sample.}
+\newcommand{\restrictions}{The sample period is from year 2000 to year 2012. Sample is limited to persons
+	25-55 year old.}
 \newcommand{\agerestrictions}{25-55 year olds only.}
@@
 is the sole official language.\\
-\textbf{Design/methodology/approach --} The authors use the Estonian Labour Force Survey from 1989 to 2012 to study the impact of language skills on unemployment probability and wages.\\
+\textbf{Design/methodology/approach --} The authors use the Estonian Labour Force Survey from 1989 to 2012 to study the impact of language skills on unemployment (probability) and wages.\\
 \textbf{Findings --} For men, fluency in
-Estonian is related to approximately 5 percentage points lower
-unemployment probability, but to virtually no income
+Estonian is related to approximately 5 percentage points lower unemployment, but to virtually no income
 premium. English skills are associated with a
@@
 They find that the better foreign language skills are related to higher willingness to work abroad.
-\cite{Alan2015} \fxnote{SKB: Quite detailed article about Russian language proficiency in three former Soviet Union states. Needs further comments from us and find similar articles.}
-\cite{Kahanec2009} provide an overview about \enquote{the roles of foreign origin and citizenship in the labor markets of Eastern and Eestern[sic] Member States of the EU} \dots and use the EU Survey of Income and Living Conditions (EU-SILC) dataset.
-They\enquote{ mapped and compared the roles of foreign origin and citizenship for labor market performance in Eastern and Western EU Member States.}
-Using Oaxaca and Fairlie decompositions, they show that there is native/non-native divide in the national labour markets \dots.
-They find that \enquote{both foreign origin and citizenship remain important barriers to non-native labor market integration}
-\enquote{In Estonia and Latvia, in particular, employment
-	policies seem to be most relevant for non-immigrant non-citizens. Once employed,
-	non-nativity may play a less negative role in the labor market for some groups,
-	although labor market segmentation remains a significant issue.}
+\cite{Alan2015}  show that Russian language proficiency stills matters for labour market outcomes in three former Soviet Union countries (Armenia, Azerbaijan and Georgia).
+Russian language skills increase the likelihood of being employed between six and nine percentage points.
+Similar articles about other former Soviet Union countries are not known to the authors.
+%\enquote{During the Soviet era, proficiency in the Russian language was often a ticket to
+%	attractive employment opportunities in the member republics. Does it still contribute
+%	to securing employment in the former Soviet republics after two decades of transition?
+%	Using data from Armenia, Azerbaijan and Georgia in the years 2008–2010,
+%	this paper demonstrates that Russian language skills remain economically valuable.
+%	The baseline estimates suggest that Russian language skills increase probability of
+%	employment by about 6 (males) and 9 (females) percentage points. Our results bear
+%	important implications for the ongoing debates on language policies in the post-
+%	Soviet countries.} 
+\fxnote{SKB: Quite detailed article about Russian language proficiency in three former Soviet Union states. Needs further comments from us and find similar articles.}
+\cite{Kahanec2009} provide an overview about the roles of foreign origin and citizenship in the labor markets of CEE Member States of the EU. 
+ They use the EU Survey of Income and Living Conditions (EU-SILC) dataset to  map and compare the roles of foreign origin and citizenship for labor market performance.
+Using Oaxaca and Fairlie decompositions, they show that there is native/non-native divide in the national labour markets which reduces the employment and earnings prospects of men and women with foreign origin and/or citizenship.
+%They find that \enquote{both foreign origin and citizenship remain important barriers to non-native labor market integration}
+For Latvia and Estonia, they find that ethnic related employment policies are most relevant for the Russian speaking minorities which are not citizens of the two states.
+Once employed, the negative impact of non-nativity is less important, but labor market segregation/segmentation remains important.
+This is in line with our findings in this, although we focus more on the language aspect as a mediator of the ethnic dimension.
+%\enquote{In Estonia and Latvia, in particular, employment
+%	policies seem to be most relevant for non-immigrant non-citizens. Once employed,
+%	non-nativity may play a less negative role in the labor market for some groups,
+%	although labor market segmentation remains a significant issue.}
 \fxnote{\cite{Kahanec2009} essentially confirms your results in \cite{Leping2008,Toomet2011}}
-\cite{Kahanec2010} show that \enquote{the labor market situation of ethnic minorities in the European
-	Union. Facing a serious measurement challenge and lacking adequate data, we apply
-	several measures of ethnicity and examine various data sources as well as secondary
-	evidence. We find significant gaps between ethnic minority and majority populations in
-	terms of labor market outcomes.}
+\cite{Kahanec2010} discuss the difficulties of ethnic minorities in the labour market of the European Union.
+Their analyses are made difficult by the lack of (enough) information about the ethnic composition in available EU-wide harmonized microdata sets, such as the
+European Social Survey (ESS), Eurobarometer, EU Labour Force Survey (EU LFS), EU
+Survey of Income and Living Conditions (EU SILC) or the European Community
+Household Panel (ECHP). 
+Still, they find confirmation of the results in \cite{Kahanec2009}
 %Continue with existing stuff
@@
 majority and minority language skills, and English for both
-wage and unemployment probability.  We analyse Estonia, a former Soviet republic
+wage and unemployment.  We analyse Estonia, a former Soviet republic
 and now a rapidly growing and
@@
 the mid-1990s.  \Cref{fig:gdp_growth} indicates that the Estonian economy grew around 7\% per year before the financial crisis in 2008 and after that grew at a lower rate around 3\% per year.
+\fxwarning{ot: a few numbers about economic growth would be good}
+\fxwarning{SKB: I added rather a figure. Pure numbers or table might not give the best impression of the growth.}
 \begin{figure}[h]
 	\centering
-	\caption{Annual GDP growth in Estonia}\label{fig:gdp_growth}
+	\caption{GDP growth per year for Estonia}\label{fig:gdp_growth}
 	\includegraphics[width=0.6\linewidth]{gdp_growth_per_year.eps}
@@
 \end{figure}
-\fxnote{ot: remove the cryptic series?}
   As
@@
 \fxwarning{ot: citation here?}
+\fxwarning{SKB: Not found yet, otherwise drop it.}
 
@@
 individuals who are either working or actively looking for a job.
+
 The dataset allows us to control for standard personal
@@
 and family status.  The central variables in this study are the same
-as in \citet{Leping2008}.
+as in \citep{Leping2008}:
 
@@
 
-The labor market outcomes we analyze are income, the ``last salary on the main job'', and
-labor force status (working or unemployed).
-
-The survey includes self-reported language skills on all languages
-respondents can understand or communicate.  The questionnaire 
-gives some guidance in assessing the skills, one can report either
+The labor market outcomes we analyze are income, the ``last salary on the main job'' and
+labor force status (working, unemployed or inactive).
+
+The survey includes self-reported language skills on languages used at
+home, and all other languages they understand.  The respondents are
+give some guidance in assessing their skills, they can report either
 no knowledge, understanding, speaking, writing, or using the
@@
 SaarPoll and focuses on
-ethnic relations in Estonia.  The sample size is 1500, out of which 
-500 respondents do not consider themselves ethnic Estonians.  We analyse
+ethnic relations in Estonia.  The sample size is 1500,
+500 of the respondents consider themselves not ethnic Estonians.  We analyse
 two questions: ``which is the language of communication at your
@@
 English is more closely associated with unemployment than Russian:
-Estonians fluent in English have in average 5.0 percent unemployment rate
+Estonians fluent in English have in average 5.0 percent unemployment
 while those who are not fluent have 8.8 percent.  The difference
@@
 	\label{tab:descriptive}%
-        \newgeometry{textwidth=0.75\paperheight}
-        \begin{flushleft}
-          \small Workplace--related variables are reported for
-          employed individuals, other variables for the complete
-          workforce.  Sample is limited to persons
+	\caption*{\small
+		Workplace--related variables are reported for employed individuals,
+		other variables for the complete workforce.  Sample is limited to persons
 		25-55 year old.\\
-          \emph{RUS 0} refers to individuals who cannot speak
-          Russian and \emph{RUS 1} to those who can. Analogously for
-          English (ENG) and
+		\emph{RUS 0} refers to individuals who cannot speak Russian and
+		\emph{RUS 1} to those who can. Analogously for English
+                (ENG) and
 		Estonian (EST).\\
-          Primary sector = Agriculture, Fishing, Mining; Secondary
-          sector = Manufacturing, Construction, Electricity;
-          Tertiary (service) sector = Wholesale, Hotels, Transport,
-          Financial intermediation, Real estate; Public sector =
-          Public administration, Education, Health
-        \end{flushleft}
+		Primary sector = Agriculture,
+		Fishing, Mining \\ Secondary sector = Manufacturing,
+		Construction, Electricity \\ Tertiary (service) sector =
+		Wholesale, Hotels, Transport, Financial intermediation, Real
+		estate \\ Public sector = Public administration, Education,
+		Health}
 \end{sidewaystable}%
@@
 We use linear probability models (LPM) to estimate the relationship between
-language skills and unemployment probability, mainly in order to avoid unnecessary parametric
+language skills and unemployment, mainly in order to avoid unnecessary parametric
 assumptions in the corresponding binary choice models.\footnote{The
@@
 
-We describe the outcome of individual $i$ at year $t$ as
+We describe the outcome of individual $i$ belonging to group $g$ (either Estonian
+or Russian) at year $t$ as
 \begin{equation}
@@
 	\begin{split}
-		y_{it} = &\: \vec{\alpha}{}' \vec{X}_{it} + \vec{\beta}{}' \vec{L}_{it} +
-		\eta_{i} +
-		\upsilon_{t} + \epsilon_{it},
+		y_{it} ^{g} = &\: \alpha^{g}{}' \vec{X}_{it}^{g} + \vec{\beta}^{g}{}' \vec{L}_{it}^{g} +
+		\eta_{i}^{g} +
+		\upsilon_{t} + \epsilon_{it}^{g},
 	\end{split}
@@
 where $y$ is the outcome (either unemployment indicator
-or logarithm of net monthly wage), $\vec{X}$ are the individual and
-workplace descriptors; $\vec{L}$ is the vector of
-language skill descriptors, $\eta_{i}$ is the individual random effect, $\upsilon_{t}$ are the year dummies and $\epsilon_{it}$
-is the idiosyncratic error term.  We estimate separate models for
-Estonians and Russians.
-\fxnote{ot: if you do random effects--do you still have to cluster?}
+or logarithm of net monthly wage), $\vec{X}$ are the other individual
+characteristics; $\vec{L}$ is the vector of
+language skill descriptors, $\eta_{i}^{g}$ is the individual-specific effect, $\upsilon_{t}$ are the year dummies and $\epsilon_{it}^{g}$
+is the idiosyncratic error term. 
+\fxerror{ot: what's the eta term?  do you do random effects?}
+\fxerror{SKB: Eta should be the individual specific random effect.
+We cluster the standard errors at the individual level, hence estimate a random-effect model, although not a panel random-effect model.}
+\fxerror{ot: why does $\upsilon$ have index $g$?}
+\fxerror{SKB: Should be an error, probably index $g$ was just added to everything.}
 As we use panel data, we cluster the
@@
 
-We estimate three models that differ in
+We estimate three models that differ in terms of the number of
 control variables. The first specification only includes the language skills
@@
 status, indicator for inter-ethnic marriage, having kids up to 17 years
-old), and county of residence.  
+old) and county of residence.  
 Finally, the third specification also adds industry, occupation, and other
@@
 we only estimate the first two models.
+\fxnote{SKB: Actually, I tried to estimate Model 3 as well for unemployment probability.
+The language coefficients become insignificant after controlling for industry and occupation.
+Hence, Estonian language fluency lowers the unemployment probability only if workplace characteristics are ignored.
+Since nobody questioned this result during review, we should maybe not mention it now.
+}
 
@@
 The central results for unemployment regressions are given in
-\cref{tab:unemployment_estimation_by_sex_and_ethnic_same_sample}\footnote{We
+\cref{tab:unemployment_estimation_by_sex_and_ethnic_same_sample}.\footnote{We
   restrict both models to have the same number of observations as
-  requested by a reviewer. The unrestricted results are qualitatively
-  very similar (\cref{tab:unemployment_estimation_by_sex_and_ethnic}
-  in Appendix).}
-(the full results are available in Section~\ref{sec:unemployment_full}
-in Appendix).
-\fxerror{ot: if we have wage, we should also have unemployment}
+  requested by a reviewer. The unrestricted table is in the appendix \cref{tab:unemployment_estimation_by_sex_and_ethnic}.}
 The
@@
 	\begin{center}
-		\caption{Estimation results for unemployment probability.}
+		\caption{Estimation results for unemployment.}
 		\label{tab:unemployment_estimation_by_sex_and_ethnic_same_sample} %SKB 04.07.2018 14:22:Not yet updated only prepared
@@
 		\begin{flushleft}
-                  \legend \\ Standard errors (clustered on individuals) in parentheses.\\  Individual characteristics are \modelTwo. \\ \restrictions
+			\caption*{ \legend \\ Standard errors (clustered on individuals) in parentheses.\\  Individual characteristics are \modelTwo. \\ \restrictions}
 		\end{flushleft}
@@
 Knowledge of Russian is not associated with less unemployment for
-Estonian men, and is even related to a slightly higher unemployment probability
+Estonian men, and is even related to a slightly higher unemployment
 for Estonian women. The latter outcome may be related to omitted
@@
 \subsection{Wage}
+%SKB: Adding occupation to Model 3 reduces the effects drastically. Beforehand I somehow forgot to add it to the estimation. Now occupation is included as it should have been in the first place.
 \label{subsec:basic_model_wage}
@@
 central wage regression
-results\footnote{As above, we
+results.\footnote{As above, we
   restrict both models to have the same number of observations as
-  requested by a reviewer.  The unrestricted results are qualitatively
-  very similar (\cref{tab:wage_estimation_by_sex_and_ethnic} in
-  Appendix).}
-(The full results are given in Section~\ref{sec:wage_full} in Appendix).
+  requested by a reviewer.  The unrestricted table is in the appendix \cref{tab:wage_estimation_by_sex_and_ethnic}.}
 The table
@@
 		\begin{flushleft}
-                  \legend \\ Standard errors (clustered on individuals) in parenthesis \\ Individual characteristics are \modelTwo. \\ Workplace characteristics are \modelThreeAdd. \\ \restrictions
+			\caption*{\legend \\ Standard errors (clustered on individuals) in parenthesis \\ Individual characteristics are \modelTwo. \\ Workplace characteristics are \modelThreeAdd. \\ \restrictions}
 		\end{flushleft}
@@
 
-The effect of language fluency on unemployment probability is shown on
+The effect of language fluency on unemployment is shown on
 Figure~\ref{fig:long-run_unemployment}, and on wage on
@@
 	}
-	\caption{The effect of language fluency on unemployment probability, 1992--2012. \\ Control variables are \modelTwo. \agerestrictions }
+	\caption{The effect of language fluency on unemployment, 1992--2012. \\ Control variables are \modelTwo. \agerestrictions }
 	\label{fig:long-run_unemployment}
@@
 period of observation whereas fluency in Russian has no effect.
-Only few of the results are pointwise statistically significant though.
+Only few of the results are point wise statistically significant though.
 For Estonian women, both languages are associated with less
@@
 	\centering
-	\caption{Estimated trend over time across the age groups}
+	\caption{The trend over time across the age groups (ethnic Estonians)}
 	\begin{tabular}{lccc|cc c}
@@
 	\end{tabular}
-        \begin{flushleft}
-          \legend \\ Standard errors (clustered on individuals) in
-          parenthesis \\
-          Individual characteristics are \modelTwo. \\
-          \restrictions
-        \end{flushleft}
+
+	\caption*{\legend \\ Standard errors (clustered on individuals) in parenthesis}
 	\label{tab:age_group_trend}
@@
     Notes: \emph{Log Wage} refers to regression residual where log
-    wage is explained by year fixed effects.  \emph{EST0} and
+    wage is explained by year fixed effects.  \emph{EST 0} and
     \emph{EST 1} are mean values for those who cannot, and who can,
@@
 
-We can conclude the table~\ref{tab:loc-lang-edu} that our
+We can conclude from the table~\ref{tab:loc-lang-edu} that our
 most surprising finding, no positive effect of Estonian language
@@
 	\begin{flushleft}
-		Note: percentage of respondents (Russian speakers) who respond affirmatively
+		Note: percentage of respondents who respond affirmatively
 	\end{flushleft}
@@
 to speak the language is related to a substantially
-lower unemployment probability.
+lower unemployment rate.
 Our analysis supports \citet{YaoandOurs2015}, and \citet{Lindemann2013} findings that
@@
 labour market.
-This suggests for majority of Russian speaking men, Estonian
+This suggests for the majority of Russian speaking men, Estonian
 language gives a distinct advantage by facilitating hiring by

### 2018-07-20 response-to-reviewers.tex

@@
 Could the models be run using the same sample for each column?
-\debug{These typos got fixed.}
+
+  \begin{response}
+    These were typos in the text.  Fixed now.
+  \end{response}
+
 \end{enumerate}
@@
     what “cv.ee” means.
-    \debug{SKB: We should set a link or further explanations}
   \end{enumerate}
+
+  \begin{response}
+    We have corrected these (and many more) errors.  cv.ee refers to
+    an online job portal, however, we removed the discussion of
+    it from the text.
+  \end{response}
+
 \item pg 13 ln 35. “However too little results are
@@
   useful/good? A little more explanation would be helpful.
-  \debug{SR: For more explanations I reestimated Model2 for unemployment for the age groups.
-I made new folder in dropbox:Tabels4\_5. Here are Estimates for the age groups for 4 sub-periods, for time period 2000-2012 and for time period 1989-2012. I also made some changes in the text.}
-\debug{SKB: I did not find the tables. Where exactly did you put them? Did you include them in the text as well?}
-\item pg 15 ln 60(?) “, but not precisely estimated.” More explanation on what you mean here would be helpful.
+
+  \begin{response}
+    This is mainly due to the small groups after splitting the sample
+    into 12 subgroups.  We added a small explanation in the text.
+  \end{response}
+
+\item pg 15 ln 60(?) “, but not precisely estimated.” More explanation
+  on what you mean here would be helpful.
+
+  \begin{response}
+    We refer to large standard errors.  Changed in text.
+  \end{response}
 \end{enumerate}

### 2018-07-21 response-to-reviewers.tex
Fixed a error from broken merge; minor formatting corrections for multiple tables; minor reactions to several comments.

@@
   Appendix.  We agree these figures are valuable, in particular in the
-  light of the striving toward the replicable research in the recend
+  light of the striving toward the replicable research in the recent
   years, but we think they fit better in an online supplement.
@@
   \fxwarning{ot: should you cluster if you do random effects?}
+  \fxwarning{SKB: What do you mean?
+As far as I understand clustered standard errors, they introduce a random effect into the estimation, but should not be completely equivalent in our case, because we do not have a typical panel structure.}
 \item - The tables and figures should have notes that explain in more
@@
 \begin{response}
-  We have removed the erroneous mentioning of inactivity 
+  We have removed the erroneous mentioning of inactivity. 
 \end{response}
@@
     \fxerror{ot: if we do wage, we should also do unemployment}
+    \fxerror{skb: now both are available}
   \end{response}

### 2018-07-21 paper/ijm.tex
Fixed a error from broken merge; minor formatting corrections for multiple tables; minor reactions to several comments.

@@
 			$\ast$ : 5\% \hspace{1em} $\ast\ast$ : 1\% \normalsize}}}
+\def\sym#1{\ifmmode^{#1}\else\(^{#1}\)\fi} % needed for the tables produced by the esttab command in Stata, to avoid redundancy put here instead of in appendix.tex, where it is needed		
 %SKB: Added for documenting the tables and figures
@@
 \newcommand{\restrictions}{The sample period is from year 2000 to year 2012. Sample is limited to persons
-	25-55 year old.}
+	25-55
+
+ year old.}
 \newcommand{\agerestrictions}{25-55 year olds only.}
@@
 While the language policies in the Baltic states are discussed in \cite{Hogan-Brun2008,Hogan-Brun2007}, the implications for the labour market are not discussed.
+\cite{Dietrich2005} discusses the status of the Russian language and the related language policy in former Soviet Union countries.
+\cite{Giddings2003} discusses the ethnic wage gap in Bulgaria between ethnic Bulgarians and ethnic Turks. The wage gap increased from 0.16 in 1986 to 0.4 log points on average in 1997.
 \cite{Grasmane2011} use information from a survey conducted at the Latvian University of Agriculture with undergraduate, master, doctoral students to find out  how foreign language skills impact employability.
@@
 %	although labor market segmentation remains a significant issue.}
-\fxnote{\cite{Kahanec2009} essentially confirms your results in \cite{Leping2008,Toomet2011}}
+%\fxnote{\cite{Kahanec2009} essentially confirms your results in \cite{Leping2008,Toomet2011}}
 \cite{Kahanec2010} discuss the difficulties of ethnic minorities in the labour market of the European Union.
@@
 Household Panel (ECHP). 
-Still, they find confirmation of the results in \cite{Kahanec2009}
+Still, they find confirmation of the results in \cite{Kahanec2009}, that a finding a job is difficult as a member of an ethnic minority. 
+\cite{Constant2011} document the ethnic wage gap in Ukraine between ethnic  Russians and ethnic Ukrainians in favour of ethnic Russians.
+%But after being in the job, the labour market prospect are somewhat similar to the ethnic majority members.
 %Continue with existing stuff
@@
 she only includes recent school graduates in her study.
+Even earlier, \cite{Kroncke1999} found for Estonian Labour Force Survey that in 1989, there was no evidence for ethnic wage discrimination in Estonia, while in 1994 there was already a substantial wage discrimination against ethnic Russians.
+But in line with our findings here and in \cite{Toomet2011}, Estonian language skills did not affects wages.
 
@@
 the mid-1990s.  \Cref{fig:gdp_growth} indicates that the Estonian economy grew around 7\% per year before the financial crisis in 2008 and after that grew at a lower rate around 3\% per year.
-\fxwarning{ot: a few numbers about economic growth would be good}
-\fxwarning{SKB: I added rather a figure. Pure numbers or table might not give the best impression of the growth.}
+%\fxwarning{ot: a few numbers about economic growth would be good}
+%\fxwarning{SKB: I added rather a figure. Pure numbers or table might not give the best impression of the growth.}
 \begin{figure}[h]
@@
 	\caption*{Source: Worldbank - World Development Indicators, Series  NY.GDP.MKTP.KD.ZG}
+\fxnote{ot: remove the cryptic series?}
+%\fxnote{skb: removed the series from y-axis label. Should I remove the rest as well since it is already stated in the figure caption?}
 \end{figure}
-  As
-a bi-product of the re-adjustment, English skills become extremely
+e-adjustment, English skills become extremely
 valuable while the supply was still rather limited during the early
@@
 % Table generated by Excel2LaTeX from sheet 'subgroups_by_ethnic_language'
-\begin{sidewaystable}[tbp]
+\begin{sidewaystable}[htbp]
 	\centering
@@
 	\label{tab:descriptive}%
+
 	\caption*{\small
@@
 			\emph{RUS 0} refers to individuals who cannot speak Russian and
-		\emph{RUS 1} to those who can. Analogously for English
+			\emph{RUS 1} to those who can. ;Analogously for   
+			English
 			(ENG) and
@@
 			estate \\ Public sector = Public administration, Education,
-		Health}
+			Health
+		}
 \end{sidewaystable}%
@@
 is the idiosyncratic error term. 
-\fxerror{ot: what's the eta term?  do you do random effects?}
-\fxerror{SKB: Eta should be the individual specific random effect.
+%\fxerror{ot: what's the eta term?  do you do random effects?}
+%\fxerror{SKB: Eta should be the individual specific random effect.
 We cluster the standard errors at the individual level, hence estimate a random-effect model, although not a panel random-effect model.}
-\fxerror{ot: why does $\upsilon$ have index $g$?}
-\fxerror{SKB: Should be an error, probably index $g$ was just added to everything.}
+%\fxerror{ot: why does $\upsilon$ have index $g$?}
+%\fxerror{SKB: Should be an error, probably index $g$ was just added to everything.}
 As we use panel data, we cluster the
@@
 and year dummies.  It describes the ``raw'' effect of language skills
-on outcomes after controlling for substantial time trends in our data.
+substantial time trends in our data.
 The second specification additionally includes individual
@@
 			&         \multicolumn{2}{c}{Men}         &        \multicolumn{2}{c}{Women}        \\
-			Estonians:      & \multicolumn{1}{c}{1}      & \multicolumn{1}{l}{\hspace{10pt}2} & \multicolumn{1}{c}{1}      & \multicolumn{1}{c}{2}      \\
+			Estonians:      & \multicolumn{1}{c}{1}      & \multicolumn{1}{l}{\hspace{10pt}2} & \multicolumn{1}{c}{1}      & \multicolumn{1}{c}{2}      \\ \midrule
 			Russian         & -0.026^{***}               & -0.001                             & -0.009^{*}                 & 0.010^{**}                 \\
@@
 	\end{center}
-
 \end{table}%
@@
 
-\begin{table}[tbp]
+\begin{table}[htbp]
 	\begin{center}
@@
 			&                                   \multicolumn{3}{c}{Men}                                    &                              \multicolumn{3}{c}{Women}                               \\
-			Estonians          & \multicolumn{1}{c}{1}      & \multicolumn{1}{c}{2}      & \multicolumn{1}{l}{\hspace{10pt}3} & \multicolumn{1}{c}{1}      & \multicolumn{1}{c}{2}      & \multicolumn{1}{c}{3}      \\\midrule
+			Estonians          & \multicolumn{1}{c}{\hspace{-12pt}1}      & \multicolumn{1}{l}{\hspace{12pt}2}      & \multicolumn{1}{l}{\hspace{12pt}3} & \multicolumn{1}{c}{\hspace{-12pt}1}      & \multicolumn{1}{l}{\hspace{12pt}2}      & \multicolumn{1}{c}{3}      \\\midrule
 			Russian            & 0.112^{***}                & 0.078^{***}                & 0.043^{***}                        & 0.094^{***}                & 0.039^{***}                & 0.016^{*}                \\
@@
 
-\begin{figure}[bt!]
+\begin{figure}[hbt]
 	\centering
@@
 
-\begin{figure}[tb!]
+\begin{figure}[htb]
 	\centering
@@
 \label{sec:age_groups}
-
 As age is a central determinant how major economic and political
@@
 		           & (0.055) & (0.050)  & (0.047) & (0.051) & (0.044) & (0.038)  \\ \midrule
-		English:   &         &          &         &         &         &          \\
+		English:   &         &          &         &         &         &  
+                      \\
+
 		89-95      & 0.325*  & 0.362*   & 0.473*  & 0.191   & 0.096   & -0.096   \\
@@
 
-	\caption*{\legend \\ Standard errors (clustered on individuals) in parenthesis}
+	\caption*{\legend \\ Standard errors (clustered on individuals) in parenthesis. \\ Individual characteristics are \modelTwo. 	}
 	\label{tab:age_group_trend}
@@
 		\midrule
-		observations                         & 132  & 134   \\
+		\# Observations                         & 132  & 134   \\
 		\bottomrule
@@
 		                  & \std{0.091} &     & \std{0.074} &     & \std{0.088} &   \\ \midrule
-		\# observations             & 228         &     & 228         &     & 228         &   \\
+		\# Observations             & 228         &     & 228         &     & 228         &   \\
 		$R^{2}$           & 0.2598      &     & 0.2831      &     & 0.108       &   \\ \bottomrule
@@
 significant.
-\fxwarning{ot: let's remove the cv.ee stuff.  Or substantially improve
-that.}
-\fxwarning{SKB: You removed the cv.ee already?
-I only see stuff using data from Integration Monitor Survey 2008.
-I did not do these analyses nor do I have the data to repeat the analyses for the latest edition of the Integration Monitor Survey.
-The cv.ee might have been interesting or useful, if it was done properly documented. But that might warrant another section or even another paper. See \cite{fabo+2017E} for more on that.
-}
-
-\section{Discussion and Concluding Remarks}
+
 \label{sec:discussion}

### 2018-07-22 paper/ijm.tex
Minor corrections

@@
 %Start here CEE stuff for now
+
 Comparing the results for Estonia with other Central Eastern European (CEE) countries and former Soviet Union countries is rather difficult due to the lack of data about language skills.
@@
 re-oriented to the Western markets and has been growing rapidly since
-the mid-1990s.  \Cref{fig:gdp_growth} indicates that the Estonian economy grew around 7\% per year before the financial crisis in 2008 and after that grew at a lower rate around 3\% per year.
+the mid-1990s.  
+\Cref{fig:gdp_growth} indicates that the Estonian economy grew around 7\% per year before the financial crisis in 2008 and after that grew at a lower rate around 3\% per year.
 %\fxwarning{ot: a few numbers about economic growth would be good}
@@
 \end{figure}
-e-adjustment, English skills become extremely
+ As a bi-product of the re-adjustment, English skills become extremely
 valuable while the supply was still rather limited during the early
@@
 The central results for unemployment regressions are given in
-\cref{tab:unemployment_estimation_by_sex_and_ethnic_same_sample}.\footnote{We
+\cref{tab:unemployment_estimation_by_sex_and_ethnic_same_sample}\footnote{We
   restrict both models to have the same number of observations as
-  requested by a reviewer. The unrestricted table is in the appendix \cref{tab:unemployment_estimation_by_sex_and_ethnic}.}
+  requested by a reviewer. The unrestricted table is in the appendix \cref{tab:unemployment_estimation_by_sex_and_ethnic}.}.
 The
@@
 
-We repeat the exercise for unemployment models.
+We repeat the exercise for the unemployment models.
 However, as most of the results are not statistically significant, we
@@
 
-The most surprising result in our analysis so far--the fact that
-Russian men earn virtually no Estonian language premium while women do--warrants a
+The most surprising result in our analysis so far -- the fact that
+Russian men earn virtually no Estonian language premium while women do -- warrants a
 deeper look at the data.  We split the average wage for the Russian male wage-earners
@@
 
-We can conclude from the table~\ref{tab:loc-lang-edu} that our
+We can conclude from the Table~\ref{tab:loc-lang-edu} that our
 most surprising finding, no positive effect of Estonian language
@@
 virtually to no effect on unemployment.  This is similar to findings by
-\citet{ginsburgh+prieto-rodriguez2011ILRR} and
-\citet{beblavy+2016CEPS} who show that English is more important at better paid
+\citet{ginsburgh+prieto-rodriguez2011ILRR} and \cite{fabo+2017E}
+ who show that English is more important at better paid
 jobs.  In contrast, our outcomes suggest that English has little use

### 2018-07-22 paper/ijm.tex
the changes that SKB lost re-introduced

@@
 In contrast, the sole language that plays a role in determining
-unemployment is Estonian.  It's fluency is associated with
+unemployment is Estonian.  Its fluency is associated with
 approximately 5 percentage points lower probability of being unemployed.
@@
 We repeat the exercise for the unemployment models.
-However, as most of the results are not statistically significant, we
+However, due to relatively small groups, most of the results are not
+statistically significant and we
 do not report the results here.
@@
 Both figures are statistically significant (at 5\% and 10 \% level
-respectively), but not precisely estimated.  We can also see that
+respectively), although the standard errors are large.  We can also see that
 college education is associated by much more Estonian need and usage,

### 2018-07-22 paper/ijm.tex
abstract rewritten

@@
 \begin{abstract}
-
-	\noindent	\textbf{Purpose --} The purpose of this paper is to study the relationship between language skills and labour market
-outcomes in Estonia, a linguistically divided country where Estonian
-is the sole official language.\\
-\textbf{Design/methodology/approach --} The authors use the Estonian Labour Force Survey from 1989 to 2012 to study the impact of language skills on unemployment (probability) and wages.\\
-\textbf{Findings --} For men, fluency in                                   
-Estonian is related to approximately 5 percentage points lower unemployment, but to virtually no income
-premium. English skills are associated with a
-substantial income premium, but are virtually unrelated to
-unemployment. Russian skills are related to higher wages for Estonians,
-but the premium is falling over time and Russian is not associated with lower unemployment.	\\
-\textbf{Research limitations/implications -- } No casual claims are possible unless a suitable instruments for language skills can be found. Individual characteristics are able to explain a
-large part of English returns, so that part of the remaining effect
-may also be related to an ability bias. 
-The usage of self-reported language skills may introduce measurement errors, which may	decrease in the future, as language test data becomes available.\\	
-\textbf{Practical implications --} These results can be explained by simultaneous ethnic and gender
-segregation where the high-skilled male labour market is more segregated
-than the female labour market, and females are more often working in
-communication-intensive jobs.\\
-\textbf{Originality/value --} This paper provides a comprehensive overview about the effects of language skills on labour market outcomes for a linguistically divided, low immigration population.
-In contrast, the existing literature deals mostly with the effects of language skills on the labour market outcomes of immigrants.
+  \noindent
+  \textbf{Purpose --} We analyze the relationship between skills of
+  Estonian, Russian and English, and labour market
+  outcomes in Estonia, a linguistically divided country.
+  \\
+  \textbf{Design/methodology/approach --} We use the Estonian Labour
+  Force Surveys 1992--2012.  We rely on multivariate linear regression
+  models to document the relationship between language skills and
+  labor market outcomes.
+  \\
+  \textbf{Findings --} Estonian language knowledge (for ethnic Russians)
+  are important determinants of unemployment.  Wage, in contrary, is
+  closely related to English skills.  Ethic Russian men do not earn
+  any premium from speaking Estonian, while women, fluent in Estonian
+  earn approximately 10\% more.  For ethnic Estonians, Russian fluency
+  is associated with a similar income gain.
+  \\
+  \textbf{Research limitations/implications -- } Due to the
+  observational nature of the data, the effects reported in our study
+  are not causal effects.  As a second limitation, the self-reported
+  language skills data may be imprecise and hence the effects we
+  report may be too small.
+  \\
+  \textbf{Practical implications --} Our results stress the role of
+  workplace segregation, both along gender and ethnic lines, in
+  determining the individual labor market experience.  
+  \\
+  \textbf{Originality/value --} We provide a comprehensive overview of
+  the effects of language skills in a rapidly developing labor
+  market in a linguistically divided economy.  We analyze several
+  languages with different legal status and document long-term
+  trends in the effects.
   \\

### 2018-07-22 paper/ijm.tex
introduction, in particular CEE stuff, redone

@@
 of the local majority language for immigrants.  It is well known that
-language skills are associated with a substantial income premium
+language skills are associated with an income premium
 between 5 and 35 percent
-\citep{Chiswick1995,bleakley+chin2004,shields+price2002,leslie+lindley2001,chiswick+miller2002,Chiswick2003,Chiswick2010,Chiswick2015, Dustmann2003}.  For
+\citep{Chiswick1995,bleakley+chin2004,shields+price2002,leslie+lindley2001,chiswick+miller2002,Chiswick2010,Chiswick2015, Dustmann2003}.  For
 instance, \citet{chiswick2008} argues that ``proficient'' speakers
@@
 
-There is also an increasing body of literature focusing on relationship
-between other languages than the local main business language and
-income.  These studies generally find
+There is also an increasing body of literature focusing on other languages than the local main business language.  These studies generally find
 that English is a significant predictor of better income
 \citep{Lang2009, Casale2011, Toomet2011, Williams2011, azam+2013EDandCC, isphording2013, fabo+2017E}.
-
 The role of other languages, in particular in multi-lingual economy, is
@@
 market from the viewpoint of language skills.
-\citet{Chiswick1995, chiswick+miller2002, chiswick+miller2007, Bellante1998, Chiswick2010} analyse the effects of dominant language fluency for earnings among immigrants in the United States
+\citet{Chiswick1995, chiswick+miller2002, chiswick+miller2007,
+  Bellante1998, Chiswick2010} analyse the effects of dominant language
+fluency for earnings among immigrants in the United States, 
 \citet{Chiswick1995} also do this for Canada, Australia and Israel.
-\citet{Dustmann2003, shields+price2002} explore of immigrant assimilation into the labour market of the United Kingdom.
-
 \citet{leslie+lindley2001} analyse both employment and income but
@@
 on labour market performance in Netherlands.
-\fxwarning{ot:add CEE stuff here?}
-\fxwarning{SKB: Let's collect first enough material and then decide, but I can start adding here some notes from \cite{Kahanec2009,Kahanec2010}.}
-%Start here CEE stuff for now
-
-Comparing the results for Estonia with other Central Eastern European (CEE) countries and former Soviet Union countries is rather difficult due to the lack of data about language skills.
-Information about ethnicity is widely available, but no information about individual native and foreign language skills.
-For example, the Latvian Labour Force Survey does not (did not) contain questions regarding language skills.
-While the language policies in the Baltic states are discussed in \cite{Hogan-Brun2008,Hogan-Brun2007}, the implications for the labour market are not discussed.
-\cite{Dietrich2005} discusses the status of the Russian language and the related language policy in former Soviet Union countries.
-\cite{Giddings2003} discusses the ethnic wage gap in Bulgaria between ethnic Bulgarians and ethnic Turks. The wage gap increased from 0.16 in 1986 to 0.4 log points on average in 1997.
-\cite{Grasmane2011} use information from a survey conducted at the Latvian University of Agriculture with undergraduate, master, doctoral students to find out  how foreign language skills impact employability.
-They find that the better foreign language skills are related to higher willingness to work abroad.
-\cite{Alan2015}  show that Russian language proficiency stills matters for labour market outcomes in three former Soviet Union countries (Armenia, Azerbaijan and Georgia).
-Russian language skills increase the likelihood of being employed between six and nine percentage points.
-Similar articles about other former Soviet Union countries are not known to the authors.
-%\enquote{During the Soviet era, proficiency in the Russian language was often a ticket to
-%	attractive employment opportunities in the member republics. Does it still contribute
-%	to securing employment in the former Soviet republics after two decades of transition?
-%	Using data from Armenia, Azerbaijan and Georgia in the years 2008–2010,
-%	this paper demonstrates that Russian language skills remain economically valuable.
-%	The baseline estimates suggest that Russian language skills increase probability of
-%	employment by about 6 (males) and 9 (females) percentage points. Our results bear
-%	important implications for the ongoing debates on language policies in the post-
-%	Soviet countries.} 
-\fxnote{SKB: Quite detailed article about Russian language proficiency in three former Soviet Union states. Needs further comments from us and find similar articles.}
-\cite{Kahanec2009} provide an overview about the roles of foreign origin and citizenship in the labor markets of CEE Member States of the EU. 
- They use the EU Survey of Income and Living Conditions (EU-SILC) dataset to  map and compare the roles of foreign origin and citizenship for labor market performance.
-Using Oaxaca and Fairlie decompositions, they show that there is native/non-native divide in the national labour markets which reduces the employment and earnings prospects of men and women with foreign origin and/or citizenship.
-%They find that \enquote{both foreign origin and citizenship remain important barriers to non-native labor market integration}
-For Latvia and Estonia, they find that ethnic related employment policies are most relevant for the Russian speaking minorities which are not citizens of the two states.
-Once employed, the negative impact of non-nativity is less important, but labor market segregation/segmentation remains important.
-This is in line with our findings in this, although we focus more on the language aspect as a mediator of the ethnic dimension.
-%\enquote{In Estonia and Latvia, in particular, employment
-%	policies seem to be most relevant for non-immigrant non-citizens. Once employed,
-%	non-nativity may play a less negative role in the labor market for some groups,
-%	although labor market segmentation remains a significant issue.}
-%\fxnote{\cite{Kahanec2009} essentially confirms your results in \cite{Leping2008,Toomet2011}}
-\cite{Kahanec2010} discuss the difficulties of ethnic minorities in the labour market of the European Union.
-Their analyses are made difficult by the lack of (enough) information about the ethnic composition in available EU-wide harmonized microdata sets, such as the
-European Social Survey (ESS), Eurobarometer, EU Labour Force Survey (EU LFS), EU
-Survey of Income and Living Conditions (EU SILC) or the European Community
-Household Panel (ECHP). 
-Still, they find confirmation of the results in \cite{Kahanec2009}, that a finding a job is difficult as a member of an ethnic minority. 
-\cite{Constant2011} document the ethnic wage gap in Ukraine between ethnic  Russians and ethnic Ukrainians in favour of ethnic Russians.
-%But after being in the job, the labour market prospect are somewhat similar to the ethnic majority members.
-%Continue with existing stuff
-In case of Estonia,
-\citet{Toomet2011} shows that the majority language gives little wage
-premium for minority men.  However, he analyses neither women, nor
-unemployment.  \citet{Lindemann2013} shows that Estonian fluency
-is associated with faster job finding rate while while it does not
-explain the lower occupational prestige of Russian speakers.  However,
-she only includes recent school graduates in her study.
-Even earlier, \cite{Kroncke1999} found for Estonian Labour Force Survey that in 1989, there was no evidence for ethnic wage discrimination in Estonia, while in 1994 there was already a substantial wage discrimination against ethnic Russians.
-But in line with our findings here and in \cite{Toomet2011}, Estonian language skills did not affects wages.
+
+The literature on Central Eastern Europe (CEE) and former Soviet Union
+countries is rather limited.  We know that the different development
+trajectories have lead to disparities both favoring Russian-speaking
+minority in Ukraine \citep{Constant2011} and hindering them in Estonia
+\citep{Leping2008}.  \citet{Kahanec2009} show that non-citizens suffer
+less favorable outcomes, in particular ethnic Russians in Estonia and
+Latvia. 
+\cite{Alan2015} show that Russian language proficiency is valuable in
+the former USSR republic in Caucasus (Armenia, Azerbaijan and
+Georgia) by increasing employment likelihood between six and nine
+percentage points.  \citet{Toomet2011}, however, fails to find any
+income premium from the majority language fluency in Estonia and
+Latvia.  This outcome is corroborated by \citet{Lindemann2013} who shows that Estonian fluency
+is associated with faster job finding rate while it does not
+explain the lower occupational prestige of Russian speakers.  
+A number of these studies have to overcome severe data limitations,
+such as lack of fine-grained information on ethnic background in
+EU-wide surveys \citep{Kahanec2010}.
 
@@
 where the Russian-speaking community forms almost 30\% of
-the population.  We provide long--term trends from the last years
+the population.  We use Estonian Labor Force Survey, one of the
+higher-quality long-term datasets, very well suitable for our
+purpose.  We provide long--term trends from the last years
 of the planned economy in 1989 till the post-recession time in 2012.
@@
 higher wage but the relationship is slowly fading.  English fluency was
-associated with a very large wage premium early after the country
-transitioned to a market economy, later its importance
+associated with a very large wage premium during the early years of
+economic transition, later its importance
 declined but remained sizeable.  
-
 In contrast, the sole language that plays a role in determining
-unemployment is Estonian.  Its fluency is associated with
+unemployment probability is Estonian.  Its fluency is associated with
 approximately 5 percentage points lower probability of being unemployed.
 These results suggest that Estonian labour market is      
-segmented both along gender and the ethnic boundaries, men
+segmented both along gender and the along ethnic background, with men
 more likely occupied in less communication-intense jobs.
@@
 approach, sections \ref{sec:results} and \ref{sec:extensions} present
-the results for unemployment probability and wages.
+the results for unemployment probability and wages.  The two last
+sections, \ref{sec:segregation-analysis} and \ref{sec:discussion}, are
+devoted to additional analysis of labor market segregation, and
+concluding discussion.
 
@@
 \section{Additional Evidence: Education and Workplace}
-\label{sec:segregation_analysis}
+\label{sec:segregation-analysis}
 
@@
 
+\section{Discussion and Concluding Remarks}
 \label{sec:discussion}

### 2018-07-22 paper/ijm.tex
integration monitor regression code file found and added here

@@
 See \citet{Leping2008} and
-\citet{lindemann+saar2011Russian2ndGeneration} for more information.
+\citet{lindemann+saar2011Russian2ndGeneration} for more detailed information.
 
 Before the Second World War, the country was ethnically rather
-homogeneous, populated almost exclusively by ethnic Estonians. After the War,
+homogeneous with 90 percent of the population being ethnic Estonians. After the War,
 the Russian-speaking population grew rapidly through migration and
@@
 mineral-rich industrial area in North-East of the country, and in the
-metropolitan area near the capital city Tallinn, and hence the
-Russian-speakers are still very unevenly distributed across the country.
+metropolitan area near the capital city Tallinn.  The
+Russian-speakers are still very unevenly distributed.
 
@@
 also reflected at workplace \citep{leppik+vihalemm2015JofBaltStud}.
-Certain sectors in the economy, such as the army, railways and the
+Certain sectors in the economy, such as the armed forces, railways and the
 merchant fleet
@@
 such as agriculture and
-local public administration,
+public administration,
 were dominated by ethnic Estonians.
 Both communities followed the media in their own respective language, the
-universities taught many subjects in Russian and Estonian,
+universities taught many subjects in both Russian and Estonian,
 and service sector was largely bilingual.  However, the bilingualism
@@
 When the central Soviet authority weakened during the late 1980, the
-Estonian-speaking community was quick to organize and establish a
+Estonian-speaking community was quick to organize, and established a
 nation-state in 1991 where
 Estonian was granted status as the sole official language.  The
-above-mentioned ``one-sided bilingualism'' slowly started turning
+above-mentioned ``one-sided bilingualism'' started turning
 around.  The universities quickly moved to Estonian-only curriculum,
-Estonian language become a large-scale compulsory subject in Russian
-schools while teaching Russian in Estonian-language schools declined.
-Since 2007, all Russian high schools have to teach part of the
-curriculum in Estonian \citep{lindemann+saar2011Russian2ndGeneration}.
-
-According to the report of the Ministry of Education and Research the number
-of students, whose mother tongue is not Estonian in basic schools who study in the Estonian language increased from 17.5\% in 2005 to 25.8\% in 2015 due to the growing popularity of immersion
-classes (enrolment of classes rose from 7.8\% in 2005 to 17.5\% in 2015).
-At the same time the number of students whose mother tongue is not
-Estonian studying in Estonian basic schools slowly dropped
-respectively from 9.5\% to  8.3\% \citep{HTM2015}.  The younger generation of ethnic Estonians is
+Estonian language become a compulsory subject in Russian schools
+while teaching Russian in Estonian-language schools declined.
+These trends have continued till this day today, according to
+\citet{HTM2015}, one quarter of the students from non
+Estonian-speaking families studied in Estonian schools.
+As a result, the younger generation of ethnic Estonians is
 increasingly less fluent in Russian while the ethnic Russians are
@@
 the mid-1990s.  
-\Cref{fig:gdp_growth} indicates that the Estonian economy grew around 7\% per year before the financial crisis in 2008 and after that grew at a lower rate around 3\% per year.
-%\fxwarning{ot: a few numbers about economic growth would be good}
-%\fxwarning{SKB: I added rather a figure. Pure numbers or table might not give the best impression of the growth.}
-\begin{figure}[h]
-	\centering                      
-	\caption{GDP growth per year for Estonia}\label{fig:gdp_growth}
-	\includegraphics[width=0.6\linewidth]{gdp_growth_per_year.eps}
-	\caption*{Source: Worldbank - World Development Indicators, Series  NY.GDP.MKTP.KD.ZG}
-\fxnote{ot: remove the cryptic series?}
-%\fxnote{skb: removed the series from y-axis label. Should I remove the rest as well since it is already stated in the figure caption?}
-\end{figure}
+\Cref{fig:gdp_growth} shows that grew averaged at approximately 7\%
+annually
+before the financial crisis in 2008, afterwards the figure has been around 3\%.
 As a bi-product of the re-adjustment, English skills become extremely
@@
 years of transition.
+
+\begin{figure}[h]
+  \centering                      
+  \caption{Annual GDP growth in Estonia}\label{fig:gdp_growth}
+  \includegraphics[width=0.6\linewidth]{gdp_growth_per_year.eps}
+  \caption*{Source: World Bank - World Development Indicators}
+\end{figure}
 
@@
 different and occasionally antagonistic viewpoints depending on the
-language \citep{Korts2002}.  Around 25\% of Estonians show little
-tolerance for Russian-speaking population (the corresponding figure
-for Russians is substantially smaller).  A major issue for this group
-is Russians' ability and willingness to communicate in Estonian.
-\fxwarning{ot: citation here?}
-\fxwarning{SKB: Not found yet, otherwise drop it.}
+language \citep{Korts2002}.
 

### 2018-07-22 code/integrationMonitor.R

@@ -1,0 +1,89 @@
+
+langModel <- function(data, reg="lpm", outcome="need",
+                      subset=k102 >= 25 & k102 <=55) {
+   ## Estimate the language need/usage model on IntegrationMonitor data
+   subset <- eval(substitute(subset), envir=data)
+   if(!is.null(subset)) {
+      subset <- which(subset)
+      cat("Taking subset: original", nrow(data), "obs, subset", length(subset), "obs\n")
+      data <- data[subset,]
+   }
+   ## Modeling language use at work based on IntegrationMonitor
+   data <- data[tolower(trim(data$k104.1)) != "eestlane",]
+                           # ethnic backround
+   cat("Ethnic background of the sample:\n")
+   print(table(data$k104.1))
+   ETEnvir <- tolower(trim(data$k12)) == "peamiselt eesti keeles"
+                           # communication language at workplace
+   RUEnvir <- tolower(trim(data$k12)) == "peamiselt vene keeles"
+   needET <- tolower(trim(data$k78.1)) == "eesti"
+                           # which languages do you need at work
+   needRU <- (tolower(trim(data$k78.1)) == "vene") | (tolower(trim(data$k78.2)) == "vene")
+   needEN <- (tolower(trim(data$k78.1)) == "inglise") | (tolower(trim(data$k78.2)) == "inglise") |
+       (tolower(trim(data$k78.3)) == "inglise")
+   needEN[is.na(needEN)] <- FALSE
+   woman <- tolower(trim(data$k101)) == "naine"
+                           # gender
+   ##
+   region <- rep("ROC", nrow(data))
+   region[tolower(trim(data$mk)) == "harju"] <- "Capital"
+   region[tolower(trim(data$mk)) == "ida-viru"] <- "NE"
+   region <- factor(region, levels=c("ROC", "Capital", "NE"))
+   ##
+   occ <- rep("L", nrow(data))
+   occ[tolower(trim(data$k5)) == "asutuse või allüksuse juht"] <- "upper"
+                           # occupation
+   occ[tolower(trim(data$k5)) == "spetsialist ametil, mis eeldab kõrgharidust"] <- "specialist"
+   occ <- factor(occ)
+   ##
+   public <- tolower(trim(data$k6)) == "riiklikus asutuses/ettevõttes"
+                           # private/public/NGO...
[…]

### 2018-07-23 paper/ijm.tex
results done

@@
 individuals who are either working or actively looking for a job.
-
 The dataset allows us to control for standard personal
 characteristics and human capital variables, such as age, education
-and family status.  The central variables in this study are the same
-as in \citep{Leping2008}:
+and family status.  We discuss the most important variables below.
 
@@
 home, and all other languages they understand.  The respondents are
-give some guidance in assessing their skills, they can report either
-no knowledge, understanding, speaking, writing, or using the
+given some guidance in assessing their skills, they can report either
+no knowledge, understanding only, speaking but not writing, writing, or using the
 language at home.  We consolidate this information into a dummy variable, equal
@@
 only.
-  The reader should keep in mind that while the pre-2000 waves include retrospective income, they do not include retrospective language skills. In this way, the results before
-1995 are partly based on extrapolation, assuming individual language
-skills did not vary before that date.
 
@@
 skills (Estonian, Russian and English).
-\fxwarning{OT: can you add variable 'year' in this table?  I know it feels a little weird but is great to show time trends.}
-\fxwarning{SKB: What do you mean with time trends? Which value should a ``year'' variable take? Give me an example, since I don't understand what you want. }
 
@@
 			25-55 year old.\\
-			\emph{RUS 0} refers to individuals who cannot speak Russian and
-			\emph{RUS 1} to those who can. ;Analogously for   
+			\emph{RUS 0} refers to individuals who do not speak Russian and
+			\emph{RUS 1} to those who do.  Analogously for   
 			English
@@
 We analyse the relationship between labour market outcomes and language
-skills by ordinary multivariate regression models.
+skills using the ordinary multivariate regression.
 Several related studies use instrumental variables to correct for
@@
 assumptions in the corresponding binary choice models.\footnote{The
-	results of corresponding probit models are virtually equal to the LPM results.}
+	results of corresponding probit models are virtually identical to the LPM results.}
 Similarly, we estimate the effect of language skills on wage by
@@
 
-We describe the outcome of individual $i$ belonging to group $g$ (either Estonian
-or Russian) at year $t$ as
+We describe the outcome (log wage and unemployment status) $y$ of individual $i$ at year $t$ as
 \begin{equation}
@@
 	\begin{split}                                                       
-		y_{it} ^{g} = &\: \alpha^{g}{}' \vec{X}_{it}^{g} + \vec{\beta}^{g}{}' \vec{L}_{it}^{g} +
-		\eta_{i}^{g} +
-		\upsilon_{t} + \epsilon_{it}^{g},                                                                                                                                                          
+		y_{it} = &\: \vec{\alpha}' \vec{X}_{it} + \vec{\beta}{}' \vec{L}_{it} +
+		\eta_{i} +
+		\upsilon_{t} + \epsilon_{it},                                                                                                                                                          
 	\end{split}
 \end{equation}
-where $y$ is the outcome (either unemployment indicator
-or logarithm of net monthly wage), $\vec{X}$ are the other individual
-characteristics; $\vec{L}$ is the vector of
-language skill descriptors, $\eta_{i}^{g}$ is the individual-specific effect, $\upsilon_{t}$ are the year dummies and $\epsilon_{it}^{g}$
+where $\vec{L}$  is the vector of
+language skill descriptors, $\vec{X}$ are the other individual
+characteristics, $\eta_{i}$ is the individual-specific effect, $\upsilon_{t}$ are the year dummies and $\epsilon_{it}$
 is the idiosyncratic error term. 
-%\fxerror{ot: what's the eta term?  do you do random effects?}
-%\fxerror{SKB: Eta should be the individual specific random effect.
-We cluster the standard errors at the individual level, hence estimate a random-effect model, although not a panel random-effect model.}
-%\fxerror{ot: why does $\upsilon$ have index $g$?}
-%\fxerror{SKB: Should be an error, probably index $g$ was just added to everything.}
 As we use panel data, we cluster the
@@
 
-We estimate three models that differ in terms of the number of
+We estimate three models that differ in terms of 
 control variables. The first specification only includes the language skills
-and year dummies.  It describes the ``raw'' effect of language skills
-substantial time trends in our data.
+and year dummies.  It describes the ``raw'' effect of language skills,
+net of strong time trends in our data.
 The second specification additionally includes individual
@@
 we only estimate the first two models.
-\fxnote{SKB: Actually, I tried to estimate Model 3 as well for unemployment probability.
-The language coefficients become insignificant after controlling for industry and occupation.
-Hence, Estonian language fluency lowers the unemployment probability only if workplace characteristics are ignored.
-Since nobody questioned this result during review, we should maybe not mention it now.
-}
 
@@
 
-The central results for unemployment regressions are given in
+The central results for unemployment regressions are presented in
 \cref{tab:unemployment_estimation_by_sex_and_ethnic_same_sample}\footnote{We
   restrict both models to have the same number of observations as
-  requested by a reviewer. The unrestricted table is in the appendix \cref{tab:unemployment_estimation_by_sex_and_ethnic}.}.
+  requested by a reviewer. The unrestricted results are provided in the Appendix (\Cref{tab:unemployment_estimation_by_sex_and_ethnic}).}.
 The
@@
 with approximately 5 percentage points lower unemployment for both
-Russian men and women. We also see that the effect is not radically
-influenced by the individual characteristics--for men it is
+Russian men and women. We also see that the effect is not 
+influenced in any major way by the individual characteristics--for men it is
 virtually unchanged while for women the estimate falls by 30\%, from
@@
 variable bias, Russian knowledge was widespread in the Soviet era and may
-not have been closely associated with any favourable characteristics,
-but has been increasingly more associated with age  during the period of analysis.
+not have been closely associated with favorable unobserved
+characteristics, however, it has been increasingly associated with age
+through the period of analysis.
 English skills are related to less unemployment both for Estonian men
 and women, but the effect is small.
-For Russians, however, Estonian language skills matter. Those who are
-fluent in that language have approximately 5 percentage point less
-unemployment, the effect changes only a little when controlling for
-individual characteristics.  In contrast, the effect of English
-fluency is close to zero and not statistically significant.  As in
+For Russians, the most important language is clearly Estonian.  Those who are
+fluent in that language are approximately 5 percentage point less likely
+unemployed, the effect changes only a little when introducing the
+individual controls.  In contrast, the effect of English
+is close to zero and not statistically significant.  As in
 case of Estonian, individual characteristics change the estimates only
@@
 with fluency of all analyzed languages with English showing the
-largest effect.  The only remarkable exception is
+largest effect.  The only exception is
 Estonian language for Russian men where we fail to find any positive
@@
 lowers the effects further to 0.066, suggesting that part of the
-language skill premium is collected through workplace mobility.
+language skill premium is realized through workplace selection.
 
@@
 substantial income premium of 10\% for both Estonian men and women.
-The effect falls rapidly when introducing
-individual and workplace controls, suggesting that both ability bias
+Individual and workplace controls lower this figure substantially
+implying that both ability bias
 and workplace mobility play a role.
@@
 English language is associated with a very large
-wage premium, up to 34 log points (model 1 for
-Estonian men). It falls substantially when introducing the
+wage premium, up to 34 log points, for all the analyzed groups.  The number falls substantially when introducing the
 individual characteristics into the model (model 2), additional
-workplace characteristics have little effect.  However, in all
-specifications it is
-significantly more
+workplace characteristics have less effect.  However, in all
+specifications it remains
+noticeably more
 important than Russian for Estonians. The estimates are rather
@@
 
-In conclusion, the wage regressions suggest that English is the main
-language that matters for men.  The effect of Russian is minor and
+In conclusion, the wage regressions suggest that English is the
+language most closely associated with income for men.  The effect of Russian is minor and
 that of Estonian non-existent.  For women, all three languages are
@@
 trends in the estimated effect size.  Here we look at the yearly estimates from 1992 to 2012.
+The reader should keep in mind that while the pre-2000 waves include retrospective income, they do not include retrospective language skills. In this way, the results before
+1995 are partly based on extrapolation, assuming individual language
+skills did not vary before that date.
+
 We report the results for model 2, i.e. models that include year
@@
 result in our analysis and we'll return to this
-below in section~\ref{sec:segregation_analysis}.
+below in section~\ref{sec:segregation-analysis}.
 The impact of Estonian language skills for Russian women too, but

### 2018-07-23 paper/ijm.tex
all text done

@@
 As Estonian economy went through turbulent times and rapid changes
-during the 1990s, additional evidence can be gained by a long-term
+during the 1990s, it is instructive to analyze the effect long-term
 trends in the estimated effect size.  Here we look at the yearly estimates from 1992 to 2012.
@@
 Figure~\ref{fig:long-run_wage}.
-\fxnote{ot: SKB, I think I asked if you can slightly offset the black
-  and red lines and you could not?}
-\fxnote{SKB: I do not remember such request.
-The only request, that I remember, is to make the scaling of the figures equal or cut off parts of the large confidence intervals, so that the scaling of the y-axis becomes smaller/more detailed.}
 The results reveal a few interesting facts.  First, the effects are
@@
 that the peculiar labour market institutions have been persistent for
-two decades.  However, we can see how Estonian language turned
+two decades.  However, for women we can see that Estonian language turned
 important in late 1990s, suggesting that there is either less
-workplace segregation or other need for the official language for
+workplace segregation or other kind of necessity to know the official
+language at 
 the jobs commonly taken by women.  The
@@
 (Table~\ref{tab:age_group_trend}).
-We group the observation period into 4 sub-periods: Early transition period
-(1989--1995); First economic growth period (1996--1999);
-Economic boom, EU accession (2000--2007); and the recession
+We group the observation period into 4 sub-periods: early transition
+(1989--1995); first economic growth (1996--1999);
+economic boom, EU accession (2000--2007); and the recession
 (2008--2012).
@@
 (45-55) and the youngest women (25-35) show a growing trend.
-This potentially reflects both the changing supply and demand of
-English skills.
+This potentially reflects both the changing supply and demand for 
+English.
 
@@
 statistically significant results at all.  This is the most unexpected
-result in our analysis and we'll return to this
-below in section~\ref{sec:segregation-analysis}.
-The impact of Estonian language skills for Russian women too, but
-since year 2000, we observe a sizable effect of approximately
-10\% for several cases.  However, standard errors are large and we
-cannot conclude that the effect is positive for all the age groups.
+outcome in our analysis and we'll return to this
+below in Section~\ref{sec:segregation-analysis}.
+The effect of Estonian language skills was initially small for Russian
+women as well, but
+since year 2000, we observe a sizable gain of approximately
+10\% for all subgroups.
 The positive outcomes for women for the second decade in our analysis
@@
 jobs than those who cannot speak the language.
-In comparison, the estimates for English language show
-a downward trend for all age groups for both men and for women.  A likely
+In comparison, the estimates for English language trend downward over
+time
+for all age groups for both men and for women.  A likely
 cause is the increasing abundance of these skills over time.
@@
 statistically significant and we
-do not report the results here.
+do not report those here.
 
@@
 deeper look at the data.  We split the average wage for the Russian male wage-earners
-along the three
+along three
 dimensions: Estonian language skills (\emph{EST 0} and \emph{EST 1}),
@@
 and education (\emph{< HS}, \emph{HS}, \emph{College Degree}).  The metropolitan area is one of the two major regions
-where the Russian-speaking population is concentrated, and it's
+where the Russian-speaking population is concentrated, and its
 booming economy may be very different from the other such region, the
 North-East (Ida-Virumaa), and the rest of the country.
-Even more, while Russians form a large minority in and around Tallinn,
-they are in majority in the North-East.  
 In order to correct for the strong wage and language skill trends
 through the observation period, we do not present the average wage,
-but instead the respective OLS residuals where we explain the wage by year fixed
+but instead the respective OLS residuals where we explain the log wage by year fixed
 effects and include no other explanatory variables (Table~\ref{tab:loc-lang-edu}).
@@
     degree, \emph{HS} is the high school degree as the highest
-    completed education level.
+    completed education.
   \end{flushleft}
@@
 most surprising finding, no positive effect of Estonian language
-skills for Russian men, is primarily driven by workers with
-high school degree.  It also suggests that highly educated workers in
+skills for Russian men, is primarily driven by the largest group, workers with
+a high school degree.  It also suggests that highly educated workers in
 the metropolitan area enjoy, in fact, a substantial language premium.
@@
 
-The previous results can be explained by two hypotheses: first,
+The previous results can be explained by a combination of two hypotheses: first,
 Russian--speaking men, at least those with high school degree as their
@@
 little communication requirements (gender segregation).
-To shed some additional light on these hypotheses, we use data
+To get some additional evidence on these hypotheses, we use data
 from 2008 Integration Monitor Survey.  We focus on
@@
 question addresses the ethnic segregation while the second focuses on
-the need of communication.
+the need of the language for communication.
 
@@
 Table~\ref{tab:environment_model} presents the corresponding regression results
-where we estimate the likelihood of having the need, and using, Estonian at work
+where we estimate the likelihood of having the need for, and using the
+language at work
 while
@@
 
-In summary, this dataset supports the previous hypothesis: Russian women are
+In summary, this dataset supports both of the hypotheses outlined above: Russian women are
 working in less segregated environment where Estonian is the main
@@
 language gives a distinct advantage by facilitating hiring by
-Estonian-dominated employers.  However, our outcome also supports 
+Estonian-dominated employers.  But we also confirm
 \citet{leppik+vihalemm2015JofBaltStud} conclusion that
 these
-jobs are associated with little career mobility.  There is also
+jobs are associated with little career mobility.  There is also some
 anecdotal evidence suggesting that offices are
@@
 language more, such as working in a direct contact with customers.
-
 We also find evidence that over time Estonian is becoming more
@@
 economy--wide rise of the importance of Estonian language.  No such trend is visible for
-men suggesting that 20 years--almost a generation after the collapse of Soviet Union, the
+men suggesting that 20 years---almost a generation---after
+establishing a nation state and market economy, the
 labor market integration is still not complete.
 
-The other results are more in line with other studies.
+The fact the Russian language is not associated with any better
+employment prospects
+is in stark contrast to the results by \citet{Alan2015}.  This is
+potentially related to the sharp re-orientation to Western markets and
+nation-state related political reforms Estonia experienced in the
+early 1990s.  Rapid withdrawal from the former USSR economy has
+resulted in
+a laudable economic growth, but may have led to
+increased ethnic disparities, compared to the economies that moved in
+a slower pace, such as Ukraine \citep{Constant2011} and the former Caucasus republics
+\citep{Alan2015}.
+
+Our other results are more in line with other studies.
 English language is related to a substantial income premium but
-virtually to no effect on unemployment.  This is similar to findings by
+to virtually no effect on unemployment.  This is similar to findings by
 \citet{ginsburgh+prieto-rodriguez2011ILRR} and \cite{fabo+2017E}
@@
 employment and unemployment.
-Note also that for
+Note also that in case of
 English, we are able to explain a substantial part of the raw effect
@@
 
-The study has a number of limitations.  Although we believe that our
-estimates are good indicators of a causal relationship, we cannot 
-claim this as our data do not contain strong enough instruments.
+The study has two main limitations.  Although we believe that our
+estimates are good indicators of a causal relationship, we cannot be
+sure this is the case as our data do not contain strong enough instruments.
 In particular, as individual characteristics are able to explain a
@@
 may also related to an ability bias.  Another weak point in the current
-data is using the self-reported language
-skills, although this is the standard practice in the literature.  As language test data becomes available, we may be able to
+data are the self-reported language
+skills.  As language test data becomes available, we may be able to
 decrease the measurement error in the future.

### 2018-07-23 response-to-reviewers.tex
response to reviewer look good now

@@
             ]{hyperref}
-\usepackage[top=15mm, bottom=15mm, left=10mm, textwidth=130mm, marginparwidth=70mm]{geometry}
+\usepackage[top=15mm, bottom=25mm, left=10mm, textwidth=130mm,
+marginparwidth=70mm]{geometry}
 \usepackage{graphicx}
@@
 \begin{document}
-	\section*{General remarks} % which are too long for the margin... .
-\begin{itemize}
-	\item A rather general remark, I added the occupation variable to the estimations, but did not redo the graphs or tables.
-The results should not differ much.
-It will show up in the tables with all coefficients.
-\item SKB: The column separating lines in Table 4 have some \enquote{holes}.
-We might have to switch from the dcolumn package to the siunitx package to fix these issues.
-I did not manage yet fix these issues.
-The referees did not complain, but it still looks ugly or strange.
-\end{itemize}
 \section*{Response to the referees}
@@
   language in Baltic, CEE, and former Soviet Union countries.
+
+  \begin{response}
+    We have added some more references about CEE economies.  This
+    literature is now discussed in introduction and our outcomes are
+    benchmarked against some of the CEE literature in the discussion. 
+  \end{response}
 \item 
@@
 In order to expedite the processing of the revised manuscript, please be as specific as possible in your response to the referee(s).
-\end{enumerate}
 
@@
 \end{response}
+
+\end{enumerate}
 
@@
   \end{response}
+
 \item 
@@
   \end{response}
-\item
-  \debug{OT: I'll do a rewrite after changes are made, hope it's
-    sufficient.} 
-  The paper needs to be checked for spelling and grammar
+\item The paper needs to be checked for spelling and grammar
   errors. There are a number of typos and errors, which should be
@@
   so many mistakes.
+
+  \begin{response}
+    We have done a thorough proofreading and improved the language. 
+  \end{response}
 \end{enumerate}
@@
   \end{response}
-  \fxwarning{ot: should you cluster if you do random effects?}
-  \fxwarning{SKB: What do you mean?
-As far as I understand clustered standard errors, they introduce a random effect into the estimation, but should not be completely equivalent in our case, because we do not have a typical panel structure.}
 \item - The tables and figures should have notes that explain in more
@@
     tables would be more suitable for an online supplement.
-    \fxerror{ot: if we do wage, we should also do unemployment}
-    \fxerror{skb: now both are available}
   \end{response}

### 2018-07-23 response-to-reviewers.tex
First round of tool assisted spell checking; Renaming of files due to journal requirements

@@
 {\slshape}{}
-
+\date{}
+\title{Response to the referees and editor}
 \begin{document}
-\section*{Response to the referees}
 
 \section{Comments by the editor}
+
+%\enquote{You will be unable to make your revisions on the originally submitted version of the manuscript.
+Instead, revise your manuscript using a word processing program and save it on your computer.
+Please also highlight the changes to your manuscript within the document by using the track changes mode in MS Word or by using bold or coloured text.
+}
+%We used LaTeX to prepare the manuscript and were not able to use MS Word to track the changes.
+Instead we uploaded a PDF-file that shows the differences between our original submission and the revised text.
+We hope that this file satisfies the requirements.
 
@@
 
-\debug{nothing else but 7500 words/50 items.}
+%\debug{nothing else but 7500 words/50 items.}
 \item When submitting your revised manuscript, you will be able to respond to the comments made by the referee(s) in the space provided.
@@
 \end{enumerate}
+\section*{Response to the referees}
 
@@
 \begin{enumerate}
-\item For this papers findings section in the abstract they imply that
-  for all men fluency in Estonian is related to 5\% lower unemployment
-  and no income premium.  From Table 2 and 3 it appears that this
-  should be for only Russian males. English skills are associated with
-  a large income premium and no unemployment. From Table 2 and 3 this
-  appears to be more accurately just Russians, as the Estonians appear
-  to have a significant negative correlation with unemployment.  This
-  is supported by what is said later in the Discussion and Concluding
-  Remarks section in what they state is their most intriguing
-  observation.  Claiming this to be the most intriguing is interesting
-  as it seems to support some what previous literature has stated and
-  one of the extensions that this paper is making the inclusion of
-  women and namely how their effects differ from males and previous
-  literature.
-
-  \begin{response}
-    No response neede here.
-  \end{response}
+%\item For this papers findings section in the abstract they imply that
+%  for all men fluency in Estonian is related to 5\% lower unemployment
+%  and no income premium.  From Table 2 and 3 it appears that this
+%  should be for only Russian males. English skills are associated with
+%  a large income premium and no unemployment. From Table 2 and 3 this
+%  appears to be more accurately just Russians, as the Estonians appear
+%  to have a significant negative correlation with unemployment.  This
+%  is supported by what is said later in the Discussion and Concluding
+%  Remarks section in what they state is their most intriguing
+%  observation.  Claiming this to be the most intriguing is interesting
+%  as it seems to support some what previous literature has stated and
+%  one of the extensions that this paper is making the inclusion of
+%  women and namely how their effects differ from males and previous
+%  literature. 
+%
+%  \begin{response}
+%    No response needed here.
+%  \end{response}
 

### 2018-07-23 paper/ijm.tex
First round of tool assisted spell checking; Renaming of files due to journal requirements

@@
 \newcommand{\std}[1]{\emph{(#1)}}
-\newcommand{\V}{{\ensuremath\checkmark}}
+\newcommand{\V}{\ensuremath\checkmark}
 \def\fns{\footnotesize}
@@
  \noindent
-  \textbf{Purpose --} We analyze the relationship between skills of
+ \textbf{Purpose --} We analyse the relationship between skills of
  Estonian, Russian and English, and labour market
@@
  models to document the relationship between language skills and
-  labor market outcomes.
+ labour market outcomes.
  \\
@@
  are important determinants of unemployment. Wage, in contrary, is
-  closely related to English skills.  Ethic Russian men do not earn
+ closely related to English skills. Ethnic Russian men do not earn
  any premium from speaking Estonian, while women, fluent in Estonian
@@
  workplace segregation, both along gender and ethnic lines, in
-  determining the individual labor market experience.  
+ determining the individual labour market experience. 
  \\
  \textbf{Originality/value --} We provide a comprehensive overview of
-  the effects of language skills in a rapidly developing labor
-  market in a linguistically divided economy.  We analyze several
+ the effects of language skills in a rapidly developing labour
+ market in a linguistically divided economy. We analyse several
  languages with different legal status and document long-term
@@
 shows that Italian language skills in Swiss non-Italian speaking
-regions are associated with lower wage.  It remains unclear if
+regions are associated with a lower wage. It remains unclear if
 this is a true effect or just an omitted variable bias.
@@
 \citet{YaoandOurs2015} only analyse the role of Dutch language
-on labour market performance in Netherlands.
+on labour market performance in the Netherlands.
 
@@
 countries is rather limited. We know that the different development
-trajectories have lead to disparities both favoring Russian-speaking
+trajectories have led to disparities both favouring Russian-speaking
 minority in Ukraine \citep{Constant2011} and hindering them in Estonia
 \citep{Leping2008}. \citet{Kahanec2009} show that non-citizens suffer
-less favorable outcomes, in particular ethnic Russians in Estonia and
+less favourable outcomes, in particular, ethnic Russians in Estonia and
 Latvia. 
 \cite{Alan2015} show that Russian language proficiency is valuable in
-the former USSR republic in Caucasus (Armenia, Azerbaijan and
+the former USSR republic in the Caucasus (Armenia, Azerbaijan and
 Georgia) by increasing employment likelihood between six and nine
@@
 where the Russian-speaking community forms almost 30\% of
-the population.  We use Estonian Labor Force Survey, one of the
-higher-quality long-term datasets, very well suitable for our
+the population. We use Estonian Labour Force Survey, one of the
+higher-quality long-term datasets, well suitable for our
 purpose. We provide long--term trends from the last years
@@
 We find that the Estonian language, the majority and the official
-language of the country, is associated with very
+language of the country, is associated with a very
 small albeit slowly increasing wage premium over
@@
 approximately 5 percentage points lower probability of being unemployed.
-These results suggest that Estonian labour market is      
+These results suggest that the Estonian labour market is 
 segmented both along gender and the along ethnic background, with men
@@
 The paper continues as follows: The next section provides a brief
-background of Estonian society and labour market. In the following
-section we discuss the data and provide some descriptive
+background of Estonian society and the labour market. In the following
+section, we discuss the data and provide some descriptive
 statistics. In \cref{sec:method} we describe the econometric
@@
 sections, \ref{sec:segregation-analysis} and \ref{sec:discussion}, are
-devoted to additional analysis of labor market segregation, and
+devoted to an additional analysis of labour market segregation, and
 concluding discussion.
@@
 the other way around. A particular institution in parts of the Soviet
-Union was segregated school system, where Russian schools existed along the
-schools teaching in the local language.  Hence a common education
+Union was a segregated school system, where Russian schools existed along the
+schools teaching in the local language. Hence, a common education
 system, one of the central integration mechanisms in the developed world,
@@
 caused increasing concerns about the future of the Estonian
-language, in turn leading to  unwillingness to use Russian by
+language, in turn leading to an unwillingness to use Russian by
 the ethnic Estonians. This further strengthened the language-based segregation.
 
-When the central Soviet authority weakened during the late 1980, the
-Estonian-speaking community was quick to organize, and established a
+When the central Soviet authority weakened during the late 1980s, the
+Estonian-speaking community was quick to organize and established a
 nation-state in 1991 where
@@
 around. The universities quickly moved to Estonian-only curriculum,
-Estonian language become a compulsory subject in Russian schools
+the Estonian language became a compulsory subject in Russian schools
 while teaching Russian in Estonian-language schools declined.
-These trends have continued till this day today, according to
-\citet{HTM2015}, one quarter of the students from non
-Estonian-speaking families studied in Estonian schools.
+These trends have continued until today, according to
+\citet{HTM2015}, one quarter of the students from non-Estonian-speaking families studied in Estonian schools.
 As a result, the younger generation of ethnic Estonians is
@@
 before the financial crisis in 2008, afterwards the figure has been around 3\%.
-As a bi-product of the re-adjustment, English skills become extremely
+As a by-product of the re-adjustment, English skills become extremely
 valuable while the supply was still rather limited during the early
@@
  \caption{Annual GDP growth in Estonia}\label{fig:gdp_growth}
-  \includegraphics[width=0.6\linewidth]{gdp_growth_per_year.eps}
+ \includegraphics[width=0.6\linewidth]{Figure1.eps}
  \caption*{Source: World Bank - World Development Indicators}
@@
 contains data on approximately 4000 distinct individuals annually,
-however, due to it's rotating nature, we have roughly 16,000 annual
-observations for each year since 2000.  For the long-term analysis we
-also use the earlier waves.  These wave also include a retrospective
+however, due to its rotating nature, we have roughly 16,000 annual
+observations for each year since 2000. For the long-term analysis, we
+also use the earlier waves. These waves also include a retrospective
 section that contains income up to several years back.
@@
 
-The labor market outcomes we analyze are income, the ``last salary on the main job'' and
-labor force status (working, unemployed or inactive).
+The labour market outcomes we analyse are income, the ``last salary on the main job'' and
+labour force status (working, unemployed or inactive).
 
 The survey includes self-reported language skills on languages used at
-home, and all other languages they understand.  The respondents are
+home and all other languages they understand. The respondents are
 given some guidance in assessing their skills, they can report either
@@
 to one if one speaks or writes, or uses that language at
-home, and zero otherwise.  Hence we disregard passive understanding
+home, and zero otherwise. Hence, we disregard passive understanding
 only.
 
-For further evidence on ethnic and gender segregation at workplace we use data
+For further evidence on ethnic and gender segregation at the workplace, we use data
 from 2008 Integration Monitor Survey. The survey was conducted by
@@
 question addresses the ethnic segregation while the second focuses on
-the need of communication.
+the need for communication.
 
@@
  from \EUR{314} to \EUR{887} while the language knowledge changed rapidly as
-  well.  However, the ethnic composition of the workforce remained
-  roughly constant.} of Estonian
+well. However, the ethnic composition of the workforce remained roughly constant.} of Estonian
 males who are not fluent in English is \EUR{532} while for Russians it
@@
 for men (\EUR{378} versus \EUR{329} monthly) and 30\% for women
-(\EUR{260} versus \EUR{203}).  Analogously, English is more closely
-associated with income for Estonians compared to Russian language. In
+(\EUR{260} versus \EUR{203}). Analogously, English language skills are more closely
+associated with income for Estonians compared to Russian language skills. In
 contrast, unemployment shows a different picture. For ethnic Russians,
@@
 English is more closely associated with unemployment than Russian:
-Estonians fluent in English have in average 5.0 percent unemployment
+Estonians fluent in English have on average 5.0 percent unemployment
 while those who are not fluent have 8.8 percent. The difference
@@
 being fluent in Estonian, the figure for Russians is similar. We
-also see that Estonians are better in English than Russians and they
-are also better in Russian than vice versa.
+also see that Estonians are better at English than Russians and they
+are also better at Russian than vice versa.
 
@@
 respective age distribution. Not surprisingly, inter-ethnic
-households include disproportionally large share of Russian speaking
+households include a disproportionally large share of Russian speaking
 Estonians and Estonian speaking Russians.
@@
 omitted variable bias and measurement errors \citep{Chiswick1995, bleakley+chin2004}.
-We refrain from doing that. Our decision is mainly data driven,
+We refrain from doing that. Our decision is mainly data-driven,
 there are no suitable instruments in our data,\footnote{We run an IV
@@
 
-We estimate three models that differ in terms of 
-control variables. The first specification only includes the language skills
+We estimate three models that differ in terms of the control variables. The first specification only includes the language skills
 and year dummies. It describes the ``raw'' effect of language skills,
@@
 characteristics (age, education) and family descriptors (marital
-status, indicator for inter-ethnic marriage, having kids up to 17 years
+status, an indicator for inter-ethnic marriage, having kids up to 17 years
 old) and county of residence. 
@@
 			\bottomrule
-		\end{tabular}%
+		\end{tabular}
 		\begin{flushleft}
@@
 variable bias, Russian knowledge was widespread in the Soviet era and may
-not have been closely associated with favorable unobserved
+not have been closely associated with favourable unobserved
 characteristics, however, it has been increasingly associated with age
@@
 individual controls. In contrast, the effect of English
-is close to zero and not statistically significant.  As in
+is close to zero and not statistically significant. As in the
 case of Estonian, individual characteristics change the estimates only
@@
 In summary, these results suggest that Estonian is the only language
-that matters for the employment prospects.  Despite of widespread
+that matters for the employment prospects. Despite widespread
 bilingualism in the service sector, and increasing global importance of
@@
 confirms the descriptive evidence that wage is positively associated
-with fluency of all analyzed languages with English showing the
+with fluency in all analysed languages with English showing the
 largest effect. The only exception is
@@
 			year dummies    & \V             & \V             & \V                 & \V             & \V             & \V             \\
-			indiv.
-charact.
-&                            & \V                         & \V                                 &                            & \V                         & \V                         \\
-			workplace charact.
-&                            &                            & \V                                 &                            &                            & \V                         \\ \bottomrule
+			indiv. charact.  &              & \V             & \V                 &              & \V             & \V             \\
+			workplace charact. &              &              & \V                 &              &              & \V             \\ \bottomrule
 		\end{tabular}
@@
 Individual and workplace controls lower this figure substantially
-implying that both ability bias
-and workplace mobility play a role.
-
-English language is associated with a very large
-wage premium, up to 34 log points, for all the analyzed groups.  The number falls substantially when introducing the
+implying that both, ability bias
+and workplace mobility, play a role.
+
+English language fluency is associated with a very large
+wage premium, up to 34 log points, for all the analysed groups. The number falls substantially when introducing the
 individual characteristics into the model (model 2), additional
-workplace characteristics have less effect.  However, in all
-specifications it remains
-noticeably more
-important than Russian for Estonians. The estimates are rather
+workplace characteristics have less effect. However, in all specifications it remains noticeably more
+important than Russian for Estonians in all
+specifications. The estimates are rather
 similar for Estonian and Russian men but little lower for Russian
@@
 In conclusion, the wage regressions suggest that English is the
-language most closely associated with income for men.  The effect of Russian is minor and
-that of Estonian non-existent.  For women, all three languages are
-associated with higher wage but Russian to a smaller extent.
+language which is most closely associated with income for men. The effect of Russian language fluency is minor and
+that of Estonian language fluency non-existent. For women, all three languages are
+associated with higher wage but the Russian language to a smaller extent.
 This is in a stark contrast to the unemployment regressions and we return to
@@
 
-As Estonian economy went through turbulent times and rapid changes
-during the 1990s, it is instructive to analyze the effect long-term
+As the Estonian economy went through turbulent times and rapid changes
+during the 1990s, it is instructive to analyse the effect long-term
 trends in the estimated effect size. Here we look at the yearly estimates from 1992 to 2012.
 The reader should keep in mind that while the pre-2000 waves include retrospective income, they do not include retrospective language skills. In this way, the results before
-1995 are partly based on extrapolation, assuming individual language
+1995 are partly based on extrapolation, assuming an individual's language
 skills did not vary before that date.
@@
  3 for wage)
-  look qualitatively similar.  More controls in the model reduces the effect size but does not qualitatively
-  change it's temporal pattern.}
+ look qualitatively similar. More controls in the model reduce the effect size but does not qualitatively
+ change its temporal pattern.}
 
@@
 fluency has been associated with less unemployment for both Russian men and
-women since around year 2000, in 1990s it had little effect.  Russian fluency,
+women since around the year 2000, in the 1990s it had little effect. Russian fluency,
 in contrast, had never had an impact on Estonians' unemployment probability.
@@
 	\subfigure[Non-native languages for men]{
-		\includegraphics[width=0.45\linewidth]{Figure1a.eps}
+		\includegraphics[width=0.45\linewidth]{Figure2a.eps}
 
@@
 	\subfigure[Non-native languages for women]{      
-		\includegraphics[width=0.45\linewidth]{Figure1b.eps}
+		\includegraphics[width=0.45\linewidth]{Figure2b.eps}
 		\label{fig:long-run_unemployment_estonian_russian_women}
@@
 	\subfigure[English for Men]{
-		\includegraphics[width=0.45\linewidth]{Figure1c.eps}
+		\includegraphics[width=0.45\linewidth]{Figure2c.eps}
 		\label{fig:long-run_unemployment_english_men}
@@
 	\subfigure[English for Women]{
-		\includegraphics[width=0.45\linewidth]{Figure1d.eps}
+		\includegraphics[width=0.45\linewidth]{Figure2d.eps}
 		\label{fig:long-run_unemployment_english_women}
@@
 period of observation whereas fluency in Russian has no effect.
-Only few of the results are point wise statistically significant though.
+Only a few of the results are point wise statistically significant though.
 For Estonian women, both languages are associated with less
@@
 the late 1990s on. For women, the picture is mostly similar, just the
-effect of Estonian language seems to be somewhat delayed compared to
+effect of Estonian language fluency seems to be somewhat delayed compared to
 that for men.
@@
 	\subfigure[Non-native languages for men]{
-		\includegraphics[width=0.45\linewidth]{Figure2a.eps}
+		\includegraphics[width=0.45\linewidth]{Figure3a.eps}
 		\label{fig:long-run_wage_estonian_russian_men}
@@
 	\subfigure[Non-native languages for women]{
-		\includegraphics[width=0.45\linewidth]{Figure2b.eps}
+		\includegraphics[width=0.45\linewidth]{Figure3b.eps}
 		\label{fig:long-run_wage_estonian_russian_women}
@@
 	\subfigure[English for Men]{
-		\includegraphics[width=0.45\linewidth]{Figure2c.eps}
+		\includegraphics[width=0.45\linewidth]{Figure3c.eps}
 		\label{fig:long-run_wage_english_men}
@@
 	\subfigure[English for Women]{
-		\includegraphics[width=0.45\linewidth]{Figure2d.eps}
+		\includegraphics[width=0.45\linewidth]{Figure3d.eps}
 		\label{fig:long-run_wage_english_women}
@@
 English becomes important in the late 1990s. For Russian men, fluency in Estonian
-has never been significantly associated with wage.
+has never been significantly associated with a wage premium.
 The results are remarkably stable over the whole period, indicating
 that the peculiar labour market institutions have been persistent for
-two decades.  However, for women we can see that Estonian language turned
-important in late 1990s, suggesting that there is either less
-workplace segregation or other kind of necessity to know the official
+two decades. However, for women we can see that Estonian language fluency turned
+important in the late 1990s, suggesting that there is either less
+workplace segregation or another kind of necessity to know the official
 language at
@@
 \label{sec:age_groups}
-As age is a central determinant how major economic and political
+As age is a central determinant of how major economic and political
 reforms influence individual careers, 
-we also analyze the time trends by age groups
+we also analyse the time trends by age groups
 (Table~\ref{tab:age_group_trend}).
@@
 (1989--1995); first economic growth (1996--1999);
-economic boom, EU accession (2000--2007); and the recession
+the economic boom, EU accession (2000--2007); and the recession
 (2008--2012).
@@
 significant since the recession period. English was not important
-during the early years of transition, but has been very closely
-associated with better pay since 1996.  It's importance seems to be
-falling though for the young and middle male groups while the oldest men
+during the early years of transition but has been very closely
+associated with better pay since 1996. Its importance seems to
+fall for the young and middle male groups while the oldest men
 (45-55) and the youngest women (25-35) show a growing trend.
@@
 women as well, but
-since year 2000, we observe a sizable gain of approximately
+since the year 2000, we observe a sizeable gain of approximately
 10\% for all subgroups.
@@
 jobs than those who cannot speak the language.
-In comparison, the estimates for English language trend downward over
-time
-for all age groups for both men and for women.  A likely
+In comparison, the estimates for the English language skills trend downward over
+time for all age groups for both men and for women. A likely
 cause is the increasing abundance of these skills over time.
@@
 To get some additional evidence on these hypotheses, we use data
-from 2008 Integration Monitor Survey.  We focus on
+from the 2008 Integration Monitor Survey. We focus on
 two questions: ``which is the language of communication at your
@@
 Table~\ref{tab:environment_model} presents the corresponding regression results
-where we estimate the likelihood of having the need for, and using the
+where we estimate the likelihood of having the need for and using the
 language at work
@@
 In summary, this dataset supports both of the hypotheses outlined above: Russian women are
-working in less segregated environment where Estonian is the main
-communication language, and they need Estonian at work for other reasons as
+working in a less segregated environment where Estonian is the main
+communication language and they need Estonian at work for other reasons as
 well. Gender differences in English usage are not statistically
@@
 
-We document that all analyzed language skills are associated with
+We document that all analysed language skills are associated with
 unemployment and wage, however in a different way. Our most
@@
 important in the female labour market. Unfortunately, the current data
-does not let us to assess whether is due to decreasing segregation, or
+does not let us assess whether is due to decreasing segregation, or
 economy--wide rise of the importance of Estonian language. No such trend is visible for
-men suggesting that 20 years---almost a generation---after
+men suggesting that 20 years ---almost a generation--- after
 establishing a nation state and market economy, the
-labor market integration is still not complete.
-
-The fact the Russian language is not associated with any better
+labour market integration is still not complete.
+
+The fact that the Russian language is not associated with any better
 employment prospects
@@
 Our other results are more in line with other studies.
-English language is related to a substantial income premium but
+English language fluency is related to a substantial income premium but
 to virtually no effect on unemployment. This is similar to findings by
 \citet{ginsburgh+prieto-rodriguez2011ILRR} and \cite{fabo+2017E}
-who show that English is more important at better paid
+who show that English is more important at better-paid
 jobs. In contrast, our outcomes suggest that English has little use
@@
 large part of English returns, we suppose part of the remaining effect
-may also related to an ability bias.  Another weak point in the current
+may also be related to an ability bias. Another weak point in the current
 data are the self-reported language

### 2018-07-24 paper/ijm.tex
Added file which compares original and revised file. This file will have to be submitted in the end. Produced by latexdiff and manual adjustments.

@@
 \newcommand{\std}[1]{\emph{(#1)}}
-\newcommand{\V}{\ensuremath\checkmark}
+\newcommand{\V}{\checkmark}
 \def\fns{\footnotesize}
@@
 \newcommand{\modelThreeAdd}{industry, occupation, ownership type of company, number of workers in company, working in the public sector, experience in company}	
-\newcommand{\restrictions}{The sample period is from year 2000 to year 2012. Sample is limited to persons
-	25-55
-
- year old.}
+\newcommand{\restrictions}{The sample period is from year 2000 to year 2012. Sample is limited to persons 25-55 year old.}
 \newcommand{\agerestrictions}{25-55 year olds only.}
@@
 %\noindent
-{\centering \textbf{Language Skills in an Ethnically Segmented Labour market: Estonia 1989 -- 2012}}
+{\centering \textbf{Language Skills in an Ethnically Segmented Labour Market: Estonia 1989 -- 2012}}
 \begin{abstract}
  \noindent
- \textbf{Purpose --} We analyse the relationship between skills of
- Estonian, Russian and English, and labour market
+ \textbf{Purpose --} We analyse the relationship between skills in the
+ Estonian, Russian and English language, and labour market
  outcomes in Estonia, a linguistically divided country.
@@
 
-We estimate three models that differ in terms of the control variables. The first specification only includes the language skills
+We estimate three models that differ in the control variables. The first specification only includes the language skills
 and year dummies. It describes the ``raw'' effect of language skills,
@@
 workplace descriptors.
-Note that in case of unemployment probability,
+Note that for the unemployment probability,
 we only estimate the first two models.
@@
 		\begin{flushleft}
-			\caption*{ \legend \\ Standard errors (clustered on individuals) in parentheses.\\ Individual characteristics are \modelTwo. \\ \restrictions}
+			\caption*{ \legend \\ Standard errors (clustered on individuals) in parentheses; \\  Individual characteristics are \modelTwo.  \restrictions }
 		\end{flushleft}
@@
 Estonian language for Russian men where we fail to find any positive
-effect for any of the specifications. This qualitatively repeats the results of
+effect for any of the specifications. This finding qualitatively repeats the results of
 \citet{Toomet2011}. However, for women we observe a sizeable
@@
 		\begin{flushleft}
-			\caption*{\legend \\ Standard errors (clustered on individuals) in parenthesis \\ Individual characteristics are \modelTwo. \\ Workplace characteristics are \modelThreeAdd. \\ \restrictions}
+			\caption*{\legend \\ Standard errors (clustered on individuals) in parenthesis; \\ Individual characteristics are \modelTwo.  Workplace characteristics are \modelThreeAdd.  \restrictions}
 		\end{flushleft}
@@
 associated with higher wage but the Russian language to a smaller extent.
-This is in a stark contrast to the unemployment regressions and we return to
+This result is in a stark contrast to the unemployment regressions and we return to
 this question in the discussion below.
@@
 (45-55) and the youngest women (25-35) show a growing trend.
-This potentially reflects both the changing supply and demand for 
+This result potentially reflects both the changing supply and demand for 
 English.
@@
 statistically significant results at all. This is the most unexpected
-outcome in our analysis and we'll return to this
+outcome in our analysis, and we'll return to this
 below in Section~\ref{sec:segregation-analysis}.
@@
 language gives a distinct advantage by facilitating hiring by
-Estonian-dominated employers. But we also confirm
+Estonian-dominated employers. We also confirm
 \citet{leppik+vihalemm2015JofBaltStud} conclusion that
@@
 
-\listoffixmes
+%\listoffixmes
 

### 2018-07-24 paper/ijm.tex
Hopefully last commit before submission. Minor spelling mistakes.

@@
 \citep{Lang2009, Casale2011, Toomet2011, Williams2011, azam+2013EDandCC, isphording2013, fabo+2017E}.
-The role of other languages, in particular in multi-lingual economy, is
+The role of other languages, in particular in a multi-lingual economy, is
 less clear. For instance,
@@
 countries is rather limited. We know that the different development
-trajectories have led to disparities both favouring Russian-speaking
+trajectories have led to disparities both favouring the Russian-speaking
 minority in Ukraine \citep{Constant2011} and hindering them in Estonia
@@
 valuable while the supply was still rather limited during the early
-years of transition.
+years of the transition.
 
@@
 in the early 1990s \citep{Leping2008,
-	lindemann+saar2011Russian2ndGeneration}. The inter-ethnic contacts
+	lindemann+saar2011Russian2ndGeneration}. Inter-ethnic contacts
 are largely limited to superficial encounters at work and in public
@@
 being fluent in Estonian, the figure for Russians is similar. We
-also see that Estonians are better at English than Russians and they
+also see that Estonians are better at English than Russians, and they
 are also better at Russian than vice versa.
@@
 respective age distribution. Not surprisingly, inter-ethnic
-households include a disproportionally large share of Russian speaking
-Estonians and Estonian speaking Russians.
+households include a disproportionally large share of Russian-speaking
+Estonians and Estonian-speaking Russians.
 The average experience follows the same pattern as age.
-Public sector jobs are associated with disproportionally large share of
+Public sector jobs are associated with a disproportionally large share of
 Estonian fluency among Russian workers, probably reflecting the formal
@@
 where $\vec{L}$ is the vector of
-language skill descriptors, $\vec{X}$ are the other individual
-characteristics, $\eta_{i}$ is the individual-specific effect, $\upsilon_{t}$ are the year dummies and $\epsilon_{it}$
+language skill descriptors. $\vec{X}$ are the other individual
+characteristics. $\eta_{i}$ is the individual-specific effect, $\upsilon_{t}$ are the year dummies and $\epsilon_{it}$
 is the idiosyncratic error term. 
@@
 
-Neither Russian nor English show a comparably strong effect.
+Neither Russian nor English language skills show a comparably strong effect.
 Knowledge of Russian is not associated with less unemployment for
@@
 individual characteristics into the model (model 2), additional
-workplace characteristics have less effect. However, in all specifications it remains noticeably more
+workplace characteristics have less effect. However, it remains noticeably more
 important than Russian for Estonians in all
@@
 As the Estonian economy went through turbulent times and rapid changes
-during the 1990s, it is instructive to analyse the effect long-term
+during the 1990s, it is instructive to analyse the long-term
 trends in the estimated effect size. Here we look at the yearly estimates from 1992 to 2012.
@@
 The results reveal a few interesting facts. First, the effects are
-relatively stable over time, indicating that neither economic
-environment nor the data quality have changed rapidly. Estonian
+relatively stable over time, indicating that neither the economic
+environment nor the data quality have changed rapidly. Estonian language
 fluency has been associated with less unemployment for both Russian men and
-women since around the year 2000, in the 1990s it had little effect. Russian fluency,
+women since around the year 2000, in the 1990s it had little effect. Russian language fluency,
 in contrast, had never had an impact on Estonians' unemployment probability.
@@
 period of observation whereas fluency in Russian has no effect.
-Only a few of the results are point wise statistically significant though.
+Only a few of the results are pointwise statistically significant though.
 For Estonian women, both languages are associated with less
@@
 \citet{leppik+vihalemm2015JofBaltStud} analyse men and women
-separately. We find some evidence that female labor market is less
+separately. We find some evidence that female labour market is less
 segregated along ethnic lines, and women are more frequently employed in jobs in which they need Estonian
@@
 
-%\listoffixmes
-
 \end{document}

### 2018-07-31 paper/ijm.tex
Added descriptions of industry and occupation categories

@@
 \newcommand{\modelThree}{\modelTwo, industry, occupation, ownership type of company, number of workers in company, working in the public sector, experience in company}
+\newcommand{\industry}{Industry categories (according to NACE Rev.2): A Agriculture, Forestry and Fishing; B Mining and Quarrying; C Manufacturing; D Electricity, Gas, Steam and Air Conditioning Supply; E Water Supply;  Sewerage, Waste Management and Remediation Activities; F Construction; G Wholesale and Retail Trade;  Repair of Motor Vehicles and Motorcycles; H Transportation and Storage; I Accommodation and Food Service Activities; J Information and Communication; K Financial and Insurance Activities; L Real Estate Activities; M Professional, Scientific and Technical Activities; N Administrative and Support Service Activities; O Public Administration and Defence;  Compulsory Social Security; P Education; Q Human Health and Social Work Activities; R Arts, Entertainment and Recreation; S Other Service Activities; T Activities of Households as Employers;  Undifferentiate Goods and Services Producing Activities of Households for Own Use; U Activities of Extraterritorial Organisations and Bodies}
+\newcommand{\occupation}{Occupation categories according to ISCO-08: 1 Managers; 2 Professional; 3 Technicians and associate professionals; 4 Clerical support workers; 5 Service and sales workers; 6 Skilled agricultural, forestry and fishery workers; 7 Craft and related trades workers; 8 Plant and machine operators, and assemblers; 9 Elementary occupations; 10 Armed forces occupations}
 \newcommand{\modelThreeAdd}{industry, occupation, ownership type of company, number of workers in company, working in the public sector, experience in company}	
@@
 where the Russian-speaking community forms almost 30\% of
-the population. We use Estonian Labour Force Survey, one of the
+the population. We use the Estonian Labour Force Survey, one of the
 higher-quality long-term datasets, well suitable for our
@@
 the mid-1990s. 
-\Cref{fig:gdp_growth} shows that grew averaged at approximately 7\%
+\Cref{fig:gdp_growth} shows that it grew averaged at approximately 7\%
 annually
@@
 
-The effect of language fluency on unemployment is shown on
-Figure~\ref{fig:long-run_unemployment}, and on wage on
+The effect of language fluency on unemployment is shown in
+Figure~\ref{fig:long-run_unemployment}, and on wage in
 Figure~\ref{fig:long-run_wage}.

### 2018-07-31 paper/ijm.tex
Minor spelling mistakes corected

@@
 
-However, in case of less-than-perfect ethnic integration, the ``local''
+However, in the case of less-than-perfect ethnic integration, the ``local''
 language in ethnic enclaves may be the minority language instead, in
@@
 
-We find that the Estonian language, the majority and the official
+We find that the Estonian language, the ethnic majority and official
 language of the country, is associated with a very
@@
 labour market.
-This suggests for the majority of Russian speaking men, Estonian
+This suggests for the majority of Russian-speaking men, Estonian
 language gives a distinct advantage by facilitating hiring by
@@
 men suggesting that 20 years ---almost a generation--- after
-establishing a nation state and market economy, the
+establishing a nation-state and market economy, the
 labour market integration is still not complete.

### 2018-08-04 paper/ijm.tex
Minor mistakes corrected to be in line with the responses to reviewers

@@
 table clearly indicates that Estonian language skills are associated
-with approximately 5 percentage points lower unemployment for both
+with an approximately 5 percentage points lower unemployment for both
 Russian men and women. We also see that the effect is not 
@@
 			          & (0.026)          & (0.027)          & (0.024)              & (0.021)          & (0.022)          & (0.018)          \\
-			\# Observations       & \multicolumn{1}{l}{7978}  & \multicolumn{1}{l}{7978}  & \multicolumn{1}{l}{7978}      & \multicolumn{1}{l}{9904}  & \multicolumn{1}{l}{9895}  & \multicolumn{1}{c}{9697}  \\
+			\# Observations       & \multicolumn{1}{l}{7,978}  & \multicolumn{1}{l}{7,978}  & \multicolumn{1}{l}{7,978}      & \multicolumn{1}{l}{9,697}  & \multicolumn{1}{l}{9,697}  & \multicolumn{1}{c}{9,697}  \\
 			$R^{2}$      & 0.731           & 0.746           & 0.794               & 0.794           & 0.809           & 0.854           \\ \hline
@@
 		\begin{flushleft}
-			\caption*{\legend \\ Standard errors (clustered on individuals) in parenthesis; \\ Individual characteristics are \modelTwo.  Workplace characteristics are \modelThreeAdd.  \restrictions}
+			\caption*{\legend \\ Standard errors (clustered on individuals) in parentheses; \\ Individual characteristics are \modelTwo.  Workplace characteristics are \modelThreeAdd.  \restrictions}
 		\end{flushleft}
@@
 
-	\caption*{\legend \\ Standard errors (clustered on individuals) in parenthesis. \\ Individual characteristics are \modelTwo. 	}
+	\caption*{\legend \\ Standard errors (clustered on individuals) in parentheses. \\ Individual characteristics are \modelTwo. 	}
 	\label{tab:age_group_trend}
@@
   Tallinn & $<$ HS & 399 & -0.20 & -0.01 & 0.19 \\ 
-  Tallinn & HS & 2164 & 0.07 & 0.04 & -0.03 \\ 
+  Tallinn & HS & 2,164 & 0.07 & 0.04 & -0.03 \\ 
   Tallinn & College Degree & 610 & 0.15 & 0.30 & 0.15 \\ 
   Other & $<$ HS & 501 & -0.12 & -0.12 & -0.01 \\ 
-  Other & HS & 2658 & -0.10 & -0.07 & 0.03 \\ 
+  Other & HS & 2,658 & -0.10 & -0.07 & 0.03 \\ 
   Other & College Degree & 429 & 0.17 & 0.11 & -0.06 \\ 
@@
 respectively), although the standard errors are large. We can also see that
-college education is associated by much more Estonian need and usage,
-but in regions where Russian speakers are concentrated, the capital
+college education is associated with much more Estonian need and usage,
+but in regions where large amounts of Russian speakers live, the capital
 Tallinn and the North-East, Estonian is less needed. In contrast, no
@@
 We document that all analysed language skills are associated with
-unemployment and wage, however in a different way. Our most
+unemployment and wage, however in different ways. Our most
 intriguing observation is that the largest group of
@@
 important in the female labour market. Unfortunately, the current data
-does not let us assess whether is due to decreasing segregation, or
+does not let us assess whether this is due to decreasing segregation, or
 economy--wide rise of the importance of Estonian language. No such trend is visible for

### 2018-08-09 paper/ijm.tex
Maybe the very last comit before submission; some missing grammatical articles added; further improved consistency between  response to reviewers and actual text

@@
 \citep{chiswick+miller2007}.
-Immigrants who are fluent in the local language also suffer
+Immigrants who are fluent in the local ethnic majority language also suffer
 substantially less from unemployment \citep{shields+price2002, Dustmann2003}.
@@
 The paper continues as follows: The next section provides a brief
-background of Estonian society and the labour market. In the following
+background of the Estonian society and the labour market. In the following
 section, we discuss the data and provide some descriptive
@@
 
-Such an influx of mainly
+Such an influx of a mainly
 Russian-speaking population
@@
 first conducted in 1995 by the Estonian Statistical Office. We limit
-ourselves with years 2000--2012 in the main analysis, motivated by a
+ourselves to the years 2000--2012 in the main analysis, motivated by a
 methodology break: Until 1999 the survey was conducted as an annual
@@
 
-The labour market outcomes we analyse are income, the ``last salary on the main job'' and
-labour force status (working, unemployed or inactive).
+The labour market outcomes we analyse are income, the ``last salary on the main job'', and
+labour force status (working or unemployed).
 
@@
 Russian men and women. We also see that the effect is not 
-influenced in any major way by the individual characteristics--for men it is
+influenced in any major way by the individual characteristics-- for men it is
 virtually unchanged while for women the estimate falls by 30\%, from
@@
 	}
-	\caption{The effect of language fluency on unemployment, 1992--2012. \\ Control variables are \modelTwo. \agerestrictions }
+	\caption{The effect of language fluency on unemployment, 1992--2012. \\ Control variables are \modelTwo; \agerestrictions }
 	\label{fig:long-run_unemployment}
@@
 	}
-	\caption{The effect of language fluency on wage, 1992--2012. \\ Control variables are \modelTwo. \agerestrictions}
+	\caption{The effect of language fluency on wage, 1992--2012. \\ Control variables are \modelTwo; \agerestrictions}
 	\label{fig:long-run_wage}
@@
 highest completed education level, are working
-primarily in Russian language environment (ethnic segregation) while this is not true for
+primarily in a Russian language environment (ethnic segregation) while this is not true for
 women; and second, Russian-speaking men are working in jobs with
@@
 points more at work than Russian men. The table also suggests that
-Russian women are 16 percentage points more likely to be working in
+Russian women are 16 percentage points more likely to be working in an
 Estonian-speaking environment when controlling for other factors.
-Both figures are statistically significant (at 5\% and 10 \% level
+Both figures are statistically significant (at the 5\% and 10 \% level
 respectively), although the standard errors are large. We can also see that
@@
 Russian men, high school graduates, earn virtually no income premium if fluent in Estonian,
-the majority and the official language of the country, while ability
+the majority and official language of the country, while ability
 to speak the language is related to a substantially

### 2019-01-13 paper/ijm.tex
Minor changes for the article proof

@@
-%\documentclass[10pt,a4paper,english]{article}
-\documentclass[12pt, a4paper]{article}
+\documentclass[12pt, a4paper,english]{article}
 \usepackage[utf8]{inputenc}
 \usepackage[T1]{fontenc}
-\usepackage[margin=2.5cm,top=2.5cm, bottom=2.0cm]{geometry}
-\usepackage[english]{babel}
+\usepackage[hmargin=2.5cm,top=2.5cm, bottom=2.0cm]{geometry}
+\usepackage{babel}
 %\usepackage{lmodern}
@@
 \usepackage{epstopdf}
-\usepackage[layout=margin,author=,status=draft]{fixme}
- \usepackage[final]{changes} %Manually track changes
- \definechangesauthor{SKB}
 \usepackage{longtable}
@@
 \usepackage[natbibapa]{apacite}
-%\usepackage[authoryear]{natbib}
+
 \usepackage{csquotes}
@@
 
-\DeclareUnicodeCharacter{2010}{-}% support older LaTeX versions
+%\DeclareUnicodeCharacter{2010}{-}% support older LaTeX versions
 \thanksfootextra{}{\hfill}
@@
 
-\fxsetup{theme=color}
 %Custom commands
@@
 \renewcommand*{\vec}[1]{\boldsymbol{#1}}
-
+%\section{Own commands}
 \def\tenpc{$^{\ast}$}
@@
 			$\ast$ : 5\% \hspace{1em} $\ast\ast$ : 1\% \normalsize}}}
-\def\sym#1{\ifmmode^{#1}\else\(^{#1}\)\fi} % needed for the tables produced by the esttab command in Stata, to avoid redundancy put here instead of in appendix.tex, where it is needed		
-%SKB: Added for documenting the tables and figures
+\def\sym#1{\ifmmode^{#1}\else\(^{#1}\)\fi} 
+%Added for documenting the tables and figures
 \newcommand{\modelTwo}{age, age\textsuperscript{2}, education, marriage, number of children, inter-ethnic household}
 \newcommand{\modelThree}{\modelTwo, industry, occupation, ownership type of company, number of workers in company, working in the public sector, experience in company}
-\newcommand{\industry}{Industry categories (according to NACE Rev.2): A Agriculture, Forestry and Fishing; B Mining and Quarrying; C Manufacturing; D Electricity, Gas, Steam and Air Conditioning Supply; E Water Supply;  Sewerage, Waste Management and Remediation Activities; F Construction; G Wholesale and Retail Trade;  Repair of Motor Vehicles and Motorcycles; H Transportation and Storage; I Accommodation and Food Service Activities; J Information and Communication; K Financial and Insurance Activities; L Real Estate Activities; M Professional, Scientific and Technical Activities; N Administrative and Support Service Activities; O Public Administration and Defence;  Compulsory Social Security; P Education; Q Human Health and Social Work Activities; R Arts, Entertainment and Recreation; S Other Service Activities; T Activities of Households as Employers;  Undifferentiate Goods and Services Producing Activities of Households for Own Use; U Activities of Extraterritorial Organisations and Bodies}
-\newcommand{\occupation}{Occupation categories according to ISCO-08: 1 Managers; 2 Professional; 3 Technicians and associate professionals; 4 Clerical support workers; 5 Service and sales workers; 6 Skilled agricultural, forestry and fishery workers; 7 Craft and related trades workers; 8 Plant and machine operators, and assemblers; 9 Elementary occupations; 10 Armed forces occupations}
+\newcommand{\industry}{Industry categories (according to NACE Rev.2): A Agriculture, Forestry and Fishing; B Mining and Quarrying; C Manufacturing; D Electricity, Gas, Steam and Air Conditioning Supply; E Water Supply;  Sewerage, Waste Management and Remediation Activities; F Construction; G Wholesale and Retail Trade;  Repair of Motor Vehicles and Motorcycles; H Transportation and Storage; I Accommodation and Food Service Activities; J Information and Communication; K Financial and Insurance Activities; L Real Estate Activities; M Professional, Scientific and Technical Activities; N Administrative and Support Service Activities; O Public Administration and Defence;  Compulsory Social Security; P Education; Q Human Health and Social Work Activities; R Arts, Entertainment and Recreation; S Other Service Activities; T Activities of Households as Employers;  Undifferentiate Goods and Services Producing Activities of Households for Own Use; U Activities of Extraterritorial Organisations and Bodies \\ }
+\newcommand{\occupation}{Occupation categories according to ISCO-08: 1 Managers; 2 Professional; 3 Technicians and associate professionals; 4 Clerical support workers; 5 Service and sales workers; 6 Skilled agricultural, forestry and fishery workers; 7 Craft and related trades workers; 8 Plant and machine operators, and assemblers; 9 Elementary occupations; 10 Armed forces occupations \\ }
+\newcommand{\ownership}{Ownership types: 10 -- government (Estonian State);
+	20 -- local government;
+	30 -- private, Estonian;
+	40 -- private, foreign;
+	50 -- private, mixed Estonian and foreign;
+	90 -- other}
 \newcommand{\modelThreeAdd}{industry, occupation, ownership type of company, number of workers in company, working in the public sector, experience in company}	
@@
 %	{\large Sven-Kristjan Bormann} \\
-%	\emph{School of Economics and Business Administration, University of Tartu, Narva mnt. 4, 51007 Tartu, Estonia\\ Tel.: +372 5844 3873\\ Email: \href{mailto:bormann@ut.ee}{bormann@ut.ee}}	\\
+%	\emph{School of Economics and Business Administration, University of Tartu, Liivi. 4, 51007 Tartu, Estonia\\ Tel.: +372 5844 3873\\ Email: \href{mailto:bormann@ut.ee}{bormann@ut.ee}}	\\
 %
@@
 
-% Table generated by Excel2LaTeX from sheet 'subgroups_by_ethnic_language'
 \begin{sidewaystable}[htbp]
 	\centering
+
 	\caption{Averages and relative frequencies of selected explanatory
@@
 Russian men and women. We also see that the effect is not 
-influenced in any major way by the individual characteristics-- for men it is
+influenced in any major way by the individual characteristics. For men it is
 virtually unchanged while for women the estimate falls by 30\%, from
@@
 		\caption{Estimation results for unemployment.}
-		\label{tab:unemployment_estimation_by_sex_and_ethnic_same_sample} %SKB 04.07.2018 14:22:Not yet updated only prepared
+		\label{tab:unemployment_estimation_by_sex_and_ethnic_same_sample} 
 		\begin{tabular}{l D{.}{.}{3} @{\qquad} D{.}{.}{3} @{\qquad\qquad}
@@
 		\caption{Estimation results for log wage}
-		\label{tab:wage_estimation_by_sex_and_ethnic_same_sample} %SKB 04.07.2018 14:22:Not yet updated only prepared
-		%Accounting for occupation in model reduced the Estonian coefficient for women drastically (from 0.12 down 0.06)!
-		%For other groups it is less
+		\label{tab:wage_estimation_by_sex_and_ethnic_same_sample} 
 		\begin{tabular}{l | D{.}{.}{3} @{\qquad} D{.}{.}{3} @{\qquad} D{.}{.}{3} @{\qquad} | @{\qquad}
@@
 
-% latex table generated in R 3.4.4 by xtable 1.8-2 package
-% Fri Jul 6 15:59:47 2018
 \begin{table}[ht]
